### 2017-11-01 paper/paper.tex
Adding paper outline

\documentclass[conference]{IEEEtran}
\usepackage{pdftexcmds}
\usepackage[pdftex]{graphicx}
\usepackage{multirow}
\usepackage{pgfplots}
\usepackage{tikz}
\usepackage{balance}
\usepackage{amssymb, marvosym}
\usepackage{threeparttable}
\usepackage[bookmarks=false]{hyperref}
\usepackage{url}
\PassOptionsToPackage{hyphens}{url}
\hypersetup{colorlinks=true,breaklinks=true}
\usetikzlibrary{patterns,shapes,arrows}
\newcommand\tab[1][.5cm]{\hspace*{#1}}
\hyphenation{op-tical net-works semi-conduc-tor}
\IEEEoverridecommandlockouts
\raggedbottom
\newcommand{\tool}{tool-recommender-bot }
\begin{document}

% Copyright
%\setcopyright{acmlicensed}

\title{\tool}

\author{\IEEEauthorblockN{Chris Brown and Emerson Murphy-Hill}
\IEEEauthorblockA{Department of Computer Science\\
North Carolina State University\\
Raleigh, NC\\
Email: dcbrow10@ncsu.edu, emerson@csc.ncsu.edu}
}

\maketitle
\begin{abstract}
Automated recommendation systems are important for improving tool discovery and increasing user productivity. Here's ours...
\end{abstract}

\begin{IEEEkeywords}
Software Engineering; Tool Recommendation; Tool Discovery; Open Source
\end{IEEEkeywords}

\section{Introduction}
%Importance
Tool discovery is a problem... \\

Automated recommendation systems can help solve this problem... \\

But existing recommendations systems are ineffective... \\

Peer interactions and receptiveness are effective\cite{vlhcc17}... \\

We created \tool to solve this... \\

\noindent
\textbf{RQ1:} How often can we expect \tool to make recommendations?  \\
\textbf{RQ2:} How useful are recommendations from \tool to developers?  \\

Contributions...\\

\section{Related Work}

Existing automated tool recommendation systems...

\section{Tool}
\tool is awesome. Here's how...

\subsection{Implementation}
Technical details...

\subsection{Receptiveness}
How we integrated receptiveness...

\paragraph{Desire}

\paragraph{Familiarity}

\section{Methodology}

\subsection{Projects}

Trending open source java projects on Github that build with maven used for evaluation...

\subsection{Study Design}

We divided our study into two segments to address each research question:

\subsubsection{RQ1}

Last n pull requests on repositories...

\subsubsection{RQ2}

Followed up with developers to gather responses...

\section{Results}

\subsection{How often can we expect \tool to make recommendations?}

Number of recommendations... \\

0 false positives... \\

\subsection{How useful are recommendations from \tool to developers?}

Response rate...\\

Qualitative responses... \\

\section{Discussion}

\subsection{Implications}

What do results say about ways to improve tool recommendation systems...

\subsection{Threats to Validity}

\subsection{Future Work}

\section{Conclusion}

%\balance
%\section{Acknowledgments}

%Thanks to all of the student and professional data analysts who volunteered for this study.

% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{paper}  
% You must have a proper ''.bib'' file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!

%% That's all folks!
\end{document}

### 2017-11-02 com/chbrown13/pull_rec/PullRecommender.java
Adding cleanup functionality to delete temp repos

@@ -80,6 +80,7 @@ public class PullRecommender {
 		} catch (IOException e) {
 			e.printStackTrace();
 		}	
+		Utils.cleanup();
 	}
 
 	/**
@@ -117,20 +118,6 @@ public class PullRecommender {
 			}
 		}
 		System.out.println("{num} recommendations made for {prs} prs.".replace("{num}", Integer.toString(recommender.getRecommendationCount())).replace("{prs}", Integer.toString(recommender.getPRCount())));
-		
-		/*try {
-			Utils.cd("RecommenderTest");
-			Process p = Runtime.getRuntime().exec("sh RecommenderTest/checkout.sh");
-			BufferedReader br = new BufferedReader(new InputStreamReader(p.getErrorStream()));
-			String line;
-			String output = "";
-			while ((line = br.readLine()) != null) {
-			    output += line + "\n";
-			}
-			System.out.println(output);
-		} catch (Exception e) {
-			e.printStackTrace();
-		}	*/
 	}
 }
 

### 2017-11-02 com/chbrown13/pull_rec/Utils.java

@@ -502,8 +502,18 @@ public class Utils {
 		return tool.parseOutput(log);
 	}
 
+	/**
+	 * Remove temp repositories in directory
+	 */
 	public static void cleanup() {
-		//Process p = Runtime.getRuntime().exec(REMOVE.replace("{project}", projectName));
+		try {
+			String[] dirs = {projectName+"1", projectName+"2"};
+			for (String d: dirs) {
+				Process p = Runtime.getRuntime().exec("rm -rf " + d);
+			}
+		} catch (Exception e) {
+			e.printStackTrace();
+		}	
 	}
 
 	/**

### 2017-11-02 com/chbrown13/pull_rec/PullRecommender.java
Checkout each repo instead of re-clone

@@ -71,7 +71,7 @@ public class PullRecommender {
 				fixed.removeAll(pullErrors);
 				for (Error e: fixed) {
 					System.out.println(e.getKey() + " " + pullErrors.contains(e));
-					if (Utils.isFix(baseHash, pullHash, e)) {
+					if (Utils.isFix(e)) {
 						makeRecommendation(tool, pull, e, pullHash, Utils.getFix(), baseErrors);
 					}
 				}
@@ -80,7 +80,6 @@ public class PullRecommender {
 		} catch (IOException e) {
 			e.printStackTrace();
 		}	
-		Utils.cleanup();
 	}
 
 	/**

### 2017-11-02 com/chbrown13/pull_rec/Utils.java

@@ -14,6 +14,8 @@ import java.net.*;
 import java.util.*;
 import javax.xml.parsers.*;
 import org.eclipse.jgit.api.Git;
+import org.eclipse.jgit.api.errors.JGitInternalException;
+import org.eclipse.jgit.api.ResetCommand.ResetType;
 import org.eclipse.jgit.lib.Repository;
 import org.eclipse.jgit.storage.file.FileRepositoryBuilder;
 import org.xml.sax.*;
@@ -34,13 +36,7 @@ public class Utils {
 
 	private static String MVN_COMPILE = "mvn -q -f {dir}/pom.xml compile";
 
-	private static String REMOVE = "rm -rf {project}*";
-
-	private static String CHECKOUT = "git --git-dir=_project/.git fetch origin pull/{num}/head:_name && git --git-dir=_project/.git checkout -f _name";
-
 	private static String currentDir = System.getProperty("user.dir");
-
-	private static List<String> created = new ArrayList<String>();
 
 	private static boolean myTool = false;
 
@@ -139,7 +135,6 @@ public class Utils {
 			}
 			prev = line;
 		}
-
 		File file = new File(srcFile);
 		try {
 			int i = 0;
@@ -168,7 +163,7 @@ public class Utils {
 	 * Check if a node exists in the updated file
 	 * 
 	 * @param node   ITree to search for in destination file
-	 * @param map    Mapping between file versions
+	 * @param tree   Mapping between file versions
 	 * @return       True if node is in new file, else false
 	 */
 	private static boolean searchNode(ITree node, ITree tree) {
@@ -244,7 +239,6 @@ public class Utils {
 		} catch (IOException e) {
 			e.printStackTrace();
 		}
-
 		MappingStore store = m.getMappings();		
 		ITree errorNode = getErrorNode(tree1.getRoot(), errorPos);
 		List<Action> actions = g.getActions(); 
@@ -280,8 +274,8 @@ public class Utils {
 	/**
 	 * Checks if pull request changes only remove code without fix
 	 * 
-	 * @param base   Path to base file
-	 * @param pull   Path to pull request version of file
+	 * @param file1   Path to base file
+	 * @param file2   Path to pull request version of file
 	 * @param error  Current error to check
 	 * @return       False if code is updated or added, otherwise true
 	 */
@@ -300,7 +294,6 @@ public class Utils {
    				}
 			}
 			System.out.println("Error removed but may not have been fixed");
[…]

### 2017-11-02 com/chbrown13/pull_rec/PullRecommender.java
Updating output and fixing repo issues

@@ -14,6 +14,8 @@ public class PullRecommender {
 	private Repo repo;
 	private int recs;
 	private Set<String> prs;
+	private static int open = 0;
+	private static int pulls;
 
 	public PullRecommender(Repo repo) {
 		this.repo = repo;
@@ -70,13 +72,14 @@ public class PullRecommender {
 				//System.out.println("LET'S GO!!!!!!!!!!!!!");
 				fixed.removeAll(pullErrors);
 				for (Error e: fixed) {
-					System.out.println(e.getKey() + " " + pullErrors.contains(e));
+					//System.out.println(e.getKey() + " " + pullErrors.contains(e));
 					if (Utils.isFix(e)) {
 						makeRecommendation(tool, pull, e, pullHash, Utils.getFix(), baseErrors);
 					}
 				}
 
 			}
+			Utils.cleanup();
 		} catch (IOException e) {
 			e.printStackTrace();
 		}	
@@ -99,8 +102,16 @@ public class PullRecommender {
 				break;
 			}
 			Pull.Smart pull = new Pull.Smart(pullit.next());
+			try{
+				if (pull.state().equals("open")) {
+					open += 1;
+				}
+			} catch (Exception e) {
+				//nada
+			}
 			requests.add(pull);
 			i++;
+			pulls++;
 		}
 		return requests;
 	}
@@ -116,7 +127,11 @@ public class PullRecommender {
 				recommender.analyze(pull);
 			}
 		}
-		System.out.println("{num} recommendations made for {prs} prs.".replace("{num}", Integer.toString(recommender.getRecommendationCount())).replace("{prs}", Integer.toString(recommender.getPRCount())));
+		System.out.println("{num} recommendations made on {prs} PRs, {open} which were open out of {pulls} total."
+			.replace("{num}", Integer.toString(recommender.getRecommendationCount()))
+			.replace("{prs}", Integer.toString(recommender.getPRCount()))
+			.replace("{open}", Integer.toString(open))
+			.replace("{pulls}", Integer.toString(pulls)));
 	}
 }
 

### 2017-11-02 com/chbrown13/pull_rec/Utils.java

@@ -412,7 +412,7 @@ public class Utils {
 	 * @param tool  Static analysis tool to analyze code
 	 */
 	private static void addToolPomPlugin(String dir, Tool tool) {
-		try{
+		try {
 			String pom = String.join("/",currentDir, dir, "pom.xml");
 			File tempPom = new File(String.join("/",currentDir, dir, "pom.temp"));
 			FileWriter writer = new FileWriter(tempPom, false);
@@ -436,26 +436,20 @@ public class Utils {
 	 */
 	public static Set<Error> checkout(String hash, String author, Tool tool, boolean base) {
 		String dirName = projectName;
+		String owner = "";
 		if(base) {
 			dirName += "1";
+			owner = projectOwner;
 		} else {
 			dirName += "2";
+			owner = author;
 		}
 		try {
 			Git git = Git.cloneRepository()
-			.setURI("https://github.com/{owner}/{repo}.git".replace("{owner}", author)
+			.setURI("https://github.com/{owner}/{repo}.git".replace("{owner}", owner)
 				.replace("{repo}", projectName))
 			.setDirectory(new File(dirName)).call();
 			git.checkout().setName(hash).call();
-		} catch (JGitInternalException jgie) {
-			try {
-				Git git = Git.open(new File(String.join("/", currentDir, dirName, ".git")));
-				git.reset().setMode(ResetType.HARD).setRef( "master" ).call();
-				git.checkout().setName(hash).setForce(true).call();
-			} catch (Exception e) {
-				e.printStackTrace();
-				return null;
-			}
 		} catch (Exception e) {
 			e.printStackTrace();
 			return null;
@@ -464,6 +458,20 @@ public class Utils {
 		addToolPomPlugin(dirName, tool);
 		String log = compile(dirName);
 		return tool.parseOutput(log);
+	}
+
+	/**
+	 * Remove temp repo directories
+	 */
+	public static void cleanup() {
+		try {
+			String[] dirs = {projectName+"1", projectName+"2"};
+			for (String d: dirs) {
+				Process p = Runtime.getRuntime().exec("rm -rf " + d);
+			}
+		} catch (Exception e) {
+			e.printStackTrace();
+		}	
 	}
 
 	/**

### 2017-11-03 com/chbrown13/pull_rec/ErrorProne.java
Updating maven xml to show all errors as warnings

@@ -17,7 +17,11 @@ public class ErrorProne extends Tool {
 			"<version>3.3</version>\n" +
 			"<configuration>\n" +
 	  		"<compilerId>javac-with-errorprone</compilerId>\n" +
-	  		"<forceJavacCompilerUse>true</forceJavacCompilerUse>\n" +
+			"<forceJavacCompilerUse>true</forceJavacCompilerUse>\n" +
+			"<showWarnings>true</showWarnings>" +
+			"<compilerArgs>" +
+			"<arg>-XepAllErrorsAsWarnings</arg>" +
+			"</compilerArgs>" +
 	  		"<source>8</source>\n" +
 	  		"<target>8</target>\n" +
 			"</configuration>\n" +

### 2017-11-07 paper/paper.tex
Updates to paper abstract and other random notes

@@
 \begin{abstract}
-Automated recommendation systems are important for improving tool discovery and increasing user productivity. Here's ours...
+Recommendation systems were developed to improve the adoption of useful software tools and features designed to save time and effort in completing tasks that are often ignored by users.
+Previous research suggests that peer-to-peer recommendations are the most effective mode of tool discovery and that the receptiveness of recommendees is the most important characteristic in determining the outcome of tool recommendations.
+To help increase awareness of useful tools, we developed and evaluated a new recommendation system \tool designed to integrate aspects of peer interactions and user receptivity into automated tool suggestions for software developers of real-world applications.
+Our findings suggest that \tool is awesome, cool, and very effective in improving tool discovery.
 \end{abstract}
@@
 
-Peer interactions and receptiveness are effective\cite{vlhcc17}... \\
+Peer interactions and receptiveness are effective~\cite{vlhcc17}... \\
 
@@
 
-Contributions...\\
+To answer these questions, we conducted a study analyzing \tool on five?
+popular open source Java projects to observe how many tool suggestions would be made based on past changes to the code base and how software developers reacted to receiving recommendations.
+This research makes the following contributions:\\
+
+\begin{itemize}
+\item We introduce the design and implementation of a novel automated recommendation system \tool
+\item We provide implications for future
+\end{itemize}
 
 \section{Related Work}
+
+Improving tool discovery...\\
 
@@
 \subsection{Implementation}
-Technical details...
+\tool technical details...
+
+\subsubsection{Jenkins}
+
+\subsubsection{Maven}
+
+\subsubsection{Error Prone}
 
 \subsection{Receptiveness}
-How we integrated receptiveness...
+\tool was designed to integrate characteristics of peer interactions into automated recommendations.
+To better understand what makes peer-to-peer recommendations an effective mode of tool discovery, we observed how colleagues recommend tools to each other while completing tasks in a previous study.
+Our results found that the receptiveness of users was the only significant indicator of determining whether a tool recommendation was effective or not.
+Fogg defines receptiveness with to criteria, \textit{demonstrating desire} and \textit{familiarity} with the technology~\cite{FoggPersuasive}.
 
@@
 
-Last n pull requests on repositories...
+Last 100 pull requests on repositories...
 
@@
 
-Followed up with developers to gather responses...
+Followed up with pull request authors to gather data on recommendation...
 
@@
 
-Number of recommendations... \\
+Tons of recommendations... \\
 
-0 false positives... \\
+No false positives... \\
 
@@
 
-Response rate...\\
+Excellent responses from recommendees...\\
 
-Qualitative responses... \\
+Statistically significant data...
 
@@
 
-What do results say about ways to improve tool recommendation systems...
+Here's what our results say about ways to improve tool recommendation systems...
 
@@
 
+Internal:
+
+External: Java, open vs. closed source, Error Prone,
+
 \subsection{Future Work}
+
+More tools to recommend (static analysis, security, etc.) \\
+
+More programming languages instead of just java...\\
+
+More build systems (ant, gradle, TravisCI, bazel)...\\
 

### 2017-11-07 com/chbrown13/pull_rec/ErrorProne.java
Updating fix and logging output

@@ -17,7 +17,6 @@ public class ErrorProne extends Tool {
 			"<version>3.3</version>\n" +
 			"<configuration>\n" +
 	  		"<compilerId>javac-with-errorprone</compilerId>\n" +
-			"<forceJavacCompilerUse>true</forceJavacCompilerUse>\n" +
 			"<showWarnings>true</showWarnings>\n" +
 			"<compilerArgs>\n" +
 			"<arg>-XepAllErrorsAsWarnings</arg>\n" +
@@ -87,6 +86,7 @@ public class ErrorProne extends Tool {
 				}
 				String errorMessage = error[3];
 				temp = new Error(errorFileName, errorFilePath, errorLine, errorProne, errorMessage, "");
+				temp.addLog(line);
 			} else if (temp != null) {
 				temp.addLog(line);
 			}

### 2017-11-07 com/chbrown13/pull_rec/PullRecommender.java

@@ -39,6 +39,15 @@ public class PullRecommender {
 	}
 
 	/**
+	 * Checks if the change is actually a fix or not
+	 */
+	private boolean isFix(Set<Error> base, Set<Error> pull, Error error) {
+		if (base.size() == 0 || pull.size() == 0 || base.size() == pull.size()) {
+			return false;
+		}
+		return Utils.isFix(error);
+	}
+	/**
 	 * Analyze code of files in pull request and compare to master branch.
 	 *
 	 * @param pull   Current pull request
@@ -48,7 +57,7 @@ public class PullRecommender {
 		Tool tool = new ErrorProne();
 		System.out.println("Analyzing PR #" + Integer.toString(pull.number()) + "...");
 		try {
-			String author = pull.json().getJsonObject("user").getString("login");
+			String author = pull.json().getJsonObject("head").getJsonObject("user").getString("login");
 			String pullHash = pull.json().getJsonObject("head").getString("sha");
 			String baseHash = pull.json().getJsonObject("base").getString("sha");
 			Set<Error> baseErrors = Utils.checkout(baseHash, author, tool, true);
@@ -60,13 +69,13 @@ public class PullRecommender {
 				int i = 0;
 				for (Error e: fixed) {
 					//System.out.println(e.getKey());
-					if (Utils.isFix(e)) {
-						System.out.println("Fixed "+ e.getKey() +" in PR #"+Integer.toString(pull.number()));
+					if (isFix(baseErrors, pullErrors, e)) {
+						System.out.println("Fixed "+ e.getKey() +" in PR #"+Integer.toString(pull.number())+" "+pull.title());
 						makeRecommendation(tool, pull, e, pullHash, Utils.getFix(), baseErrors);
 					} else {
 						removed += 1;
 					}
-				}
+				}	
 			}
 			Utils.cleanup();
 		} catch (IOException e) {
@@ -122,6 +131,9 @@ public class PullRecommender {
 			.replace("{open}", Integer.toString(open))
 			.replace("{pulls}", Integer.toString(pulls))
 			.replace("{rem}", Integer.toString(removed)));
+		for (Integer i: prs) {
+			System.out.println(i);
+		}
 	}
 }
 

### 2017-11-07 com/chbrown13/pull_rec/Utils.java

@@ -237,6 +237,7 @@ public class Utils {
 		Matcher m = null;
 		ActionGenerator g = null;
 		boolean deleteOnly = true;
+		boolean insertOnly = true;
 		try {
 			tree1 = jdt1.generateFromFile(base);
 			tree2 = jdt2.generateFromFile(pull);
@@ -263,12 +264,15 @@ public class Utils {
 			if(!a.toString().startsWith("DEL")) {
 				deleteOnly = false;
 			}
+			if(!a.toString().startsWith("INS")) {
+				insertOnly = false;
+			}
 			int pos = a.getNode().getPos();
 			if (Math.abs(errorNode.getPos() - pos) < Math.abs(errorNode.getPos() - closestAction.getNode().getPos())) {
 				closestAction = a;
 			}
 		}
-		if (deleteOnly) {
+		if (deleteOnly || insertOnly) {
 			return -1;
 		}
 		ITree temp = null;
@@ -295,13 +299,7 @@ public class Utils {
 	 * @return   Line number of what is considered a fix or null if none
      */
 	public static int getFix() {
-		if (fixLine > 0) {
-			return fixLine;
-		} else if (fixLine == 0) {
-			return 1;
-		} else { // Shouldn't have been considered a fix
-			return (Integer)null;
-		}
+		return fixLine;
 	}
 
 	/**
@@ -313,6 +311,10 @@ public class Utils {
 	public static boolean isFix(Error error) {
 		String file1 = error.getFilePath();
 		String file2 = file1.replace(projectName + "1", projectName+"2");
+		if (!(new File(file1).isFile()) || !(new File(file2).isFile())) {
+			System.out.println("No file");
+			return false;
+		}
 		return findFix(file1, file2, getErrorOffset(error, file1)) > 0;
 	}
 
@@ -336,7 +338,7 @@ public class Utils {
 			e.printStackTrace();
 			return null;
 		}
-		System.out.println(output);
+		//System.out.println(output);
 		return output;
 	}
 

### 2017-11-07 paper/paper.tex
Updates to paper and description of tools for evaluation

@@
 
-\subsubsection{Maven}
-
 \subsubsection{Error Prone}
@@
 \tool was designed to integrate characteristics of peer interactions into automated recommendations.
-To better understand what makes peer-to-peer recommendations an effective mode of tool discovery, we observed how colleagues recommend tools to each other while completing tasks in a previous study.
-Our results found that the receptiveness of users was the only significant indicator of determining whether a tool recommendation was effective or not.
-Fogg defines receptiveness with to criteria, \textit{demonstrating desire} and \textit{familiarity} with the technology~\cite{FoggPersuasive}.
+To better understand user-to-user recommendations and why they are effective for tool discovery, we observed how colleagues recommend tools to each other while completing tasks in prior work.
+Our results found that the receptiveness of users was the only significant indicator of determining whether a tool recommendation was effective or not compared to other interaction characteristics, such as politeness~\cite{vlhcc17}.
+Fogg defines receptiveness using two criteria, \textit{demonstrating a desire} and \textit{familiarity} with the adopted behavior~\cite{FoggPersuasive}.
 
@@
 
-Trending open source java projects on Github that build with maven used for evaluation...
+To evaluate the effectiveness of our recommendation system, we implemented \tool on five real-world open-source software applications.
+We selected projects hosted on Github\footnote{https://github.com}, a popular source code management site that hosts thousands of code repositories online.
+To narrow down projects for our evaluation, we picked Github projects that met the following criteria:
+
+\begin{itemize}
+\item one of the top Trending projects\footnote{https://github.com/trending} on GitHub based on activity by the community at the time of this writing,
+\item primarily written in the Java programming language\footnote{https://java.com},
+\item owned by a Github organization instead of personal user accounts,
+\item and used Maven\footnote{https://maven.apache.org/} for software build management.
+\end{itemize}
+
+\begin{table}
+	\centering
+	\caption{Evaluation Projects}
+	\begin{tabular}{|l|l|l|c|}
+		\hline
+		\textbf{Project} & \textbf{Java Files} & \textbf{LOC} & \textbf{Pull Requests} \\
+		\hline
+		spring-boot\footnote{https://github.com/spring-projects/spring-boot.git} &  &  & \\
+		\hline
+		dubbo\footnote{https://github.com/alibaba/dubbo.git} &  &  & \\
+		\hline
+		guava\footnote{https://github.com/google/guava.git}  &  &  & \\
+		\hline
+		retrofit\footnote{https://github.com/square/retrofit.git}  &  &  & \\
+		\hline
+		rocketmq\footnote{https://github.com/apache/rocketmq.git}  &  &  & \\
+		\hline
+		\end{tabular}
+	\begin{tablenotes}
+        \item[1] Details on projects used for study including GitHub repository name, number of Java files, lines of Java code, and total pull requests.
+    \end{tablenotes}
+	\label{tools}
+\end{table}
+
+Table~\ref{tools} presents the projects used for evaluating \tool in our study and provides details about each repository.
+These repositories span a wide range of organizations and real-world software applications, including a system to create ``stand-alone, production-grade'' Spring applications~\cite{spring-boot}, a high-performance remote procedure call framework from Chinese e-commerce company Alibaba~\cite{dubbo}, a collection of core Google libraries~\cite{guava}, an HTTP client for Android financial services mobile application Square~\cite{square-retrofit}, and a distributed messaging and data-streaming platform by Apache~\cite{rocketmq}.
 
@@
 
+\subsection{Observations}
+
 \subsection{Implications}
@@
 
-\subsection{Threats to Validity}
+\section{Limitations}
 
-Internal:
+Internal\\
 
-External: Java, open vs. closed source, Error Prone,
+An external threat to the validity of our study is that we only observed open source projects hosted on Github in our evaluation.
+Our results may not generalize to closed source software projects and their developers.
+To minimize this, we selected popular real-world software applications on Github owned by organizations to avoid the use of personal development projects.
+Additionally, our recommendation system has limited generalizablility due to the fact we currently only assess recommendations for the Error Prone static analysis tool on Java projects that build with Maven.
+Future work will look to extend \tool to include different types of tools, programming languages, and build systems.
 
-\subsection{Future Work}
+\section{Future Work}
 
@@
 \section{Conclusion}
+
+\tool is awesome
 

### 2017-11-08 com/chbrown13/pull_rec/Error.java
Pushing updated version to test build

@@ -14,7 +14,7 @@ public class Error {
 	public Error(String name, String path, String line, String error, String msg, String log) {
 		String project = Utils.getProjectName();
 		String realPath = path.replace(project+"1", project).replace(project+"2", project);
-		this.key = String.join(":", realPath, line, error);
+		this.key = String.join(":", realPath, error);
 		this.filename = name;
 		this.filepath = path;
 		this.line = Integer.parseInt(line);

### 2017-11-08 com/chbrown13/pull_rec/ErrorProne.java

@@ -16,7 +16,8 @@ public class ErrorProne extends Tool {
 			"<artifactId>maven-compiler-plugin</artifactId>\n" +
 			"<version>3.3</version>\n" +
 			"<configuration>\n" +
-	  		"<compilerId>javac-with-errorprone</compilerId>\n" +
+			"<compilerId>javac-with-errorprone</compilerId>\n" +
+			"<forceJavacCompilerUse>true</forceJavacCompilerUse>\n" +
 			"<showWarnings>true</showWarnings>\n" +
 			"<compilerArgs>\n" +
 			"<arg>-XepAllErrorsAsWarnings</arg>\n" +
@@ -86,7 +87,6 @@ public class ErrorProne extends Tool {
 				}
 				String errorMessage = error[3];
 				temp = new Error(errorFileName, errorFilePath, errorLine, errorProne, errorMessage, "");
-				temp.addLog(line);
 			} else if (temp != null) {
 				temp.addLog(line);
 			}

### 2017-11-08 com/chbrown13/pull_rec/PullRecommender.java

@@ -42,7 +42,7 @@ public class PullRecommender {
 	 * Checks if the change is actually a fix or not
 	 */
 	private boolean isFix(Set<Error> base, Set<Error> pull, Error error) {
-		if (base.size() == 0 || pull.size() == 0 || base.size() == pull.size()) {
+		if (base.size() == 0 || pull.size() == 0) {
 			return false;
 		}
 		return Utils.isFix(error);
@@ -67,8 +67,10 @@ public class PullRecommender {
 				fixed.addAll(baseErrors);				
 				fixed.removeAll(pullErrors);
 				int i = 0;
+				System.out.println(baseErrors.size());
+				System.out.println(pullErrors.size());
+				System.out.println(fixed.size());
 				for (Error e: fixed) {
-					//System.out.println(e.getKey());
 					if (isFix(baseErrors, pullErrors, e)) {
 						System.out.println("Fixed "+ e.getKey() +" in PR #"+Integer.toString(pull.number())+" "+pull.title());
 						makeRecommendation(tool, pull, e, pullHash, Utils.getFix(), baseErrors);

### 2017-11-08 com/chbrown13/pull_rec/Utils.java

@@ -11,8 +11,10 @@ import com.github.gumtreediff.tree.*;
 import java.io.*;
 import java.lang.*;
 import java.net.*;
+import java.nio.file.*;
 import java.util.*;
 import javax.xml.parsers.*;
+import org.apache.commons.io.FileUtils;
 import org.eclipse.jgit.api.Git;
 import org.eclipse.jgit.api.errors.JGitInternalException;
 import org.eclipse.jgit.api.ResetCommand.ResetType;
@@ -272,7 +274,10 @@ public class Utils {
 				closestAction = a;
 			}
 		}
-		if (deleteOnly || insertOnly) {
+		if (deleteOnly) {
+			return -1;
+		}
+		if (insertOnly) {
 			return -1;
 		}
 		ITree temp = null;
@@ -311,10 +316,36 @@ public class Utils {
 	public static boolean isFix(Error error) {
 		String file1 = error.getFilePath();
 		String file2 = file1.replace(projectName + "1", projectName+"2");
-		if (!(new File(file1).isFile()) || !(new File(file2).isFile())) {
-			System.out.println("No file");
+		boolean noChange = false;
+		String content1 = "";
+		String content2 = "";
+		File base = new File(file1);
+		File pull = new File(file2);
+		if (!base.isFile() || !pull.isFile()) {
 			return false;
+		} else {
+			try {
+				noChange = FileUtils.contentEquals(base, pull);	
+				content1 = new String(Files.readAllBytes(Paths.get(file1)));
+				content2 = new String(Files.readAllBytes(Paths.get(file2)));			
+			} catch (IOException e) {
+				e.printStackTrace();
+				return false;
+			}
+			if (noChange || content1.equals(content2)) {
+				return false;
+			}
 		}
+		/*if(file1.contains("ProviderServiceImpl.java")) {
+			System.out.println(file1+" "+noChange);
+			try{
+				
+				System.out.println(content1);
+				System.out.println(content2);				
+			} catch (Exception e) {
+				e.printStackTrace();
+			}
+		}*/
 		return findFix(file1, file2, getErrorOffset(error, file1)) > 0;
 	}
 
@@ -338,7 +369,6 @@ public class Utils {
 			e.printStackTrace();
 			return null;
 		}
-		//System.out.println(output);
 		return output;
 	}
 
@@ -438,6 +468,7 @@ public class Utils {
 			dirName += "2";
 			owner = author;
 		}
[…]

### 2017-11-08 com/chbrown13/pull_rec/PullRecommender.java
Updates to printing for jenkins

@@ -67,9 +67,6 @@ public class PullRecommender {
 				fixed.addAll(baseErrors);				
 				fixed.removeAll(pullErrors);
 				int i = 0;
-				System.out.println(baseErrors.size());
-				System.out.println(pullErrors.size());
-				System.out.println(fixed.size());
 				for (Error e: fixed) {
 					if (isFix(baseErrors, pullErrors, e)) {
 						System.out.println("Fixed "+ e.getKey() +" in PR #"+Integer.toString(pull.number())+" "+pull.title());

### 2017-11-08 com/chbrown13/pull_rec/Utils.java

@@ -336,16 +336,8 @@ public class Utils {
 				return false;
 			}
 		}
-		/*if(file1.contains("ProviderServiceImpl.java")) {
-			System.out.println(file1+" "+noChange);
-			try{
-				
-				System.out.println(content1);
-				System.out.println(content2);				
-			} catch (Exception e) {
-				e.printStackTrace();
-			}
-		}*/
+		System.out.println(content1);
+		System.out.println(content2);
 		return findFix(file1, file2, getErrorOffset(error, file1)) > 0;
 	}
 

### 2017-11-08 com/chbrown13/pull_rec/Utils.java
Fix typo in Utils

@@ -460,7 +460,7 @@ public class Utils {
 			dirName += "2";
 			owner = author;
 		}
-		System.out.println(dirName+" "+author+" "+hash);
+		System.out.println(dirName+" "+owner+" "+hash);
 		try {
 			Git git = Git.cloneRepository()
 			.setURI("https://github.com/{owner}/{repo}.git".replace("{owner}", owner)

### 2017-11-13 com/chbrown13/pull_rec/Utils.java
Adding credential provider
Attempt to fix 
org.eclipse.jgit.api.errors.TransportException: https://github.com/vsair/rocketmq.git: Authentication is required but no CredentialsProvider has been registered
	at org.eclipse.jgit.api.FetchCommand.call(FetchCommand.java:250)
	at org.eclipse.jgit.api.CloneCommand.fetch(CloneCommand.java:304)
	at org.eclipse.jgit.api.CloneCommand.call(CloneCommand.java:201)
	at com.chbrown13.pull_rec.Utils.checkout(Utils.java:486)
	at com.chbrown13.pull_rec.PullRecommender.analyze(PullRecommender.java:64)
	at com.chbrown13.pull_rec.PullRecommender.main(PullRecommender

@@ -15,11 +15,12 @@ import java.nio.file.*;
 import java.util.*;
 import javax.xml.parsers.*;
 import org.apache.commons.io.FileUtils;
-import org.eclipse.jgit.api.Git;
+import org.eclipse.jgit.api.*;
 import org.eclipse.jgit.api.errors.JGitInternalException;
 import org.eclipse.jgit.api.ResetCommand.ResetType;
 import org.eclipse.jgit.lib.Repository;
 import org.eclipse.jgit.storage.file.FileRepositoryBuilder;
+import org.eclipse.jgit.transport.*;
 import org.xml.sax.*;
 import org.xml.sax.helpers.DefaultHandler;
 
@@ -483,6 +484,7 @@ public class Utils {
 			Git git = Git.cloneRepository()
 			.setURI("https://github.com/{owner}/{repo}.git".replace("{owner}", owner)
 				.replace("{repo}", projectName))
+			.setCredentialsProvider(new UsernamePasswordCredentialsProvider("tool-recommender-bot", "bot-recommender-tool"))
 			.setDirectory(new File(dirName)).call();
 			git.checkout().setName(hash).call();
 		} catch (Exception e) {

### 2017-11-14 paper/paper.tex
Updates to Tool section of paper

@@
 \raggedbottom
-\newcommand{\tool}{tool-recommender-bot }
+\newcommand{\tool}{tool-recommender-bot}
+\newcommand{\pseudosection}[1]{\vspace{2mm} \noindent {\bf #1}}
+\newcommand{\pseudosubsection}[1]{\vspace{2mm} {\it #1}}
+
 \begin{document}
@@
 Recommendation systems were developed to improve the adoption of useful software tools and features designed to save time and effort in completing tasks that are often ignored by users.
-Previous research suggests that peer-to-peer recommendations are the most effective mode of tool discovery and that the receptiveness of recommendees is the most important characteristic in determining the outcome of tool recommendations.
-To help increase awareness of useful tools, we developed and evaluated a new recommendation system \tool designed to integrate aspects of peer interactions and user receptivity into automated tool suggestions for software developers of real-world applications.
-Our findings suggest that \tool is awesome, cool, and very effective in improving tool discovery.
+Previous research suggests that peer-to-peer recommendations is an effective mode of tool discovery, and the receptiveness of recommendees is a vital characteristic in determining the outcome of tool suggestions.
+To help increase awareness of useful tools, we developed and evaluated a new system \tool~designed to integrate aspects of peer interactions and user receptivity into automated tool recommendations for software developers of real-world applications.
+Our findings suggest that \tool~is awesome, cool, and very effective in improving tool discovery.
+%Software quality is a primary concern of software engineers and users, however developers often ignore useful tools to improve quality and ease debugging for programmers.
 \end{abstract}
@@
 
-We created \tool to solve this... \\
+We created \tool~to solve this... \\
 
 \noindent
-\textbf{RQ1:} How often can we expect \tool to make recommendations?  \\
-\textbf{RQ2:} How useful are recommendations from \tool to developers?  \\
+\textbf{RQ1:} How often can we expect \tool~to make recommendations?  \\
+\textbf{RQ2:} How useful are recommendations from \tool~to developers?  \\
 
-To answer these questions, we conducted a study analyzing \tool on five?
+To answer these questions, we conducted a study analyzing \tool~on five?
 popular open source Java projects to observe how many tool suggestions would be made based on past changes to the code base and how software developers reacted to receiving recommendations.
@@
 \begin{itemize}
-\item We introduce the design and implementation of a novel automated recommendation system \tool
+\item We introduce the design and implementation of a novel automated recommendation system \tool~
 \item We provide implications for future
@@
 
-Existing automated tool recommendation systems...
+Existing automated tool recommendation systems...\\
+
+Improving awareness of software engineering tools...\\
 
 \section{Tool}
-\tool is awesome. Here's how...
+Our approach, \tool, aims to increase awareness of useful programming tools to software engineers. This section describes the design and implementation of our system.
+
+\subsection{Design}
+Previous research shows that recommendations between peers is an effective way to increase tool discovery and adoption~\cite{Murphy-HillPeerInteraction}.
+Many automated help systems are designed to simulate user-to-user recommendations in order to increase awareness of application tools and features, for instance Microsoft's intelligent office assistant Clippy.
+To better understand what makes peer interactions an effective mode of tool discovery, our prior work observed how colleagues recommend tools to each other while working on tasks.
+We found that \emph{receptiveness} has a significant outcome of a tool recommendation, while other interaction characteristics such as politeness or persuasiveness did no impact effectivenesst~\cite{vlhcc17}.
+
+\pseudosection{Receptiveness}
+
+Previous work emphasizes the importance of receptivity.
+Fogg outlined best practicies for creating persuasive technology to change user behavior, and argued designers must choose a receptive audience~\cite{FoggPersuasive}.
+He defines receptiveness using two criteria: 1) demonstrating a desire to adopt the target behavior and 2) familiarity with the technology.
+Below we present how \tool~integrates each of these concepts and how they influence the design of the system.
+
+\pseudosubsection{1. Desire}
+
+Software has permeated every area of our society.
+The primary desire of software users is to have enjoyable and problem-free experiences with software.
+The developers of these applications also have similar desires, to create high-quality and functioning programs for users.
+A 2002 study by the National Institute of Standards and Technology revealed that software engineers demonstrate this desire by spending the majority of the software development process and 70-80\% of their time testing and debugging code~\cite{NIST}.
+To aid developers in finding, fixing, and preventing various issues in code, many different types of tools have been created to help save time and effort in completing these tasks.
+We aim to increase awareness of these tools and improve software developer productivity by automatically making recommendations to capitalize on user and programmer desires to have mistake-free software.
+
+To target this desire, our initial implementation automatically recommends \textsc{Error Prone}, a static analysis tool created by Google to check for errors in Java code based on a suite of bug patterns.\footnote{http://errorprone.info} Static analysis tools can improve software quality by automatically inspecting code without running the program.
+These tools are useful in debugging and creating desireable applications, however they are often underutilized by software engineers~\cite{Johnson2013Why}.
+
+\pseudosubsection{2. Familiarity}
+
+Choosing an audience familiar with the target behavior is also vital to increasing adoption.
+To increase use of helpful programming tools, such as static analysis tools, our system focuses on making recommendations to software engineers in the projects they develop.
+Familiarity with source code is important for creating software applications, and code understandability is crucial for software development,  maintenance, debugging, and testing~\cite{ASE}.
+
+To choose a familiar audience, we make recommendations to developers of Java projects hosted on Github\footnote{https://github.com}, a popular source code management website that hosts millions of projects and serves millions of users.
+\tool~makes tool recommendations on pull requests, or proposed changes by contributors submitted to the source code.
+Developers making these changes should be knowledgeable about the project they are contributing to.
+Furthermore, our approach makes suggestions for tools when errors are fixed by the developer instead of reporting errors in their changes since pull request creators are familiar with the changes they are proposing to make to the source code.
+The GitHub interface allows users to review and comment on pull requests in situ with the proposed changes, and this is where we make our recommendations.
 
 \subsection{Implementation}
-\tool technical details...
 
-\subsubsection{Jenkins}
+\tool~builds on four key concepts to automatically recommend tools to users and improve tool discovery based on our design goals for receptivity.
 
-\subsubsection{Error Prone}
+\pseudosubsection{1. Continuous Integration}
 
-\subsection{Receptiveness}
-\tool was designed to integrate characteristics of peer interactions into automated recommendations.
-To better understand user-to-user recommendations and why they are effective for tool discovery, we observed how colleagues recommend tools to each other while completing tasks in prior work.
-Our results found that the receptiveness of users was the only significant indicator of determining whether a tool recommendation was effective or not compared to other interaction characteristics, such as politeness~\cite{vlhcc17}.
-Fogg defines receptiveness using two criteria, \textit{demonstrating a desire} and \textit{familiarity} with the adopted behavior~\cite{FoggPersuasive}.
+Our system utilizes continuous integration to recommend useful tools before pull request changes are integrated into the main repository, or merged.
+\tool~is implemented as a plugin for Jenkins, ``the leading open source automation server'' for source code deployment and delivery.\footnote{https://jenkins.io/} The system uses Jenkins to clone Github repositories and periodically check for newly-opened pull requests every 15 minutes.
+When a new pull request is found, our system uses Jenkins to automatically run our approach to recommend \textsc{Error Prone}.
 
-\paragraph{Desire}
+To analyze the source code, we target projects that use the Maven~\footnote{https://maven.apache.org/} build automation and software management tool for Java applications.
+Our approach uses Maven to automatically handle dependencies and perform the static analysis when the project builds.
+We inject \textsc{Error Prone} as a Maven plugin to repository's \textit{pom.xml} project object model file to add it to the build process.
+\tool~then builds both the original version of the code before the proposed changes were made (base) and the changed version of the repository with the pull request modifications implemented (head) to inspect differences.
+Using Maven allows \tool~to run on a large number of Java projects that use the popular build tool and also makes our approach extendable to recommend other tools implemented as Maven plugins in future work.
 
-\paragraph{Familiarity}
+\pseudosubsection{2. Fix Identification}
+
+After analyzing the base and head versions of the code, our approach parses the build output of each version to determine if any reported errors were fixed in the pull request.
+\textsc{Error Prone} identifies the faults and we developed an algorithm to use that information and determine if a fix to the identified bug was made.
+\tool~uses the code differencing tool GumTree to identify actions (addition, delete, insert, move, and update) performed to changed files in pull request versions and convert the code into symtax trees~\cite{GumTree}.
+
+To determine if an error was fixed, we take several things into consideration: First, our approach ignores instances where only delete actions were detected between the base and head versions of a file.
+This avoids making recommendations in situations where bugs were removed but not necessarily fixed in refactoring tasks, such as deleting and moving code, renaming classes, etc.
+Second, we ignore occurrences of deprecated classes because, similarly, the error reported was not fixed but removed.
+Third, we do not consider error fixes that were made by changes to a different file because we want to make recommendations where the developer is familiar with the changes that occurred.
+These help us minimize the number of false positives and errant recommendations in our approach.
+
+\pseudosubsection{3. Fix Localizaton}
+
+When a fix is identified in the pull request, \tool~then aims to find the location of the fix in the head version.
+To find the modified line that fixed a bug, we use GumTree to parse the Java file and convert it into abstract syntax trees.
+We look for the action closest to the offset of the error node calculated from the bug line number reported by \textsc{Error Prone}.
+If the closest action is not a delete, then our approach take the location takes the location of that action.
+Otherwise, if the line was removed our algorithm searches for the closest sibling node or if none exists then the location of the parent.
+
+\pseudosubsection{4. Code Review}
+
+Code reviews from developers are often required for examining code changes~\cite{?}.
+On Github, code reviews are primarily done through pull request comments~\cite{?}.
+Our approach simulates peer reviews by making recommendations for static analysis tools as a comment to the pull request.
+Github provides functionality for making comments at specific lines of code in a pull request, and \tool~recommends \textsc{Error Prone} as a comment at the fix location line from the previous step.
+Additionally, our system also aims to make recommendations using language similar to interactions between colleagues, such as complementing their work using ``Good job!''~\cite{?}.
+
+To further increase the adoption of static analysis tools, we report other instances of similar errors found by \textsc{Error Prone} in the base version of the code.
+In the recommendation, \tool~adds links to at most two locations where \textsc{Error Prone} found the same error as the one that was fixed.
+We hope this encourags the use of \textsc{Error Prone} to find more bugs in the pull request before the code is merged into the code base.
+Figure 1 presents a recommendation from our system on a pull request review.
 
@@
 
-To evaluate the effectiveness of our recommendation system, we implemented \tool on five real-world open-source software applications.
-We selected projects hosted on Github\footnote{https://github.com}, a popular source code management site that hosts thousands of code repositories online.
-To narrow down projects for our evaluation, we picked Github projects that met the following criteria:
+To evaluate the effectiveness of our recommendation system, we assessed \tool~on five real-world open-source software applications.
+To narrow down projects for our evaluation, we picked Github repositories that met the following criteria:
 
 \begin{itemize}
-\item one of the top Trending projects\footnote{https://github.com/trending} on GitHub based on activity by the community at the time of this writing,
+\item one of the top Trending projects\footnote{https://github.com/trending} on Github based on activity by the community at the time of this writing,
 \item primarily written in the Java programming language\footnote{https://java.com},
-\item owned by a Github organization instead of personal user accounts,
-\item and used Maven\footnote{https://maven.apache.org/} for software build management.
+\item build with Maven,
+\item and are owned by a GitHub organization, instead of personal user account projects.
 \end{itemize}
@@
 
-Table~\ref{tools} presents the projects used for evaluating \tool in our study and provides details about each repository.
+Table~\ref{tools} presents the projects used for evaluating \tool~in our study and provides details about each repository.
 These repositories span a wide range of organizations and real-world software applications, including a system to create ``stand-alone, production-grade'' Spring applications~\cite{spring-boot}, a high-performance remote procedure call framework from Chinese e-commerce company Alibaba~\cite{dubbo}, a collection of core Google libraries~\cite{guava}, an HTTP client for Android financial services mobile application Square~\cite{square-retrofit}, and a distributed messaging and data-streaming platform by Apache~\cite{rocketmq}.
@@
 
-\subsection{How often can we expect \tool to make recommendations?}
+\subsection{How often can we expect \tool~to make recommendations?}
 
@@
 
-\subsection{How useful are recommendations from \tool to developers?}
+\subsection{How useful are recommendations from \tool~to developers?}
 
@@
 Additionally, our recommendation system has limited generalizablility due to the fact we currently only assess recommendations for the Error Prone static analysis tool on Java projects that build with Maven.
-Future work will look to extend \tool to include different types of tools, programming languages, and build systems.
+Future work will look to extend \tool~to include different types of tools, programming languages, and build systems.
 

### 2017-11-14 paper/paper.tex
Updates to Tool section of paper

@@
 \section{Tool}
-Our approach, \tool, aims to increase awareness of useful programming tools to software engineers. This section describes the design and implementation of our system.
+Our approach to improving tool discovery, \tool, aims to increase awareness and use of programming tools among software developers. This section describes the design and implementation of our system.
 
@@
 Previous research shows that recommendations between peers is an effective way to increase tool discovery and adoption~\cite{Murphy-HillPeerInteraction}.
-Many automated help systems are designed to simulate user-to-user recommendations in order to increase awareness of application tools and features, for instance Microsoft's intelligent office assistant Clippy.
+Many automated help systems are designed to simulate user-to-user recommendations in order to increase awareness of application tools and features, for instance Microsoft's intelligent office assistant Clippy\cite{Clippy}.
+
 To better understand what makes peer interactions an effective mode of tool discovery, our prior work observed how colleagues recommend tools to each other while working on tasks.
-We found that \emph{receptiveness} has a significant outcome of a tool recommendation, while other interaction characteristics such as politeness or persuasiveness did no impact effectivenesst~\cite{vlhcc17}.
+Our results found that \emph{receptiveness} is a significant factor in determining the effectiveness of a tool recommendation, while other characteristics, such as politeness and persuasiveness, do not significantly impact the outcome~\cite{vlhcc17}.
+We designed \tool~to integrate user receptivity into our approach for making tool recommendations to increase awareness of programming tools.
 
@@
 Fogg outlined best practicies for creating persuasive technology to change user behavior, and argued designers must choose a receptive audience~\cite{FoggPersuasive}.
-He defines receptiveness using two criteria: 1) demonstrating a desire to adopt the target behavior and 2) familiarity with the technology.
-Below we present how \tool~integrates each of these concepts and how they influence the design of the system.
+Our prior work defined receptiveness using two criteria introduced by Fogg: 1) demonstrating a desire and 2) familiarity with the target behavior and technology.
+Below we explain how \tool~was designed to recommend programming tools to software developers based on their desire and familiarity.
 
@@
 
-Software has permeated every area of our society.
 The primary desire of software users is to have enjoyable and problem-free experiences with software.
-The developers of these applications also have similar desires, to create high-quality and functioning programs for users.
-A 2002 study by the National Institute of Standards and Technology revealed that software engineers demonstrate this desire by spending the majority of the software development process and 70-80\% of their time testing and debugging code~\cite{NIST}.
-To aid developers in finding, fixing, and preventing various issues in code, many different types of tools have been created to help save time and effort in completing these tasks.
-We aim to increase awareness of these tools and improve software developer productivity by automatically making recommendations to capitalize on user and programmer desires to have mistake-free software.
+Developers of these applications also have similar desires, to create high-quality and functioning programs for users.
+A 2002 study revealed that software engineers demonstrate this desire by spending the majority of the software development process and 70-80\% of their time testing and debugging code~\cite{NIST}.
+To aid developers in finding, fixing, and preventing various issues in code, many different types of tools have been created to help accomplish these tasks.
+However, despite the existence of effective tools for detecting errors, the number of bugs in software is increasing~\cite{HaveThingsChanged}.
+We aim to increase awareness of these tools to improve software quality and developer productivity, ultimately meeting users' and developers' desire for less buggy software.
 
-To target this desire, our initial implementation automatically recommends \textsc{Error Prone}, a static analysis tool created by Google to check for errors in Java code based on a suite of bug patterns.\footnote{http://errorprone.info} Static analysis tools can improve software quality by automatically inspecting code without running the program.
+To target this desire of mistake-free code, our initial implementation of \tool~automatically recommends \textsc{Error Prone}.\footnote{http://errorprone.info} \textsc{Error Prone} is a static analysis tool created by Google to check for errors in Java code based on a suite of bug patterns.
+Static analysis tools can improve software quality by automatically inspecting code without running the program.
 These tools are useful in debugging and creating desireable applications, however they are often underutilized by software engineers~\cite{Johnson2013Why}.
@@
 Choosing an audience familiar with the target behavior is also vital to increasing adoption.
-To increase use of helpful programming tools, such as static analysis tools, our system focuses on making recommendations to software engineers in the projects they develop.
-Familiarity with source code is important for creating software applications, and code understandability is crucial for software development,  maintenance, debugging, and testing~\cite{ASE}.
+To increase use of helpful programming tools, such as static analysis tools, our system focuses on making recommendations to software engineers within the context of the projects they develop.
+Familiarity with source code is important for creating software applications, and code understandability is one of the most important factors for software development, maintenance, debugging, and testing~\cite{Understandability}.
 
-To choose a familiar audience, we make recommendations to developers of Java projects hosted on Github\footnote{https://github.com}, a popular source code management website that hosts millions of projects and serves millions of users.
-\tool~makes tool recommendations on pull requests, or proposed changes by contributors submitted to the source code.
-Developers making these changes should be knowledgeable about the project they are contributing to.
-Furthermore, our approach makes suggestions for tools when errors are fixed by the developer instead of reporting errors in their changes since pull request creators are familiar with the changes they are proposing to make to the source code.
+To choose a familiar audience, our approach makes recommendations on Github\footnote{https://github.com}, a popular source code management and version control website that hosts millions of projects and serves millions of users.
+\tool~makes its recommendations on pull requests, or proposed changes to source code submitted by programmers.
+Developers making these changes should be knowledgeable about the changes they propose as well as the code base to which they are contributing.
+Our approach suggests \textsc{Error Prone} when reported errors are fixed by developers in pull requests to capitalize on their familiarity with their modifications.
 The GitHub interface allows users to review and comment on pull requests in situ with the proposed changes, and this is where we make our recommendations.
@@
 
-\tool~builds on four key concepts to automatically recommend tools to users and improve tool discovery based on our design goals for receptivity.
+\tool~builds on four key concepts to automatically recommend tools to users and improve tool discovery based on our design goals for targeting developer receptivity.
 
@@
 After analyzing the base and head versions of the code, our approach parses the build output of each version to determine if any reported errors were fixed in the pull request.
-\textsc{Error Prone} identifies the faults and we developed an algorithm to use that information and determine if a fix to the identified bug was made.
-\tool~uses the code differencing tool GumTree to identify actions (addition, delete, insert, move, and update) performed to changed files in pull request versions and convert the code into symtax trees~\cite{GumTree}.
+\textsc{Error Prone} identifies faults found in the source code, and we developed an algorithm using that information to determine if changes made to the code in the head version fix the identified bug.
+Our technique uses the code differencing tool GumTree~\cite{GumTree} to identify actions (addition, delete, insert, move, and update) performed between pull request versions and parse the code to convert the text into abstract syntax trees.
 
@@
 
-Code reviews from developers are often required for examining code changes~\cite{?}.
-On Github, code reviews are primarily done through pull request comments~\cite{?}.
+Code reviews from co-workers are often standard practice in software development.
+Pull requests are the primary method of code contributions and code reviews on Github~\cite{PullRequestReview}.
 Our approach simulates peer reviews by making recommendations for static analysis tools as a comment to the pull request.
 Github provides functionality for making comments at specific lines of code in a pull request, and \tool~recommends \textsc{Error Prone} as a comment at the fix location line from the previous step.
-Additionally, our system also aims to make recommendations using language similar to interactions between colleagues, such as complementing their work using ``Good job!''~\cite{?}.
+Additionally, our system  uses language similar to comments between co-workers in recommendations, such as using ``Good job!'' to compliment developers on their work'~\cite{?}.
 

### 2017-11-15 com/chbrown13/pull_rec/PullRecommender.java
Updates for checking developers and attempt at git error

@@ -54,30 +54,45 @@ public class PullRecommender {
 	 * @return       Number of recommendations made
 	 */
 	private void analyze(Pull.Smart pull) {
-		Tool tool = new ErrorProne();
 		System.out.println("Analyzing PR #" + Integer.toString(pull.number()) + "...");
+		Tool tool = new ErrorProne();		
+		String developer = "";
+		boolean pullRec = true;
 		try {
-			String author = pull.json().getJsonObject("head").getJsonObject("user").getString("login");
-			String pullHash = pull.json().getJsonObject("head").getString("sha");
-			String baseHash = pull.json().getJsonObject("base").getString("sha");
-			Set<Error> baseErrors = Utils.checkout(baseHash, author, tool, true);
-			Set<Error> pullErrors = Utils.checkout(pullHash, author, tool, false);
-			if(baseErrors != null && pullErrors != null) {
-				Set<Error> fixed = new HashSet<Error>();				
-				fixed.addAll(baseErrors);				
-				fixed.removeAll(pullErrors);
-				int i = 0;
-				for (Error e: fixed) {
-					if (isFix(baseErrors, pullErrors, e)) {
-						System.out.println("Fixed "+ e.getKey() +" in PR #"+Integer.toString(pull.number())+" "+pull.title()
-							+ " at line " + Integer.toString(Utils.getFix()));
-						makeRecommendation(tool, pull, e, pullHash, Utils.getFix(), baseErrors);
-					} else {
-						removed += 1;
-					}
-				}	
+			Iterator<Commit> commits = pull.commits().iterator();
+			while (commits.hasNext()) {
+				Commit.Smart commit = new Commit.Smart(commits.next());
+				String dev = commit.json().getJsonObject("author").getString("name");
+				if (developer.isEmpty()) {
+					developer = dev;
+				} else if (dev != developer) {
+					pullRec = false;
+					System.out.println("multiple devs");
+				}
 			}
-			Utils.cleanup();
+			if (pullRec) {
+				String label = pull.json().getJsonObject("head").getString("label");
+				String pullHash = pull.json().getJsonObject("head").getString("sha");
+				String baseHash = pull.json().getJsonObject("base").getString("sha");
+				Set<Error> baseErrors = Utils.checkout(baseHash, label, pull.number(), tool, true);
+				Set<Error> pullErrors = Utils.checkout(pullHash, label, pull.number(), tool, false);
[…]

### 2017-11-15 com/chbrown13/pull_rec/Utils.java

@@ -47,7 +47,29 @@ public class Utils {
 	
 	private static String projectOwner = "";
 
+	private static String username = "";
+
+	private static String password = "";
+
 	private static int fixLine = -1;
+
+	/**
+	 * Stores current user's Github login
+	 *
+	 * @param name   Github account username
+	 */
+	public static void setUserName(String name) {
+		username = name;
+	}
+
+	/**
+	 * Stores current user's Github password
+	 *
+	 * @param pass   Github account password
+	 */
+	public static void setPassword(String pass) {
+		password = pass;
+	}
 
 	/**
 	 * Stores current project name.
@@ -469,27 +491,36 @@ public class Utils {
 	 * @param base   True if checking base repo, false if PR version
 	 * @return       Set errors reported from tool
 	 */
-	public static Set<Error> checkout(String hash, String author, Tool tool, boolean base) {
+	public static Set<Error> checkout(String hash, String ref, int id, Tool tool, boolean base) {
 		String dirName = projectName;
 		String owner = "";
+		String branch = "";
 		if(base) {
 			dirName += "1";
 			owner = projectOwner;
 		} else {
 			dirName += "2";
-			owner = author;
+			owner = ref.split(":")[0];
+			branch = ref.split(":")[1];
 		}
 		System.out.println(dirName+" "+owner+" "+hash);
 		try {
 			Git git = Git.cloneRepository()
-			.setURI("https://github.com/{owner}/{repo}.git".replace("{owner}", owner)
-				.replace("{repo}", projectName))
-			.setCredentialsProvider(new UsernamePasswordCredentialsProvider("tool-recommender-bot", "bot-recommender-tool"))
-			.setDirectory(new File(dirName)).call();
+				.setURI("https://github.com/{owner}/{repo}.git"
+					.replace("{owner}", owner).replace("{repo}", projectName))
+				.setCredentialsProvider(new UsernamePasswordCredentialsProvider(username, password))
+				.setDirectory(new File(dirName)).call();
 			git.checkout().setName(hash).call();
 		} catch (Exception e) {
-			e.printStackTrace();
-			return null;
+			if (!base) {
+				String cmd = "git --git-dir={dir}/.git fetch origin pull/{num}/head:{branch}; git --git-dir={dir}/.git checkout -f {branch}"
+					.replaceAll("\\{dir\\}", dirName)
+					.replaceAll("\\{branch\\}", branch)
[…]

### 2017-11-15 com/chbrown13/pull_rec/PullRecommender.java
Updates to commenting and fixed git checkout issue

@@ -33,9 +33,11 @@ public class PullRecommender {
 	 */
 	private void makeRecommendation(Tool tool, Pull.Smart pull, Error error, String hash, int line, Set<Error> errors) {
 		String comment = error.generateComment(tool, errors, hash);
-		System.out.println(comment);
-		recs += 1;
-		prs.add(pull.number());
+		if (comment != null) {
+			System.out.println(comment);
+			recs += 1;
+			prs.add(pull.number());
+		}
 	}
 
 	/**
@@ -47,6 +49,7 @@ public class PullRecommender {
 		}
 		return Utils.isFix(error);
 	}
+
 	/**
 	 * Analyze code of files in pull request and compare to master branch.
 	 *
@@ -59,7 +62,7 @@ public class PullRecommender {
 		String developer = "";
 		boolean pullRec = true;
 		try {
-			Iterator<Commit> commits = pull.commits().iterator();
+			/*Iterator<Commit> commits = pull.commits().iterator();
 			while (commits.hasNext()) {
 				Commit.Smart commit = new Commit.Smart(commits.next());
 				String dev = commit.json().getJsonObject("author").getString("name");
@@ -70,7 +73,7 @@ public class PullRecommender {
 					System.out.println("multiple devs");
 				}
 			}
-			if (pullRec) {
+			if (pullRec) {*/
 				String label = pull.json().getJsonObject("head").getString("label");
 				String pullHash = pull.json().getJsonObject("head").getString("sha");
 				String baseHash = pull.json().getJsonObject("base").getString("sha");
@@ -92,7 +95,7 @@ public class PullRecommender {
 					}	
 				}
 				Utils.cleanup();
-			}
+			//}
 		} catch (IOException e) {
 			e.printStackTrace();
 		}	

### 2017-11-20 paper/paper.tex
These are no longer the projects we will use

@@
 %Importance
-Tool discovery is a problem... \\
+Software contains many tools and features designed to make users more efficient and effective in their work.
+However, despite a wide availability of such useful tools many are often ignored or because users do not know of their existence.\\
 
@@
 		\hline
-		spring-boot\footnote{https://github.com/spring-projects/spring-boot.git} &  &  & \\
-		\hline
-		dubbo\footnote{https://github.com/alibaba/dubbo.git} &  &  & \\
-		\hline
-		guava\footnote{https://github.com/google/guava.git}  &  &  & \\
-		\hline
-		retrofit\footnote{https://github.com/square/retrofit.git}  &  &  & \\
-		\hline
-		rocketmq\footnote{https://github.com/apache/rocketmq.git}  &  &  & \\
-		\hline
+%		spring-boot\footnote{https://github.com/spring-projects/spring-boot.git} &  &  & \\
+%		\hline
+%		dubbo\footnote{https://github.com/alibaba/dubbo.git} &  &  & \\
+%		\hline
+%		guava\footnote{https://github.com/google/guava.git}  &  &  & \\
+%		\hline
+%		retrofit\footnote{https://github.com/square/retrofit.git}  &  &  & \\
+%		\hline
+%		rocketmq\footnote{https://github.com/apache/rocketmq.git}  &  &  & \\
+%		\hline
 		\end{tabular}
@@
 \end{table}
-
-Table~\ref{tools} presents the projects used for evaluating \tool~in our study and provides details about each repository.
-These repositories span a wide range of organizations and real-world software applications, including a system to create ``stand-alone, production-grade'' Spring applications~\cite{spring-boot}, a high-performance remote procedure call framework from Chinese e-commerce company Alibaba~\cite{dubbo}, a collection of core Google libraries~\cite{guava}, an HTTP client for Android financial services mobile application Square~\cite{square-retrofit}, and a distributed messaging and data-streaming platform by Apache~\cite{rocketmq}.
 

### 2017-11-20 paper/paper.tex
Start of introduction

@@
 Software contains many tools and features designed to make users more efficient and effective in their work.
-However, despite a wide availability of such useful tools many are often ignored or because users do not know of their existence.\\
+However, despite a wide availability of such useful tools, many are often ignored or underutilized because users do not know of their existence.
+The amount of tools provided by applications is also continuing to increase, making it more difficult for users to discover helpful tools.
+This lack of awareness can lead to wasted time and billions of wasted dollars each year.
 
-Automated recommendation systems can help solve this problem... \\
+One area where worker effectiveness and efficiency is extremely important is the software industry.
+Software has permeated nearly every facet of our society and.
+Additionally, defects and errors in software cost companies millions of dollars to fix.
 
-But existing recommendations systems are ineffective... \\
+Automated recommendation systems can help solve this problem...
 
-Peer interactions and receptiveness are effective~\cite{vlhcc17}... \\
+But existing recommendations systems are ineffective...
 
-We created \tool~to solve this... \\
+Peer interactions and receptiveness are effective~\cite{vlhcc17}...
+
+We created \tool~to solve this... To evaluate the effectiveness of our approach, we studied the following research questions (RQs): \\
 
@@
 
-To answer these questions, we conducted a study analyzing \tool~on five?
-popular open source Java projects to observe how many tool suggestions would be made based on past changes to the code base and how software developers reacted to receiving recommendations.
-This research makes the following contributions:\\
+To answer these questions, we evaluated our system on open source Java projects to observe how many tool suggestions would be made based on past changes to the code base and how software developers reacted to receiving recommendations.
+This research makes the following contributions:
 
 \begin{itemize}
-\item We introduce the design and implementation of a novel automated recommendation system \tool~
-\item We provide implications for future
+\item introduce the design and evaluation of \tool, a novel approach to improving tool discovery
+\item provide implications for designing effective automated recommendation systems.
 \end{itemize}

### 2017-11-20 paper/paper.tex
Intro updates

@@
 Our findings suggest that \tool~is awesome, cool, and very effective in improving tool discovery.
-%Software quality is a primary concern of software engineers and users, however developers often ignore useful tools to improve quality and ease debugging for programmers.
 \end{abstract}
@@
 Software contains many tools and features designed to make users more efficient and effective in their work.
-However, despite a wide availability of such useful tools, many are often ignored or underutilized because users do not know of their existence.
-The amount of tools provided by applications is also continuing to increase, making it more difficult for users to discover helpful tools.
-This lack of awareness can lead to wasted time and billions of wasted dollars each year.
+However, despite a wide availability of such useful tools, many are often ignored or underutilized because users do not know of their existence~\cite{?}.
+The amount of tools provided by applications is also continuing to increase, making it more difficult for users to discover these helpful tools~\cite{bloat}.
+This lack of awareness leads to wasted time and billions of wasted dollars each year~\cite{malachowski}.
 
@@
 Software has permeated nearly every facet of our society and.
-Additionally, defects and errors in software cost companies millions of dollars to fix.
+Additionally, defects and errors in software cost companies millions of dollars to fix~\cite{?}.
+Quality is a primary concern for both software engineers and software users, however developers often ignore useful tools to help improve the quality of their code.
 

### 2017-11-21 com/chbrown13/pull_rec/PullRecommender.java
Check for modified files

@@ -49,11 +49,19 @@ public class PullRecommender {
 	/**
 	 * Checks if the change is actually a fix or not
 	 */
-	private boolean isFix(Set<Error> base, Set<Error> pull, Error error) {
-		if (base.size() == 0) {
-			return false;
+	private boolean isFix(Set<Error> base, Set<Error> pull, Error error, List<String> files) {
+		boolean fileCheck = false;
+		for (String f: files) {
+			if (error.getFilePath().contains(f)) {
+				System.out.println("!!!!"+error.getFilePath()+"    "+f);
+				fileCheck = true;
+				break;
+			}
 		}
-		return Utils.isFix(error);
+		if (base.size() > 0 && fileCheck) {
+			return Utils.isFix(error);
+		}
+		return false;
 	}
 
 	/**
@@ -66,7 +74,26 @@ public class PullRecommender {
 		System.out.println("Analyzing PR #" + Integer.toString(pull.number()) + "...");
 		Tool tool = new ErrorProne();		
 		String developer = "";
-		boolean pullRec = true;
+		boolean pullRec = false;
+		List<String> javaFiles = new ArrayList<String>();
+		Iterator<JsonObject> files = null;
+		try {
+			files = pull.files().iterator();			
+		} catch (Exception e) {
+			e.printStackTrace();
+			return;
+		}
+		while (files.hasNext()) {
+			JsonObject f = files.next();
+			if (f.getString("filename").endsWith(".java") && f.getString("status").equals("modified")) {
+				javaFiles.add(f.getString("filename"));
+				pullRec = true;
+			}		
+		}
+		if (!pullRec) {
+			System.out.println("No java changes.");
+			return;
+		}
 		try {
 			Set<Error> baseErrors = Utils.checkout(pull, tool, true);
 			Set<Error> pullErrors = Utils.checkout(pull, tool, false);
@@ -76,7 +103,7 @@ public class PullRecommender {
 				fixed.removeAll(pullErrors);
 				int i = 0;
 				for (Error e: fixed) {
-					if (isFix(baseErrors, pullErrors, e)) {
+					if (isFix(baseErrors, pullErrors, e, javaFiles)) {
 						System.out.println("Fixed "+ e.getKey() +" in PR #"+Integer.toString(pull.number())
 							+ " reported at line " + e.getLineNumberStr() + " fixed at line " + Integer.toString(Utils.getFix()));
 						makeRecommendation(tool, pull, e, Utils.getFix(), baseErrors);

### 2017-11-21 com/chbrown13/pull_rec/Utils.java
Print out log too, just because

@@ -542,6 +542,7 @@ public class Utils {
 		}
 		addToolPomPlugin(dirName, tool);
 		String log = compile(dirName);
+		System.out.println(log);
 		return tool.parseOutput(log);
 	}
 

### 2017-11-28 paper/paper.tex
Intro updates

--- 2017-11-20 paper/paper.tex
@@
 \section{Introduction}
-%Importance
-Software contains many tools and features designed to make users more efficient and effective in their work.
-However, despite a wide availability of such useful tools many are often ignored or because users do not know of their existence.\\
 
-Automated recommendation systems can help solve this problem... \\
+Software has permeated nearly every area of our society.
+To keep up with the increasing demand for technology, software quality has become an increasingly important metric for software development teams.
+Processes such as peer code reviews, unit tests, continuous integration, test automation, and more have been implemented to ensure software maintains a high quality.
 
-But existing recommendations systems are ineffective... \\
+Despite increased attention to the quality of code, the process of finding and fixing bugs in software, or debugging, is becoming more time-consuming and costly.
+A study by the National Institute of Standards and Technology reported that software engineers spend 70-80\% of their time at work debugging, and on average it takes 17.4 hours to debug one error~\cite{NIST}.
+Additionally, these errors can cost companies millions of dollars.
+For example, a recent bug found in the cryptocurrency Ethereum resulted in the loss of \$30 million.\footnote{https://qz.com/1034321/ethereum-hack-a-coding-error-led-to-30-million-in-ethereum-being-stolen/}.
+Additionally, the price of repairing these code failures is becoming more expensive over time~\cite{SEEconomics}.
 
-Peer interactions and receptiveness are effective~\cite{vlhcc17}... \\
+To make software engineers more effective and efficient in their work, many types of tools have been created to automatically perform code analysis, refactoring, security checks, and more for programmers.
+One such type is static analysis tools.
+Static analysis tools can improve software quality by automatically inspecting code without running the program.
+These tools can be useful for finding code defects early in the development process before code is released.
+According to a report from IBM, the relative cost for fixing errors also drastically increases the longer the fault exists in the code base through the software development lifecycle.
+Previous studies also show that static analysis tools are effective in preventing bugs in code to save money for companies in addition to time and effort for developers~\cite{UsingStaticAnalysis}.
 
-We created \tool~to solve this... \\
+Althouth quality is a primary concern for software producers and consumers, developers often ignore these useful tools which help improve the quality of their code~\cite{Johnson2013Why}.
+There are many barriers to tool adoption, and one of the main reasons useful tools are ignored or underutilized is because of the discoverability barrier.
+This refers to when users are unaware of tools' existence in software~\cite{Murphy-HillScreencastingDiscovery}.
+This lack of awareness can lead to significant amounts of wasted time and money in the software industry.
+
+%Researchers have explored methods for increasing tool discovery among software users.
+Fischer suggests that some of the more popular methods for raising tool awareness, such as documentation and help menus, are ineffective for increasing adoption of useful tools and features~\cite{ActiveHelpSystems}.
+These \textit{passive help systems} require users to first recognize the system's existence, navigate to the items, and then manually search for help.
+However, users rarely seek help by discovering new functionality and will often just rely on their own previous knowledge~\cite{something}.
+%
+%Active help systems are the preferred method of helping users discover new functionality in software.
+These systems automatically recommend useful tools to software users.
+However, there remains room for improvement among these system-to-user recommendation systems.
+For example, Clippy, an intelligent office assistant for Microsoft Office products, was able to automatically suggest tools and features to Microsoft software users.
+However, the system was found ineffective and eventually removed.
+Peer interactions and receptiveness are effective~\cite{vlhcc17}...
+
+To solve the static analysis tool discovery problem, we developed a new recommender system called \textit{\tool}.
+\tool was designed to automatically recommend static analysis tools to software engineers.
+We designed our system to make suggestions by integrating characteristics of peer interactions and concepts from the software engineering industry.
+To evaluate the effectiveness of our system, we studied the following research questions (RQs): \\
 
@@
 
-To answer these questions, we conducted a study analyzing \tool~on five?
-popular open source Java projects to observe how many tool suggestions would be made based on past changes to the code base and how software developers reacted to receiving recommendations.
-This research makes the following contributions:\\
-
-\begin{itemize}
-\item We introduce the design and implementation of a novel automated recommendation system \tool~
-\item We provide implications for future
-\end{itemize}
+To answer these questions, we evaluated our system on open source Java projects to observe how many tool suggestions would be made based on past changes to the code base.
+We also examined how software developers reacted to receiving tool recommendations from our system.
+The main research contribution of our work is introducing the design and evaluation of a new automated recommendation system \tool, a novel approach to improving the discovery of static analysis tools for software engineers by simulating tool recommendations made between peers.
 
@@
 Previous research shows that recommendations between peers is an effective way to increase tool discovery and adoption~\cite{Murphy-HillPeerInteraction}.
-Many automated help systems are designed to simulate user-to-user recommendations in order to increase awareness of application tools and features, for instance Microsoft's intelligent office assistant Clippy\cite{Clippy}.
+Many automated help systems are designed to simulate user-to-user recommendations in order to increase awareness of application tools and features, for instance Microsoft Clippy\cite{Clippy}.
 
@@
 To target this desire of mistake-free code, our initial implementation of \tool~automatically recommends \textsc{Error Prone}.\footnote{http://errorprone.info} \textsc{Error Prone} is a static analysis tool created by Google to check for errors in Java code based on a suite of bug patterns.
-Static analysis tools can improve software quality by automatically inspecting code without running the program.
 These tools are useful in debugging and creating desireable applications, however they are often underutilized by software engineers~\cite{Johnson2013Why}.

### 2017-11-28 paper/paper.tex
1 page intro

@@
 Althouth quality is a primary concern for software producers and consumers, developers often ignore these useful tools which help improve the quality of their code~\cite{Johnson2013Why}.
-There are many barriers to tool adoption, and one of the main reasons useful tools are ignored or underutilized is because of the discoverability barrier.
-This refers to when users are unaware of tools' existence in software~\cite{Murphy-HillScreencastingDiscovery}.
-This lack of awareness can lead to significant amounts of wasted time and money in the software industry.
+There are many barriers to tool adoption, and one of the main reasons useful tools are ignored or underutilized is the discoverability barrier.
+This refers to when users are unaware of a tool's existence within software~\cite{Murphy-HillScreencastingDiscovery}.
+The tool discovery problem will continue to persist as applications become more ``bloated'' with features~\cite{SoftwareBloat}.
+This lack of awareness of static analysis tools can lead to significant amounts of wasted time and money in the software industry.
 
@@
 
-To solve the static analysis tool discovery problem, we developed a new recommender system called \textit{\tool}.
-\tool was designed to automatically recommend static analysis tools to software engineers.
+To solve the static analysis tool discovery problem, we developed a new recommender system called~\textit{\tool}.
+\tool~was designed to automatically recommend static analysis tools to software engineers.
+Previous research has shown that user-to-user recommendations, or peer interactions, are the most effective mode of increasing awareness of tools among software users~\cite{PeerInteraction}.
 We designed our system to make suggestions by integrating characteristics of peer interactions and concepts from the software engineering industry.

### 2017-11-28 paper/paper.tex
Adding IBM cite

@@
 These tools can be useful for finding code defects early in the development process before code is released.
-According to a report from IBM, the relative cost for fixing errors also drastically increases the longer the fault exists in the code base through the software development lifecycle.
+According to a report from IBM, the relative cost for fixing errors also drastically increases the longer the fault exists in the code base through the software development lifecycle~\cite{SoftwareAssuranceSDLC}.
 Previous studies also show that static analysis tools are effective in preventing bugs in code to save money for companies in addition to time and effort for developers~\cite{UsingStaticAnalysis}.

### 2017-11-28 com/chbrown13/pull_rec/PullRecommender.java
com/chbrown13/pull_rec/ErrorProne.java

@@ -17,6 +17,7 @@ public class PullRecommender {
 	private static int open = 0;
 	private static int pulls = 0;
 	private static int removed = 0;
+	private static int fixes = 0;
 
 	public PullRecommender(Repo repo) {
 		this.repo = repo;
@@ -53,7 +54,6 @@ public class PullRecommender {
 		boolean fileCheck = false;
 		for (String f: files) {
 			if (error.getFilePath().contains(f)) {
-				System.out.println("!!!!"+error.getFilePath()+"    "+f);
 				fileCheck = true;
 				break;
 			}
@@ -98,14 +98,16 @@ public class PullRecommender {
 			Set<Error> baseErrors = Utils.checkout(pull, tool, true);
 			Set<Error> pullErrors = Utils.checkout(pull, tool, false);
 			if(baseErrors != null && pullErrors != null) {
+				System.out.println(Integer.toString(baseErrors.size()) +"------"+Integer.toString(pullErrors.size()));				
 				Set<Error> fixed = new HashSet<Error>();				
 				fixed.addAll(baseErrors);				
 				fixed.removeAll(pullErrors);
 				int i = 0;
 				for (Error e: fixed) {
+					fixes += 1;
 					if (isFix(baseErrors, pullErrors, e, javaFiles)) {
 						System.out.println("Fixed "+ e.getKey() +" in PR #"+Integer.toString(pull.number())
-							+ " reported at line " + e.getLineNumberStr() + " fixed at line " + Integer.toString(Utils.getFix()));
+							+ " reported at line " + e.getLineNumberStr() + " possibly fixed at line " + Integer.toString(Utils.getFix()));
 						makeRecommendation(tool, pull, e, Utils.getFix(), baseErrors);
 					} else {
 						removed += 1;
@@ -140,6 +142,7 @@ public class PullRecommender {
 			requests.add(pull);
 			i++;
 			pulls++;
+			System.out.println(i);
 		}
 		return requests;
 	}
@@ -150,10 +153,11 @@ public class PullRecommender {
         Repo repo = github.repos().get(new Coordinates.Simple(args[0], args[1]));
 		PullRecommender recommender = new PullRecommender(repo);
 		ArrayList<Pull.Smart> requests = recommender.getPullRequests(Integer.parseInt(args[2]));
-		System.out.println("{recs} recommendations made on {pulls} pull request(s) out of {totals} total."
[…]

### 2017-11-28 com/chbrown13/pull_rec/Utils.java

@@ -518,31 +518,11 @@ public class Utils {
 				.setCloneAllBranches(true).call();
 			git.checkout().setName(hash).call();
 		} catch (Exception e) {
-			/*if (git != null && !base) {
-				try {
-					git.branchCreate().setName(branch)
-						.setUpstreamMode(SetupUpstreamMode.TRACK)
-						.call();
-					git.checkout().setName(branch).call();
-				} catch (RefAlreadyExistsException raee) {
-					try {
-						git.checkout().setName(branch).call();
-					} catch (Exception e2) {
-						e2.printStackTrace();
-						return null;
-					}
-				} catch (Exception e3) {
-					e3.printStackTrace();
-					return null;
-				}
-			} else {*/
-				e.printStackTrace();
-				return null;
-			//}
+			e.printStackTrace();
+			return null;
 		}
 		addToolPomPlugin(dirName, tool);
 		String log = compile(dirName);
-		System.out.println(log);
 		return tool.parseOutput(log);
 	}
 

### 2017-11-28 com/chbrown13/pull_rec/ErrorProne.java
Updates to stats tracked

@@ -59,7 +59,6 @@ public class ErrorProne extends Tool {
 	  */
 	@Override
 	public Set<Error> parseOutput(String msg) {
-		//System.out.println(msg+"...");
 		String regex = "^[\\w+/]*\\w.java\\:\\d+\\:.*\\:.*";
 		String dir = Utils.getCurrentDir();
 		String[] lines = msg.split("\n");

### 2017-11-29 com/chbrown13/pull_rec/Error.java
Merging updated code to master branch

@@ -1,0 +1,211 @@
+package com.chbrown13.pull_rec;
+
+import java.util.*;
+
+public class Error {
+    private String key;
+	private String filename;
+	private String filepath;
+	private int line;
+	private String error;
+	private String message;
+	private String log;
+
+	public Error(String name, String path, String line, String error, String msg, String log) {
+		String project = Utils.getProjectName();
+		String realPath = path.replace(project+"1", project).replace(project+"2", project);
+		this.key = String.join(":", realPath, error);
+		this.filename = name;
+		this.filepath = path;
+		this.line = Integer.parseInt(line);
+		this.error = error;
+		this.message = msg;
+		this.log = log;
+    }
+
+    /**
+	 * Gets static analysis output for current error
+	 *
+	 * @return   Error message
+	 */
+	public String getLog() {
+		return this.log;
+	}
+	
+	/**
+	 * Appends output to the log.
+	 *
+ 	 * @param log   Message to add to log
+	 */
+	public void addLog(String log) {
+		this.log += "\n"+log;
+	}
+	
+	/**
+	 * Gets key to uniquely identify errors
+	 *
+	 * @return   String key for error
+	 */
+	public String getKey() {
+		return this.key;
+	}
+
+	/**
+	 * Gets filepath to where error was reported.
+	 *
+ 	 * @return   String filepath
+	 */
+	public String getFilePath() {
+		return this.filepath;
+    }
+    
+    /**
+	 * Gets the local filepath to where error was reported in the project.
+	 *
+ 	 * @return   String filepath
+	 */
+	public String getLocalFilePath() {
+        String path = this.filepath.replace(Utils.getCurrentDir() + "/", "");
+        return path.substring(path.indexOf("/") + 1);
+	}
+
+	/**
+	 * Sets the filepath for error.
+	 *
+	 * @param path   Filepath to error
+	 */
+	public void setFilePath(String path) {
+		this.filepath = path;
+	}
+
+	/**
+	 * Gets filename of file containing error reported.
+	 *
+ 	 * @return   String filepath
+	 */
+	public String getFileName() {
+		return this.filename;
+	}
+
+	/**
+	 * Sets the filename for error.
+	 *
+	 * @param path   Filename of file with error
+	 */
+	public void setFileName(String file) {
+		this.filename = file;
+	}
+
+	/**
+	 * Gets the error message from static analysis output.
+	 *
[…]

### 2017-11-29 com/chbrown13/pull_rec/ErrorProne.java

@@ -1,0 +1,121 @@
+package com.chbrown13.pull_rec;
+
+//import com.google.errorprone.*;
+//import com.sun.tools.javac.main.Main.Result;
+import java.io.*;
+import java.util.*;
+
+/**
+ * The ErrorProne class contains methods concerning the ErrorProne static analysis tool and an object storing information for a bug reported.
+ */
+public class ErrorProne extends Tool {
+	
+	private final String RUN_CMD = "java -Xbootclasspath/p:error_prone_ant-2.1.0.jar com.google.errorprone.ErrorProneCompiler {file}";	
+	private final String MAVEN = "<plugin>\n"+
+			"<groupId>org.apache.maven.plugins</groupId>\n" +
+			"<artifactId>maven-compiler-plugin</artifactId>\n" +
+			"<version>3.3</version>\n" +
+			"<configuration>\n" +
+			"<compilerId>javac-with-errorprone</compilerId>\n" +
+			"<forceJavacCompilerUse>true</forceJavacCompilerUse>\n" +
+			"<showWarnings>true</showWarnings>\n" +
+			"<compilerArgs>\n" +
+			"<arg>-XepAllErrorsAsWarnings</arg>\n" +
+			"</compilerArgs>\n" +
+	  		"<source>8</source>\n" +
+	  		"<target>8</target>\n" +
+			"</configuration>\n" +
+			"<dependencies>\n" +
+	  		"<dependency>\n" +
+			"<groupId>org.codehaus.plexus</groupId>\n" +
+			"<artifactId>plexus-compiler-javac-errorprone</artifactId>\n" +
+			"<version>2.8</version>\n" +
+	  		"</dependency>\n" +
+	  		"<dependency>\n" +
+			"<groupId>com.google.errorprone</groupId>\n" +
+			"<artifactId>error_prone_core</artifactId>\n" +
+			"<version>2.1.2</version>\n" +
+	  		"</dependency>\n" +
+			"</dependencies>\n" +
+  			"</plugin>";
+
+	public ErrorProne() {
+		super("Error Prone", "static analysis tool", "http://errorprone.info");
+	}
+
+	/**
+	 * Returns the Error Prone maven plugin for build
+	 */
+	@Override
+	public String getPlugin() {
+		return this.MAVEN;
+	}
+	
+	/**
+	 * Parses output from ErrorProne static analysis of code and creates objects.
+	 *
+	 * @param msg    ErrorProne output
+	 * @return       List of ErrrorProne
+	  */
+	@Override
[…]

### 2017-11-29 com/chbrown13/pull_rec/ErrorProneItem.java

@@ -1,333 +1,0 @@
-package com.chbrown13.pull_rec;
-
-//import com.google.errorprone.*;
-//import com.sun.tools.javac.main.Main.Result;
-import java.io.*;
-import java.util.*;
-
-/**
- * The ErrorProneItem class contains methods concerning the ErrorProne static analysis tool and an object storing information for a bug reported.
- */
-public class ErrorProneItem {
-
-	private String key;
-	private String filename;
-	private String filepath;
-	private int line;
-	private String error;
-	private String message;
-	private String log;
-	private String commit;
-	private List<ErrorProneItem> similar;
-
-	public ErrorProneItem(String name, String path, String line, String error, String msg, String hash, String log) {
-		this.key = String.join(":", path, line, error);
-		this.filename = name;
-		this.filepath = path;
-		this.line = Integer.parseInt(line);
-		this.error = error;
-		this.message = msg;
-		this.commit = hash;
-		this.log = log;
-		this.similar = new ArrayList<ErrorProneItem>();
-	}
-
-	/**
-	 * Creates comment to recommend ErrorProne for a Github pull request.
-	 *
-	 * @return   Message containing the fixed error and other similar errors found
-	 */
-	public String generateComment() {
-		String comment = Utils.BASE_COMMENT;
-		String simSentence = " Error Prone also found similar issues in {link}. ";
-		comment = comment.replace("{fixed}", "```" + this.log.substring(this.log.indexOf("_")+1) + "```");
-		Set<String> simSet = new HashSet<String>();
-		for (ErrorProneItem e: this.similar) {
-			simSet.add(e.getKey());
-		}
-		if (simSet.isEmpty()) {
-			comment = comment.replace("{similar}", " ");
-		} else if (simSet.size() == 1) {
-			comment = comment.replace("{similar}", simSentence.replace("{link}", getErrorLink(simSet.iterator().next())));
-		} else {
-			Iterator<String> it = simSet.iterator();
-			comment = comment.replace("{similar}", simSentence.replace("{link}", String.join(" and ", getErrorLink(it.next()), getErrorLink(it.next()))));
-		}
-		return comment;
-	}
-
-	/**
-	 * Gets errors similar to the current error.
-	 *
-	 * @return   List of other ErrorProneItems with the same error
-	 */
[…]

### 2017-11-29 com/chbrown13/pull_rec/PullRecommender.java

@@ -12,6 +12,12 @@ import javax.json.JsonObject;
 public class PullRecommender {
 
 	private Repo repo;
+	private static Set<Integer> prs = new HashSet<Integer>();	
+	private static int recs = 0;;
+	private static int open = 0;
+	private static int pulls = 0;
+	private static int removed = 0;
+	private static int fixes = 0;
 
 	public PullRecommender(Repo repo) {
 		this.repo = repo;
@@ -26,14 +32,34 @@ public class PullRecommender {
 	 * @param pull	 	Pull request to comment on
 	 * @param error     Error fixed in pull request
 	 */
-	private void makeRecommendation(Pull.Smart pull, ErrorProneItem error, String sha, int line) {
+	private void makeRecommendation(Tool tool, Pull.Smart pull, Error error, int line, Set<Error> errors) {
 		try {
-			String comment = error.generateComment();
-			PullComments pullComments = pull.comments();	
-			PullComment.Smart smartComment = new PullComment.Smart(pullComments.post(comment, sha, error.getFilePath(), line));	
+			String sha = pull.json().getJsonObject("head").getString("sha");
+			String comment = error.generateComment(tool, errors, sha);
+			System.out.println(comment);
+			PullComments pullComments = pull.comments();
+			PullComment.Smart smartComment = new PullComment.Smart(pullComments.post(comment, sha, error.getLocalFilePath(), line));	
+			recs += 1;
 		} catch (IOException e) {
 			e.printStackTrace();
 		}
+	}
+
+	/**
+	 * Checks if the change is actually a fix or not
+	 */
+	private boolean isFix(Set<Error> base, Set<Error> pull, Error error, List<String> files) {
+		boolean fileCheck = false;
+		for (String f: files) {
+			if (error.getFilePath().contains(f)) {
+				fileCheck = true;
+				break;
+			}
+		}
+		if (base.size() > 0 && fileCheck) {
+			return Utils.isFix(error);
+		}
+		return false;
 	}
 
 	/**
@@ -44,41 +70,52 @@ public class PullRecommender {
 	 */
 	private void analyze(Pull.Smart pull) {
 		System.out.println("Analyzing PR #" + Integer.toString(pull.number()) + "...");
+		Tool tool = new ErrorProne();		
+		String developer = "";
+		boolean pullRec = false;
+		List<String> javaFiles = new ArrayList<String>();
[…]

### 2017-11-29 com/chbrown13/pull_rec/Tool.java

@@ -1,0 +1,42 @@
+package com.chbrown13.pull_rec;
+
+import java.util.*;
+
+public abstract class Tool {
+
+    private final String MAVEN = "";
+    private String name;
+    private String desc;
+    private String link;
+
+    public Tool (String name, String desc, String link) {
+        this.name = name;
+        this.desc = desc;
+        this.link = link;
+    }
+
+    /**
+	 * Returns the name of the current tool.
+	 */
+    public String getName() {
+        return this.name;
+    }
+
+    /**
+	 * Returns the description of the current tool.
+	 */
+    public String getDescription() {
+        return this.desc;
+    }
+
+    /**
+	 * Returns the URL for the current tool.
+	 */
+    public String getLink() {
+        return this.link;
+    }
+
+    public abstract String getPlugin();
+    
+    public abstract Set<Error> parseOutput(String log);
+}

### 2017-11-29 com/chbrown13/pull_rec/Utils.java

@@ -6,12 +6,26 @@ import com.github.gumtreediff.client.Run;
 import com.github.gumtreediff.gen.*;
 import com.github.gumtreediff.gen.jdt.JdtTreeGenerator;
 import com.github.gumtreediff.matchers.*;
-import com.github.gumtreediff.matchers.heuristic.LcsMatcher;
+import com.github.gumtreediff.matchers.heuristic.gt.*;
 import com.github.gumtreediff.tree.*;
+import com.jcabi.github.Pull;
 import java.io.*;
 import java.lang.*;
 import java.net.*;
+import java.nio.file.*;
 import java.util.*;
+import javax.json.*;
+import javax.xml.parsers.*;
+import org.apache.commons.io.FileUtils;
+import org.eclipse.jgit.api.*;
+import org.eclipse.jgit.api.CreateBranchCommand.SetupUpstreamMode;
+import org.eclipse.jgit.api.errors.*;
+import org.eclipse.jgit.api.ResetCommand.ResetType;
+import org.eclipse.jgit.lib.Repository;
+import org.eclipse.jgit.storage.file.FileRepositoryBuilder;
+import org.eclipse.jgit.transport.*;
+import org.xml.sax.*;
+import org.xml.sax.helpers.DefaultHandler;
 
 /**
  * The Utils class contains various helper methods and variables for the PullRecommender project.
@@ -22,13 +36,43 @@ public class Utils {
 
 	public static String LINK_URL = "https://github.com/{user}/{repo}/blob/{sha}/{path}#L{line}";
 
-	public static String BASE_COMMENT = "Good job! The static analysis tool Error Prone reported an error [1] used to be here, but you fixed it.{similar}Check out http://errorprone.info for more information.\n\n\n[1] {fixed}";
+	public static String RAW_URL = "https://raw.githubusercontent.com/{user}/{repo}/{sha}/{path}";
 
-	public static String ERROR_PRONE_CMD = "java -Xbootclasspath/p:error_prone_ant-2.1.0.jar com.google.errorprone.ErrorProneCompiler {file}";
-	
+	public static String BASE_COMMENT = "Good job! The {desc} {tool} reported an error [1] used to be here, but you fixed it.{similar}Check out {link} for more information.\n\n\n[1] {fixed}";
+
+	private static String MVN_COMPILE = "mvn -q -f {dir}/pom.xml compile";
+
+	private static String currentDir = System.getProperty("user.dir");
+
+	private static boolean myTool = false;
+
[…]

### 2017-11-29 com/chbrown13/pull_rec/PullRecommender.java
Fixing time issue

@@ -15,7 +15,6 @@ public class PullRecommender {
 	private static Set<Integer> prs = new HashSet<Integer>();	
 	private static int recs = 0;;
 	private static int open = 0;
-	private static int pulls = 0;
 	private static int removed = 0;
 	private static int fixes = 0;
 
@@ -124,7 +123,7 @@ public class PullRecommender {
 	 *
 	 * @return   List of new pull requests
 	 */
-	private ArrayList<Pull.Smart> getPullRequests(int num) {
+	private ArrayList<Pull.Smart> getPullRequests() {
 		System.out.println("Getting pull requests...");
 		ArrayList<Pull.Smart> requests = new ArrayList<Pull.Smart>();
 		Map<String, String> params = new HashMap<String, String>();
@@ -132,15 +131,19 @@ public class PullRecommender {
 		Iterator<Pull> pullit = this.repo.pulls().iterate(params).iterator();
 		int i = 0;
 		while (pullit.hasNext()) {
-			if (i >= num) {
-				break;
-			}
 			Pull.Smart pull = new Pull.Smart(pullit.next());
-			analyze(pull);
-			requests.add(pull);
-			i++;
-			pulls++;
-			System.out.println(i);
+			try {
+				if (new Date().getTime() - pull.createdAt().getTime() <= TimeUnit.MILLISECONDS.convert(15, TimeUnit.MINUTES)) {
+					analyze(pull);					
+					requests.add(pull);
+				} else {
+					System.out.println("No new pull requests");
+					break;
+				}
+			} catch (IOException e) {
+				e.printStackTrace();
+				return null;
+			}
 		}
 		return requests;
 	}
@@ -150,7 +153,7 @@ public class PullRecommender {
         RtGithub github = new RtGithub(acct[0], acct[1]);
         Repo repo = github.repos().get(new Coordinates.Simple(args[0], args[1]));
 		PullRecommender recommender = new PullRecommender(repo);
-		ArrayList<Pull.Smart> requests = recommender.getPullRequests(Integer.parseInt(args[2]));
+		ArrayList<Pull.Smart> requests = recommender.getPullRequests();
 		System.out.println("{recs} recommendations made on {pulls} pull request(s) out of {totals} total. {fix} were just fixed."
 			.replace("{recs}", Integer.toString(recs))
 			.replace("{pulls}", Integer.toString(prs.size()))

### 2017-11-30 paper/paper.tex
Starting related work section

@@
 \section{Related Work}
+
+Our work builds on previous research studying the lack of tool adoption by software engineers, methods for improving tool discovery, and existing approaches for automated tool recommendations.
+
+Previous research has explored reasons why software engineers don't use helpful tools.
+Murphy-Hill and colleagues studied developers to uncover why programmers don't use refactoring tools for maintaining software~\cite{MurphyHillWhyRefactoringTools}.
+Johnson et al gathered data from software engineers to determine their perspective on static analysis tools and reasons for underuse~\cite{JohnsonStaticAnalysis}.
 

### 2017-11-30 com/chbrown13/pull_rec/PullRecommender.java
Only open pull requests for master branch

@@ -127,7 +127,7 @@ public class PullRecommender {
 		System.out.println("Getting pull requests...");
 		ArrayList<Pull.Smart> requests = new ArrayList<Pull.Smart>();
 		Map<String, String> params = new HashMap<String, String>();
-		params.put("state", "all");
+		params.put("state", "open");
 		Iterator<Pull> pullit = this.repo.pulls().iterate(params).iterator();
 		int i = 0;
 		while (pullit.hasNext()) {

### 2017-12-10 paper/paper.tex
Related work and paper updates

--- 2017-11-28 paper/paper.tex
@@
 Additionally, these errors can cost companies millions of dollars.
-For example, a recent bug found in the cryptocurrency Ethereum resulted in the loss of \$30 million.\footnote{https://qz.com/1034321/ethereum-hack-a-coding-error-led-to-30-million-in-ethereum-being-stolen/}.
-Additionally, the price of repairing these code failures is becoming more expensive over time~\cite{SEEconomics}.
+For example, a recent bug found in the cryptocurrency Ethereum resulted in the loss of \$30 million~[TODO: find a better example].\footnote{https://qz.com/1034321/ethereum-hack-a-coding-error-led-to-30-million-in-ethereum-being-stolen/} Additionally, studies have shown the price of repairing these code failures becomes more expensive the longer the bug exists~\cite{SEEconomics}.
 
@@
 \tool~was designed to automatically recommend static analysis tools to software engineers.
-Previous research has shown that user-to-user recommendations, or peer interactions, are the most effective mode of increasing awareness of tools among software users~\cite{PeerInteraction}.
+Previous research has shown that user-to-user recommendations are the most effective mode of increasing awareness of tools among software users~\cite{MurphyHill2011PeerInteraction}.
 We designed our system to make suggestions by integrating characteristics of peer interactions and concepts from the software engineering industry.
@@
 
-Improving tool discovery...\\
+Our approach is based on previous research examining how users learn about and discover tools, the lack of tool adoption among software engineers, and existing automated tool recommendation systems.
 
-Existing automated tool recommendation systems...\\
+Researchers have explored ways humans learn about new tools.
+Prior work in diffusion of innovations~\cite{Rogers2003Diffusion} and persuasion theory~\cite{Shen2012Persuasion} show that the way messages are communicated impacts reception.
+There are a numerous methods for discovering tools in software, however, research suggests that recommendations from peers, or \textit{peer interactions}, are the most effective.
+Murphy-Hill found that peer interactions were the most effective mode of tool discovery among software engineers compared to chance encounters, tutorials, descriptions, social media, or discussion threads~\cite{MurphyHill2011PeerInteraction}~\cite{Murphy-Hill2015HowDoUsers}.
+Similarly, Welty discovered that software users sought help from colleagues more than search engines and help menus~\cite{Welty2011Help}.
+Our work builds on the results of these studies by integrating qualities of effective peer-to-peer recommendations into an automated recommendation system.
 
-Improving awareness of software engineering tools...\\
+Previous work has explored the tool adoption problem in software engineering and barriers preventing developers from adopting useful tools for important programming tasks.
+Researchers have created numerous tools to aid software engineers in their work, but these products are often ignored by developers~\cite{Ivanov2017Gaps}.
+Tilley and colleagues studied the challenges of adopting these research-of-the-shelf tools in industry~\cite{Tilley2003ROTS}.
+Johnson and colleagues reported reasons why software engineers don't use static analysis tools to help find and prevent bugs in their code~\cite{Johnson2013Why}.
+Xiao and colleagues examined barriers and social influences blocking developers from using security tools to detect and prevent vulnerabilities and malicious attacks~\cite{Xiao2014Security}.
+Our project aims to increase software engineer tool adoption by developing \tool~to automatically and effectively recommend useful tools to help complete development tasks.
+
+Additionally, there are numerous existing technical approaches created to improve the tool discovery problem.
+Researchers have developed several active help systems using community involvement.
+Gordon and colleagues developed Codepourri, a system using crowdsourcing to collectively create Python tutorials~\cite{Gordon2015Codepourri}.
+Linton and colleagues designed a recommender system called OWL (organization-wide learning) to disseminate tool knowledge using logs throughout a company~\cite{Linton2000OWL}.
+ToolBox was developed as a ``community sensitive help system'' by Maltzahn to recommend Unix commands~\cite{Maltzahn1995Toolbox}.
+Answer Garden helps users discover new tools based on common questions asked by colleagues~\cite{Ackerman1990AnswerGarden}.
+SpyGlass automatically recommends tools to help users navigate code~\cite{Viriyakattiyaporn2010Spyglass}
+
+Fischer and colleagues examined systems that require users to explicitly seek help from the software, or passive help systems~\cite{Fischer1984ActiveHelpSystems}.
+Fischer concluded technical passive recommendation systems, such as documentation and help menues, are ineffective and inefficient for users.
+Instead, active help systems are more useful for increasing tool awareness.
+We developed \tool~to actively suggest useful programming tools and increase awareness for software engineers.
+Our approach differs from existing recommendation systems in the design and implementation of our tool.
 
@@
 \subsection{Design}
-Previous research shows that recommendations between peers is an effective way to increase tool discovery and adoption~\cite{Murphy-HillPeerInteraction}.
-Many automated help systems are designed to simulate user-to-user recommendations in order to increase awareness of application tools and features, for instance Microsoft Clippy\cite{Clippy}.
+Previous research shows that recommendations between peers is an effective way to increase tool discovery and adoption~\cite{MurphyHill2011PeerInteraction}.
+Many existing help systems simulate user-to-user recommendations to increase awareness of application tools and features.
 
@@
 To increase use of helpful programming tools, such as static analysis tools, our system focuses on making recommendations to software engineers within the context of the projects they develop.
-Familiarity with source code is important for creating software applications, and code understandability is one of the most important factors for software development, maintenance, debugging, and testing~\cite{Understandability}.
+Familiarity with source code is important for creating software applications.
+Scalabrino and colleagues claim code understandability is one of the most important factors for software development, maintenance, debugging, and testing~\cite{Scalabrino2017Understandability}.
 
@@
 Our approach suggests \textsc{Error Prone} when reported errors are fixed by developers in pull requests to capitalize on their familiarity with their modifications.
-The GitHub interface allows users to review and comment on pull requests in situ with the proposed changes, and this is where we make our recommendations.
+The GitHub interface allows users to review and comment on pull requests in situ with the proposed changes, this is where we make our recommendations.
 
@@
 Otherwise, if the line was removed our algorithm searches for the closest sibling node or if none exists then the location of the parent.
+Additionally, the line of the fix had to be converted to the equivalent position in the pull request diff file displaying the changes between file versions, or number of lines below the "@@" header\footnote{https://developer.github.com/v3/pulls/comments/\#create-a-comment}, before moving on to the next phase.
 
@@
 Our approach simulates peer reviews by making recommendations for static analysis tools as a comment to the pull request.
+\tool~automatically runs \textsc{Error Prone} and analyzes the code, providing feedback to developers based on their changes and the output of the tool.
 Github provides functionality for making comments at specific lines of code in a pull request, and \tool~recommends \textsc{Error Prone} as a comment at the fix location line from the previous step.
@@
 \begin{itemize}
-\item one of the top Trending projects\footnote{https://github.com/trending} on Github based on activity by the community at the time of this writing,
 \item primarily written in the Java programming language\footnote{https://java.com},
-\item build with Maven,
-\item and are owned by a GitHub organization, instead of personal user account projects.
+\item build with Maven containing a \textit{pom.xml} file in the top directory,
+\item and had at least 10 pull requests submitted by developers in the last six months (180 days).
 \end{itemize}
 
-\begin{table}
-	\centering
-	\caption{Evaluation Projects}
-	\begin{tabular}{|l|l|l|c|}
-		\hline
-		\textbf{Project} & \textbf{Java Files} & \textbf{LOC} & \textbf{Pull Requests} \\
-		\hline
+Using the GitHub Search Repositories\footnote{https://developer.github.com/v3/search/\#search-repositories} functionality through the jcabi GitHub Java API\footnote{http://github.jcabi.com/}, we were able to find 106 projects that met the above criteria.
+
+%\begin{table}
+%	\centering
+%	\caption{Evaluation Projects}
+%	\begin{tabular}{|l|l|l|c|}
+%		\hline
+%		\textbf{Project} & \textbf{Java Files} & \textbf{LOC} & \textbf{Pull Requests} \\
+%		\hline
 %		spring-boot\footnote{https://github.com/spring-projects/spring-boot.git} &  &  & \\
@@
 %		\hline
-		\end{tabular}
-	\begin{tablenotes}
-        \item[1] Details on projects used for study including GitHub repository name, number of Java files, lines of Java code, and total pull requests.
-    \end{tablenotes}
-	\label{tools}
-\end{table}
+%		\end{tabular}
+%	\begin{tablenotes}
+%        \item[1] Details on projects used for study including GitHub repository name, number of Java files, lines of Java code, and total pull requests.
+%    \end{tablenotes}
+%	\label{tools}
+%\end{table}
+%
 
@@
 
-\tool is awesome
+\tool~is awesome
 

### 2017-12-10 paper/paper.tex
Notes for methodology

@@
 
-%\begin{table}
-%	\centering
-%	\caption{Evaluation Projects}
-%	\begin{tabular}{|l|l|l|c|}
-%		\hline
-%		\textbf{Project} & \textbf{Java Files} & \textbf{LOC} & \textbf{Pull Requests} \\
-%		\hline
-%		spring-boot\footnote{https://github.com/spring-projects/spring-boot.git} &  &  & \\
-%		\hline
-%		dubbo\footnote{https://github.com/alibaba/dubbo.git} &  &  & \\
-%		\hline
-%		guava\footnote{https://github.com/google/guava.git}  &  &  & \\
-%		\hline
-%		retrofit\footnote{https://github.com/square/retrofit.git}  &  &  & \\
-%		\hline
-%		rocketmq\footnote{https://github.com/apache/rocketmq.git}  &  &  & \\
-%		\hline
-%		\end{tabular}
-%	\begin{tablenotes}
-%        \item[1] Details on projects used for study including GitHub repository name, number of Java files, lines of Java code, and total pull requests.
-%    \end{tablenotes}
-%	\label{tools}
-%\end{table}
-%
+\subsection{Participants}
+
+Are we collecting any information on the developers?
 
@@
 
-We divided our study into two segments to address each research question:
+We designed our research study to address each  of our research questions.
 
-\subsubsection{RQ1}
+\pseudosubsection{RQ1}
 
-Last 100 pull requests on repositories...
+Quantitative (track number of recs over time)
 
-\subsubsection{RQ2}
+\pseudosubsection{RQ2}
+
+Qualitative (survey)
+
+\subsection{Data Analysis}
+
+\pseudosubsection{RQ1}
+
+Redirected pull requests to me to prevent false positives
+
+\pseudosubsection{RQ2}
 
@@
 Tons of recommendations... \\
-
-No false positives... \\
 

### 2017-12-10 paper/paper.tex
Methodology updates for paper

@@
 Github provides functionality for making comments at specific lines of code in a pull request, and \tool~recommends \textsc{Error Prone} as a comment at the fix location line from the previous step.
-Additionally, our system  uses language similar to comments between co-workers in recommendations, such as using ``Good job!'' to compliment developers on their work'~\cite{?}.
+Additionally, our system  uses language similar to comments between co-workers in recommendations, such as using ``Good job!'' to compliment developers on their work~\cite{?}.
 
-To further increase the adoption of static analysis tools, we report other instances of similar errors found by \textsc{Error Prone} in the base version of the code.
-In the recommendation, \tool~adds links to at most two locations where \textsc{Error Prone} found the same error as the one that was fixed.
-We hope this encourags the use of \textsc{Error Prone} to find more bugs in the pull request before the code is merged into the code base.
-Figure 1 presents a recommendation from our system on a pull request review.
+To further increase adoption and use of static analysis tools, we only make a recommendation if \textsc{Error Prone} reports other instances of the same error in the base version of the code.
+In the comment, \tool~automatically adds direct links to at most two separate locations where the defect that was fixed still exists in the code.
+We hope this encourages the developer receiving the recommendation to use \textsc{Error Prone} to fix similar errors and prevent more bugs from being merged into the master code base.
+Figure 1 presents an example recommendation from our system on a pull request review.
 
@@
 
+Our evaluation gathers both quantitative and qualitative data to evaulate the effectiveness of \tool.
+
 \subsection{Projects}
 
-To evaluate the effectiveness of our recommendation system, we assessed \tool~on five real-world open-source software applications.
-To narrow down projects for our evaluation, we picked Github repositories that met the following criteria:
+To evaluate the effectiveness of our recommendation system, we assessed \tool~on real-world open-source software applications.
+Github hosts millions of code repositories, and to narrow down projects for our evaluation we picked public repos that met the following criteria:
 
@@
 
-Using the GitHub Search Repositories\footnote{https://developer.github.com/v3/search/\#search-repositories} functionality through the jcabi GitHub Java API\footnote{http://github.jcabi.com/}, we were able to find 106 projects that met the above criteria.
-
+Using the GitHub Search Repositories\footnote{https://developer.github.com/v3/search/\#search-repositories} functionality through the jcabi GitHub Java API\footnote{http://github.jcabi.com/}, we were able to identify 106 projects that met the above criteria.
+A full list of the repositories used in our evaluation is available to view online.\footnote{link}
 \subsection{Participants}
 
-Are we collecting any information on the developers?
+Are we collecting any demographic information on the developers?
 
@@
 
-We designed our research study to address each  of our research questions.
+We designed our study to address each of our research questions and address the influence of our recommendation system on improving tool discovery.
 
@@
 
-Quantitative (track number of recs over time)
+To gather data on how often \tool~makes recommendations, we counted the number of pull request comments made by our tool throughout the duration of our study.
+We wanted to determine how regularly our approach has opportunities to make recommendations to developers.
+For each project, we accumulated the number of recommendations made over [TODO: some period of time].
+To run our evaluation on the 106 repositories simultaneously, we installed \tool~as Jenkins jobs on multiple virtual machines to analyze the code bases in parallel.
+
+In addition to the rate at which our system makes recommendations, we also collected other measurements to evaluate our system.
+We calculated our tool's false-positive rate, instances where errors were fixed but not found elsewhere in the code, so no recommendation was made, and occurrences where our approach reported an error was removed but not fixed according to our algorithm in Section III.B.2.
 
@@
 
-Qualitative (survey)
+To gather data on the usefulness of our system, we sent a follow-up survey to Github users who received a recommendation from our tool on a pull request they submitted.
+We asked the following questions to gather qualitative data:
+
+\begin{itemize}
+\item Question 1...
+\end{itemize}
+
+Developers voluntarily consented to participate in the survey and provide feedback on our recommendation.
 
@@
 
+We analyzed the frequency of recommendations and follow-up survey responses to determine the effectiveness of our approach.
+
 \pseudosubsection{RQ1}
 
-Redirected pull requests to me to prevent false positives
+To prevent false positives from our tool, all potential recommendations were redirected to the researchers before posting a comment on a pull request.
+Johnson discovered that one of the main barriers for underuse of static analysis tool among software engineers is reporting false positives in the tool output~\cite{Johnson2013Why}.
 

### 2017-12-12 paper/paper.tex
Updates to paper draft

@@
 Additionally, these errors can cost companies millions of dollars.
-For example, a recent bug found in the cryptocurrency Ethereum resulted in the loss of \$30 million~[TODO: find a better example].\footnote{https://qz.com/1034321/ethereum-hack-a-coding-error-led-to-30-million-in-ethereum-being-stolen/} Additionally, studies have shown the price of repairing these code failures becomes more expensive the longer the bug exists~\cite{SEEconomics}.
+For example, a recent bug found in the cryptocurrency Ethereum resulted in the loss of \$30 million.\footnote{https://qz.com/1034321/ethereum-hack-a-coding-error-led-to-30-million-in-ethereum-being-stolen/} Additionally, studies have shown the price of repairing these code failures becomes more expensive the longer the bug exists~\cite{SEEconomics}.
+%TODO: find better example
 
@@
 
-To target this desire of mistake-free code, our initial implementation of \tool~automatically recommends \textsc{Error Prone}.\footnote{http://errorprone.info} \textsc{Error Prone} is a static analysis tool created by Google to check for errors in Java code based on a suite of bug patterns.
-These tools are useful in debugging and creating desireable applications, however they are often underutilized by software engineers~\cite{Johnson2013Why}.
+To target this desire of mistake-free code, our initial implementation of \tool~automatically recommends the tool \textsc{Error Prone}.\footnote{http://errorprone.info} \textsc{Error Prone} is a static analysis tool created by Google to check for errors in Java code based on a suite of bug patterns.
+Static analysis tools like \textsc{Error Prone} are useful for debugging and preventing errors in source code for applications, however they are often underutilized by software engineers~\cite{Johnson2013Why}.
 
@@
 Developers making these changes should be knowledgeable about the changes they propose as well as the code base to which they are contributing.
-Our approach suggests \textsc{Error Prone} when reported errors are fixed by developers in pull requests to capitalize on their familiarity with their modifications.
-The GitHub interface allows users to review and comment on pull requests in situ with the proposed changes, this is where we make our recommendations.
+Our approach suggests \textsc{Error Prone} when a reported error is fixed by a developer in a pull requests but still exists elsewhere in the code to capitalize on their familiarity with the modifications and encourage the use of static analysis tools to find more bugs.
 
@@
 Figure 1 presents an example recommendation from our system on a pull request review.
+%TODO: Add screenshot
 
@@
 We wanted to determine how regularly our approach has opportunities to make recommendations to developers.
-For each project, we accumulated the number of recommendations made over [TODO: some period of time].
+For each project, we accumulated the number of recommendations made over [some period of time].
 To run our evaluation on the 106 repositories simultaneously, we installed \tool~as Jenkins jobs on multiple virtual machines to analyze the code bases in parallel.
-
-In addition to the rate at which our system makes recommendations, we also collected other measurements to evaluate our system.
-We calculated our tool's false-positive rate, instances where errors were fixed but not found elsewhere in the code, so no recommendation was made, and occurrences where our approach reported an error was removed but not fixed according to our algorithm in Section III.B.2.
 
@@
 To gather data on the usefulness of our system, we sent a follow-up survey to Github users who received a recommendation from our tool on a pull request they submitted.
-We asked the following questions to gather qualitative data:
-
-\begin{itemize}
-\item Question 1...
-\end{itemize}
+In our survey, we asked developers if they had ever heard of \textsc{Error Prone} before our tool's recommendation and to name static analysis tools they normally use while programming, if any.
+We also asked Likert-scale questions for the perceived usefulness of our recommendation and how likely participants are to use \textsc{Error Prone} in the future.
+The survey concluded by providing participants an opportunity to add any comments or feedback on our system and the recommendation they received.
 
 Developers voluntarily consented to participate in the survey and provide feedback on our recommendation.
+To ensure participants answered honestly, we notified them that their responses would be used for research.
+Research shows that survey respondents are more motivated to answer truthfullly if they know they are contributing to research~\cite{Krosnick1991Research}.
 
@@
 
-To prevent false positives from our tool, all potential recommendations were redirected to the researchers before posting a comment on a pull request.
+To answer our first research question, we calculated the rate at which \tool~makes recommendations on opened pull requests. 
+In addition to recommendation frequency, we collected other data to evaluate our system.
+We determined the false-positive rate for recommendations made by our system.
+To track instances where \textsc{Error Prone} defects were removed between versions of code, we also report the number of errors fixed without another instance found in the code and the number of bugs removed but not fixed according to our fix identification algorithm in Section III.B.2.
+
+To prevent unnecessary comments on pull requests from our tool, all potential recommendations were reviewed by the researchers before posting to Github.
 Johnson discovered that one of the main barriers for underuse of static analysis tool among software engineers is reporting false positives in the tool output~\cite{Johnson2013Why}.
+We reviewed each pull request to determine if a fix was actually made.
+If so, \tool~could proceed and post the comment recommending \textsc{Error Prone} on the pull request.
+Otherwise we made note of a false positive found by our approach.
 
@@
 
-Followed up with pull request authors to gather data on recommendation...
+For our second research question, we gathered data by accumulating responses from developers in our survey.
 

### 2017-12-12 com/chbrown13/pull_rec/Comment.java
Changes for eval

@@ -7,6 +7,9 @@ import com.jcabi.github.*;
  */
 public class Comment {		
 
+    public static String compile = "sudo javac -cp jcabi-github-0.23-jar-with-dependencies.jar com/chbrown13/pull_rec/Comment.java";
+    public static String cmd = "java -cp .:jcabi-github-0.23-jar-with-dependencies.jar com.chbrown13.pull_rec.Comment {args}";
+    public static String changes = "https://github.com/{user}/{repo}/pull/{num}/files";
     /**
      * Posts comment to a pull request on Github
      * 
@@ -20,7 +23,7 @@ public class Comment {
         try {
             PullComments pullComments = pull.comments();
             PullComment.Smart smartComment = new PullComment.Smart(pullComments.post(comment, hash, file, line));	
-            System.out.println(comment);
+            System.out.println("Recommendation comment posted.");
         } catch (Exception e) {
             e.printStackTrace();
         }

### 2017-12-12 com/chbrown13/pull_rec/PullRecommender.java

@@ -6,11 +6,8 @@ import java.io.*;
 import java.util.*;
 import java.util.concurrent.TimeUnit;
 import javax.json.JsonObject;
-// import javax.mail.*;
-// import javax.mail.internet.*;
-// import javax.activation.*;
-// import javax.mail.Session;
-// import javax.mail.Transport;
+import org.apache.commons.mail.*;
+
 
 /**
  * PullRecommender is the main class for this project and handles interactions with Github repositories.
@@ -18,11 +15,10 @@ import javax.json.JsonObject;
 public class PullRecommender {
 
 	private Repo repo;
-	private static Set<Integer> prs = new HashSet<Integer>();	
-	private static int recs = 0;;
-	private static int open = 0;
-	private static int removed = 0;
-	private static int fixes = 0;
+	private Set<Integer> prs = new HashSet<Integer>();	
+	private int recs = 0;;
+	private int removed = 0;
+	private int fixes = 0;
 
 	public PullRecommender(Repo repo) {
 		this.repo = repo;
@@ -30,48 +26,33 @@ public class PullRecommender {
 		Utils.setProjectOwner(repo.coordinates().user());
 	}
 
-	/*private void sendEmail() {
-				// Recipient's email ID needs to be mentioned.
-				String to = "dcbrown06@gmail.com";
-		
-			  // Sender's email ID needs to be mentioned
-			  String from = "toolrecommenderbot@gmail.com";
-		
-			  // Assuming you are sending email from localhost
-			  String host = "localhost";
-		
-			  // Get system properties
-			  Properties properties = System.getProperties();
-		
-			  // Setup mail server
-			  properties.setProperty("mail.smtp.host", host);
-		
-			  // Get the default Session object.
-			  Session session = Session.getDefaultInstance(properties);
-		
-			  try {
-				 // Create a default MimeMessage object.
-				 MimeMessage message = new MimeMessage(session);
-		
-				 // Set From: header field of the header.
-				 message.setFrom(new InternetAddress(from));
-		
-				 // Set To: header field of the header.
-				 message.addRecipient(Message.RecipientType.TO, new InternetAddress(to));
-		
-				 // Set Subject: header field
-				 message.setSubject("This is the Subject Line!");
-		
-				 // Now set the actual message
-				 message.setText("This is actual message");
-		
-				 // Send message
[…]

### 2017-12-12 com/chbrown13/pull_rec/PullRecommender.java
Missing paren

@@ -45,7 +45,7 @@ public class PullRecommender {
 			email.setSSLOnConnect(true);
 			email.setFrom("toolrecommenderbot@gmail.com");
 			email.setSubject("[tool-recommender-bot] " + subject);
-			email.setMsg(String.join("\n", viewChanges, text);
+			email.setMsg(String.join("\n", viewChanges, text));
 			email.addTo("dcbrow10@ncsu.edu");
 			email.send();		
 			System.out.println("Email sent for review.");	

### 2017-12-13 com/chbrown13/pull_rec/Error.java
Add message to log

@@ -140,7 +140,7 @@ public class Error {
 	public String generateComment(Tool tool, Set<Error> similar, String sha) {
 		String comment = Utils.BASE_COMMENT.replace("{desc}", tool.getDescription()).replace("{tool}", tool.getName()).replace("{link}", tool.getLink());
 		String simSentence = " {tool} also found {issue} in {link}. ".replace("{tool}", tool.getName()); //TODO replace with tool
-		comment = comment.replace("{fixed}", "\\`\\`\\`" + this.log + "\\`\\`\\`");
+		comment = comment.replace("{fixed}", "\\`\\`\\`" + this.message + this.log + "\\`\\`\\`");
 		Set<Error> similarSet = new HashSet<Error>();
 		Error sim;
 		for (Error epi: similar) {

### 2018-01-09 paper/paper.tex
Updates to paper for Reading Group 1/9

@@
 Previous research suggests that peer-to-peer recommendations is an effective mode of tool discovery, and the receptiveness of recommendees is a vital characteristic in determining the outcome of tool suggestions.
-To help increase awareness of useful tools, we developed and evaluated a new system \tool~designed to integrate aspects of peer interactions and user receptivity into automated tool recommendations for software developers of real-world applications.
-Our findings suggest that \tool~is awesome, cool, and very effective in improving tool discovery.
+To help increase awareness of useful tools, we developed and evaluated a new system, \tool, designed to integrate aspects of peer interaction, software engineering concepts, and user receptivity into automated tool recommendations for developers of real-world applications.
+We evaluated our approach on over 900 GitHub projects and our findings suggest that \tool~is awesome and very effective in improving tool discovery.
 \end{abstract}
@@
 
-Our evaluation gathers both quantitative and qualitative data to evaulate the effectiveness of \tool.
+Our study evaluates the effectiveness of \tool~by analyzing how often our approach makes tool recommendations and how developers respond to recommendations they receive from our system.
 
@@
 
-To evaluate the effectiveness of our recommendation system, we assessed \tool~on real-world open-source software applications.
-Github hosts millions of code repositories, and to narrow down projects for our evaluation we picked public repos that met the following criteria:
+To determine the effectiveness of our approach, we used real-world open source software applications to evaluate \tool.
+Projects for our evaluation were selected from Github, which hosts millions of code repositories online.
+To narrow down the number of projects for our study, we chose repositories that met the following criteria:
 
@@
 \item primarily written in the Java programming language\footnote{https://java.com},
-\item build with Maven containing a \textit{pom.xml} file in the top directory,
-\item and had at least 10 pull requests submitted by developers in the last six months (180 days).
+\item build with Maven and contain a \textit{pom.xml} file in the top directory,
+\item and were ranked among the top 100 forked repositories for a month since February 2008.
 \end{itemize}
 
-Using the GitHub Search Repositories\footnote{https://developer.github.com/v3/search/\#search-repositories} functionality through the jcabi GitHub Java API\footnote{http://github.jcabi.com/}, we were able to identify 106 projects that met the above criteria.
-A full list of the repositories used in our evaluation is available to view online.\footnote{link}
-\subsection{Participants}
-
-Are we collecting any demographic information on the developers?
+Using a GitHub search API with the above constraints, we identified 917 projects for our evaluation.\footnote{\url{https://docs.google.com/spreadsheets/d/1MRmVPiUeDlYMa0UODzMmFbGeYBbahzdeEv1YSgqC1oo/edit?usp=sharing}} We selected the most forked repositories to collect popular projects with a lot of activity, and forking a repository is suggested as one of the GitHub contributor best practices and is a requirement by many projects for submitting a pull request to make changes to the master code base.
 
@@
 
-We designed our study to address each of our research questions and address the influence of our recommendation system on improving tool discovery.
+We designed our evaluation to gather quantitative and qualitative data addressing our research questions.
 
-\pseudosubsection{RQ1}
+\pseudosection{RQ1}
 
-To gather data on how often \tool~makes recommendations, we counted the number of pull request comments made by our tool throughout the duration of our study.
-We wanted to determine how regularly our approach has opportunities to make recommendations to developers.
-For each project, we accumulated the number of recommendations made over [some period of time].
-To run our evaluation on the 106 repositories simultaneously, we installed \tool~as Jenkins jobs on multiple virtual machines to analyze the code bases in parallel.
+To answer our first research question, we observed how often our approach makes recommendations on newly opened pull requests.
+To analyze the 917 repositories simultaneously, we used Ansible\footnote{https://www.ansible.com/} to install \tool~as a Jenkins job on multiple virtual machines.
+In addition to the frequency of recommendations, we also tracked instances where \textsc{Error Prone} defects were removed but not reported as fixed according to our fix identification algorithm in Section III.B.2, the number of occurrences where errors were fixed but no other instances of that bug were found in the code, and the false positive rate.
 
-\pseudosubsection{RQ2}
+Johnson and colleagues discovered one of the primary barriers to static analysis tool usage among software engineers is false positives in the output~\cite{Johnson2013Why}.
+To prevent unnecessary recommendations from our system, we manually reviewed all instances where \tool~reported a recommendation should be made.
+After inspecting each reported pull request, we determined whether it was an appropriate case for our system to make a recommendation to developers.
+If so, we proceeded to post the comment recommending \textsc{Error Prone} on the pull request.
+Otherwise, we noted the instance of a false positive in our approach and did not make a recommendation.
 
-To gather data on the usefulness of our system, we sent a follow-up survey to Github users who received a recommendation from our tool on a pull request they submitted.
-In our survey, we asked developers if they had ever heard of \textsc{Error Prone} before our tool's recommendation and to name static analysis tools they normally use while programming, if any.
-We also asked Likert-scale questions for the perceived usefulness of our recommendation and how likely participants are to use \textsc{Error Prone} in the future.
-The survey concluded by providing participants an opportunity to add any comments or feedback on our system and the recommendation they received.
+\pseudosection{RQ2}
 
-Developers voluntarily consented to participate in the survey and provide feedback on our recommendation.
-To ensure participants answered honestly, we notified them that their responses would be used for research.
-Research shows that survey respondents are more motivated to answer truthfullly if they know they are contributing to research~\cite{Krosnick1991Research}.
+To gather data on the usefulness of our system, we sent a follow-up survey to developers.
+Survey participants were users who received a recommendation from \tool~on their pull request.
+We asked developers four questions about their awareness of \textsc{Error Prone}, their static analysis tool usage, the usefulness of our recommendation, and how likely they are to use \textsc{Error Prone} in the future.
+The survey also included a free-response section to provide an opportunity for participants to add any other comments or feedback about the recommendation.
+
+Developers voluntarily consented to complete the survey and provide feedback on our system.
+To ensure developers answered honestly, we notified respondents that their answers will be used for research purposes.
+Previous research has shown that survey participants are more motivated to answer truthfullly if they know they are contributing to research~\cite{Krosnick1991Research}.
 
@@
 
-We analyzed the frequency of recommendations and follow-up survey responses to determine the effectiveness of our approach.
+We analyzed the data collected in our study to determine effectiveness of our automated tool recommendation system.
 
-\pseudosubsection{RQ1}
+\pseudosection{RQ1}
 
-To answer our first research question, we calculated the rate at which \tool~makes recommendations on opened pull requests. 
-In addition to recommendation frequency, we collected other data to evaluate our system.
-We determined the false-positive rate for recommendations made by our system.
-To track instances where \textsc{Error Prone} defects were removed between versions of code, we also report the number of errors fixed without another instance found in the code and the number of bugs removed but not fixed according to our fix identification algorithm in Section III.B.2.
+Effective tool recommendation systems should have ample opportunities to regularly make recommendations to users.
+To determine how often \tool~automatically recommends \textsc{Error Prone}, we observed the number of pull request comments made by our tool.
+Our evaluation lasted for [some period of time], and we calculated the amount of true positive recommendations during that time span to measure the recommendation rate for each GitHub repository used in our study.
+To calculate the false positive rate, we compared the number of unnecessary instances where our tool proposed a recommendation found by researchers to the total number of instances where a recommendation reported by \tool.
 
-To prevent unnecessary comments on pull requests from our tool, all potential recommendations were reviewed by the researchers before posting to Github.
-Johnson discovered that one of the main barriers for underuse of static analysis tool among software engineers is reporting false positives in the tool output~\cite{Johnson2013Why}.
-We reviewed each pull request to determine if a fix was actually made.
-If so, \tool~could proceed and post the comment recommending \textsc{Error Prone} on the pull request.
-Otherwise we made note of a false positive found by our approach.
+\pseudosection{RQ2}
 
-\pseudosubsection{RQ2}
-
-For our second research question, we gathered data by accumulating responses from developers in our survey.
+For our second research question, we accumulated responses from developers in our follow-up survey to determine the usefulness of our system.
+Dichotomous questions with Yes/No responses were used to gather information on if developers had prior knowledge of the existence of \textsc{Error Prone} and if they normally use static analysis tools during their work.
+Participants were also asked to list the static analysis tools they work with during software development.
+We utilized a five-point Likert scale for participants to rank how how helpful they found our recommendation and how likely they are to use \textsc{Error Prone} for future development tasks.
+These responses were used to analyze developers' reactions to our automated recommendation.
+Finally, researchers analyzed and independently coded open-ended responses from participants to further analyze the effectiveness of our system based on developer feedback.
 
@@
 
+No false positives...
+
 \subsection{How useful are recommendations from \tool~to developers?}
@@
 
-Statistically significant data...
+Something statistically significant...
 
@@
 
+\subsubsection{Why Were There So Few Recommendations?}
+
+Non-java changes, documentation, errors removed not fixed, error fixed everywhere in code...
+
 \subsection{Implications}
 
-Here's what our results say about ways to improve tool recommendation systems...
+Here's what our results say about improving tool recommendation systems...
 
@@
 
-More tools to recommend (static analysis, security, etc.) \\
+More programming languages (Python, C, C++ etc.)...\\
 
-More programming languages instead of just java...\\
+More types of tools to recommend (static analysis, security, debugging, etc.)... \\
 

### 2018-01-09 paper/paper.tex
Updates from RG comments pt 1

@@
 \begin{itemize}
-\item primarily written in the Java programming language\footnote{https://java.com},
-\item build with Maven and contain a \textit{pom.xml} file in the top directory,
-\item and were ranked among the top 100 forked repositories for a month since February 2008.
+\item primarily written in Java,
+\item builds with Maven,
+\item and were ranked among the top 100 forked repositories for every month from February 2008 - December 2017.
 \end{itemize}
 
-Using a GitHub search API with the above constraints, we identified 917 projects for our evaluation.\footnote{\url{https://docs.google.com/spreadsheets/d/1MRmVPiUeDlYMa0UODzMmFbGeYBbahzdeEv1YSgqC1oo/edit?usp=sharing}} We selected the most forked repositories to collect popular projects with a lot of activity, and forking a repository is suggested as one of the GitHub contributor best practices and is a requirement by many projects for submitting a pull request to make changes to the master code base.
+\textsc{Error Prone} currently only analyzes Java code, so our search was restricted to open source Java projects on GitHub.
+Our study focused on Maven projects because it is a popular build system for Java projects and also contains an \textsc{Error Prone} plug-in.
+The current implementation of \tool~automatically implements this plug-in by modifying the \textit{pom.xml} file in the top directory.
+We selected the most forked repositories to collect popular projects with a lot of activity, and forking a repository is suggested as one of the GitHub best practices for contributing to a project\footnote{https://guides.github.com/activities/forking/}.
+Using a GitHub search API with the above constraints, we identified 917 projects for our evaluation.\footnote{\url{https://docs.google.com/spreadsheets/d/1MRmVPiUeDlYMa0UODzMmFbGeYBbahzdeEv1YSgqC1oo/edit?usp=sharing}}
 
@@
 Survey participants were users who received a recommendation from \tool~on their pull request.
-We asked developers four questions about their awareness of \textsc{Error Prone}, their static analysis tool usage, the usefulness of our recommendation, and how likely they are to use \textsc{Error Prone} in the future.
-The survey also included a free-response section to provide an opportunity for participants to add any other comments or feedback about the recommendation.
+We asked developers about their awareness of \textsc{Error Prone} and how likely they are to use the tool in the future.
+The survey also included a free-response section to provide an opportunity for participants to add comments on the usefulness of the recommendation.
 
@@
 For our second research question, we accumulated responses from developers in our follow-up survey to determine the usefulness of our system.
-Dichotomous questions with Yes/No responses were used to gather information on if developers had prior knowledge of the existence of \textsc{Error Prone} and if they normally use static analysis tools during their work.
-Participants were also asked to list the static analysis tools they work with during software development.
-We utilized a five-point Likert scale for participants to rank how how helpful they found our recommendation and how likely they are to use \textsc{Error Prone} for future development tasks.
+We utilized a five-point Likert scale for participants to rank how knowledgeable they were about the existence of \textsc{Error Prone} before the recommendation and how likely they are to use \textsc{Error Prone} for future development tasks.
+An optional free response section was provided at the end for respondents to describe explain why or why not they found the recommendation useful.
 These responses were used to analyze developers' reactions to our automated recommendation.

### 2018-01-25 eval_scripts/eval.py
Adding scripts for tool-recommender-bot evaluation
Removing secure data

@@ -1,0 +1,34 @@
+import paramiko
+
+def jenkins(user, repo):
+    with open("jenkins.xml") as f:
+        config = f.read()
+    config = config.replace("{user}", user).replace("{repo}", repo)
+    return config
+
+def ssh():
+    ssh = paramiko.SSHClient()
+    ssh.load_system_host_keys()
+    ssh.set_missing_host_key_policy(paramiko.AutoAddPolicy())
+    ssh.connect("", username="", password="")
+    ssh_stdin, stdout, stderr = ssh.exec_command("python projects.py")
+    return stdout.readlines()
+
+def main():
+    i = 0
+    projects = [x for x in ssh() if x != '\n']
+    for p in projects:
+        git = p.replace("\n","").split("/")
+        if git:
+            i += 1
+            filename = "tool_recommender_bot"+str(i)
+            config = jenkins(git[0], git[1]) 
+            xml = open(filename+".xml", "w")
+            xml.write(config)
+            xml.close()
+            files = open("configs.txt", "a")
+            files.write(filename+"\n")
+            files.close()
+
+if __name__ == "__main__":
+    main()

### 2018-01-25 eval_scripts/eval.py
Adding scripts for tool-recommender-bot evaluation

@@ -1,0 +1,34 @@
+import paramiko
+
+def jenkins(user, repo):
+    with open("jenkins.xml") as f:
+        config = f.read()
+    config = config.replace("{user}", user).replace("{repo}", repo)
+    return config
+
+def ssh():
+    ssh = paramiko.SSHClient()
+    ssh.load_system_host_keys()
+    ssh.set_missing_host_key_policy(paramiko.AutoAddPolicy())
+    ssh.connect("152.46.17.1", username="dcbrow10", password="chr03bro")
+    ssh_stdin, stdout, stderr = ssh.exec_command("python projects.py")
+    return stdout.readlines()
+
+def main():
+    i = 0
+    projects = [x for x in ssh() if x != '\n']
+    for p in projects:
+        git = p.replace("\n","").split("/")
+        if git:
+            i += 1
+            filename = "tool_recommender_bot"+str(i)
+            config = jenkins(git[0], git[1]) 
+            xml = open(filename+".xml", "w")
+            xml.write(config)
+            xml.close()
+            files = open("configs.txt", "a")
+            files.write(filename+"\n")
+            files.close()
+
+if __name__ == "__main__":
+    main()

### 2018-01-25 eval_scripts/setup.sh
Adding setup script
Bash script to conduct set up software, commands, etc. for each VCL image used in study

@@ -1,0 +1,42 @@
+# Update
+sudo yum -y install epel-release
+sudo yum -y update
+
+# Install commands
+sudo yum -y install wget
+sudo yum -y install unzip
+sudo yum -y install python-pip
+sudo pip install paramiko
+
+# Install Java
+sudo yum -y install java-1.8.0-openjdk.x86_64
+sudo cp /etc/profile /etc/profile_backup
+echo 'export JAVA_HOME=/usr/lib/jvm/jre-1.8.0-openjdk' | sudo tee -a /etc/profile
+echo 'export JRE_HOME=/usr/lib/jvm/jre' | sudo tee -a /etc/profile
+source /etc/profile
+echo $JAVA_HOME
+echo $JRE_HOME
+cd ~
+
+# Install and Start Jenkins
+sudo wget -O /etc/yum.repos.d/jenkins.repo https://pkg.jenkins.io/redhat-stable/jenkins.repo
+sudo rpm --import https://pkg.jenkins.io/redhat-stable/jenkins.io.key
+sudo yum -y install jenkins
+sudo systemctl start jenkins.service
+sudo systemctl enable jenkins.service
+sudo firewall-cmd --zone=public --permanent --add-port=8080/tcp
+sudo firewall-cmd --reload
+wget http://localhost:8080/jnlpJars/jenkins-cli.jar
+
+# Install Groovy
+sudo yum -y install groovy
+
+# Create Jenkins user
+
+# Install Ansible
+sudo yum -y install ansible
+sudo echo "localhost ansible_connection=local" > /etc/ansible/hosts
+
+# tool-recommender-bot study scripts
+wget https://raw.githubusercontent.com/chbrown13/PullRecommender/master/eval_scripts/tool-recommender-bot.yml
+ansible-playbook tool-recommender-bot.yml

### 2018-01-25 eval_scripts/setup.sh
Update ansible hosts for local script

@@ -35,7 +35,8 @@ sudo yum -y install groovy
 
 # Install Ansible
 sudo yum -y install ansible
-sudo echo "localhost ansible_connection=local" > /etc/ansible/hosts
+echo "localhost ansible_connection=local" > hosts
+sudo mv hosts /etc/ansible/hosts
 
 # tool-recommender-bot study scripts
 wget https://raw.githubusercontent.com/chbrown13/PullRecommender/master/eval_scripts/tool-recommender-bot.yml

### 2018-01-25 eval_scripts/eval.py
Anonymizing info

@@ -6,11 +6,21 @@ def jenkins(user, repo):
     config = config.replace("{user}", user).replace("{repo}", repo)
     return config
 
+def get_creds():
+    with open(".ip") as f:
+        ip = f.read()
+    with open(".username") as f:
+        user = f.read()
+    with open(".password") as f:
+        passwd = f.read()
+    return ip, user, passwd
+
 def ssh():
     ssh = paramiko.SSHClient()
     ssh.load_system_host_keys()
     ssh.set_missing_host_key_policy(paramiko.AutoAddPolicy())
-    ssh.connect("", username="", password="")
+    connect = get_creds()
+    ssh.connect(connect[0], username=connect[1], password=connect[2])
     ssh_stdin, stdout, stderr = ssh.exec_command("python projects.py")
     return stdout.readlines()
 

### 2018-01-26 com/chbrown13/pull_rec/PullRecommender.java
Removing comments in PullRecommender.java

@@ -195,26 +195,8 @@ public class PullRecommender {
 	public static void main(String[] args) {
 		String[] acct = Utils.getCredentials(".github.creds");
 		RtGithub github = new RtGithub(acct[0], acct[1]);
-		// try {
-		// 	BufferedReader br = new BufferedReader(new FileReader("projects.txt"));
-		// 	String line;
-		// 	int i = 0;
-		// 	while ((line = br.readLine()) != null) {
-		// 		String[] gitInfo = line.split("/");
-		// 		System.out.println(gitInfo[0] + " " + gitInfo[1] + " " + Integer.toString(i));
-				Repo repo = github.repos().get(new Coordinates.Simple(args[0], args[1]));
-				PullRecommender recommender = new PullRecommender(repo);
-				ArrayList<Pull.Smart> requests = recommender.getPullRequests();
-				// System.out.println("{recs} recommendations made on {pulls} pull request(s) out of {totals} total. {fix} were just fixed."
-				// 	.replace("{recs}", Integer.toString(recs))
-				// 	.replace("{pulls}", Integer.toString(prs.size()))
-				// 	.replace("{totals}", Integer.toString(requests.size()))
-				// 	.replace("{fix}", Integer.toString(fixes - recs))
-				// );
-				//i++;
-			//}
-		// } catch (IOException io) {
-		//	io.printStackTrace();
-		// }
+		Repo repo = github.repos().get(new Coordinates.Simple(args[0], args[1]));
+		PullRecommender recommender = new PullRecommender(repo);
+		ArrayList<Pull.Smart> requests = recommender.getPullRequests();
 	}
 }

### 2018-01-26 eval_scripts/eval.py
Updating evaluation scripts for ssh info

@@ -7,20 +7,16 @@ def jenkins(user, repo):
     return config
 
 def get_creds():
-    with open(".ip") as f:
-        ip = f.read()
-    with open(".username") as f:
-        user = f.read()
-    with open(".password") as f:
-        passwd = f.read()
-    return ip, user, passwd
+    with open(".projects_ssh") as f:
+        connect = f.readlines()
+    return [c.replace("\n", "") for c in connect]
 
 def ssh():
     ssh = paramiko.SSHClient()
     ssh.load_system_host_keys()
     ssh.set_missing_host_key_policy(paramiko.AutoAddPolicy())
-    connect = get_creds()
-    ssh.connect(connect[0], username=connect[1], password=connect[2])
+    conn = connection()
+    ssh.connect(conn[0], username=conn[1], password=conn[2])
     ssh_stdin, stdout, stderr = ssh.exec_command("python projects.py")
     return stdout.readlines()
 

### 2018-01-26 eval_scripts/setup.sh

@@ -38,6 +38,7 @@ sudo yum -y install ansible
 echo "localhost ansible_connection=local" > hosts
 sudo mv hosts /etc/ansible/hosts
 
-# tool-recommender-bot study scripts
+# Start tool-recommender-bot study
 wget https://raw.githubusercontent.com/chbrown13/PullRecommender/master/eval_scripts/tool-recommender-bot.yml
+wget https://gist.githubusercontent.com/chbrown13/ca345f0d96401144373b745975724412/raw/6d689ecc32165bfa336a084d0ac6614a4581b982/.project_ssh
 ansible-playbook tool-recommender-bot.yml

### 2018-01-26 eval_scripts/eval.py
Fixed bug

@@ -6,7 +6,7 @@ def jenkins(user, repo):
     config = config.replace("{user}", user).replace("{repo}", repo)
     return config
 
-def get_creds():
+def connection():
     with open(".projects_ssh") as f:
         connect = f.readlines()
     return [c.replace("\n", "") for c in connect]

### 2018-01-26 eval_scripts/setup.sh
Fixed link

@@ -40,5 +40,5 @@ sudo mv hosts /etc/ansible/hosts
 
 # Start tool-recommender-bot study
 wget https://raw.githubusercontent.com/chbrown13/PullRecommender/master/eval_scripts/tool-recommender-bot.yml
-wget https://gist.githubusercontent.com/chbrown13/ca345f0d96401144373b745975724412/raw/6d689ecc32165bfa336a084d0ac6614a4581b982/.project_ssh
+wget https://gist.githubusercontent.com/chbrown13/ca345f0d96401144373b745975724412/raw/72cf4f75ec85bc9ad94c1e072965c797503e52b9/.projects_ssh
 ansible-playbook tool-recommender-bot.yml

### 2018-01-30 eval_scripts/setup.sh
Upgrade to latest version of pip

@@ -6,6 +6,7 @@ sudo yum -y update
 sudo yum -y install wget
 sudo yum -y install unzip
 sudo yum -y install python-pip
+sudo pip install --upgrade pip
 sudo pip install paramiko
 
 # Install Java

### 2018-01-30 eval_scripts/setup.sh
Run eval.py before ansible

@@ -42,4 +42,7 @@ sudo mv hosts /etc/ansible/hosts
 # Start tool-recommender-bot study
 wget https://raw.githubusercontent.com/chbrown13/PullRecommender/master/eval_scripts/tool-recommender-bot.yml
 wget https://gist.githubusercontent.com/chbrown13/ca345f0d96401144373b745975724412/raw/72cf4f75ec85bc9ad94c1e072965c797503e52b9/.projects_ssh
+wget https://raw.githubusercontent.com/chbrown13/PullRecommender/master/jenkins.xml
+wget https://raw.githubusercontent.com/chbrown13/PullRecommender/master/eval_scripts/eval.py
+python eval.py
 ansible-playbook tool-recommender-bot.yml

### 2018-01-30 paper/paper.tex
Paper updates and RQ2
Abstract and intro updates

@@
 \begin{abstract}
-Recommendation systems were developed to improve the adoption of useful software tools and features designed to save time and effort in completing tasks that are often ignored by users.
-Previous research suggests that peer-to-peer recommendations is an effective mode of tool discovery, and the receptiveness of recommendees is a vital characteristic in determining the outcome of tool suggestions.
-To help increase awareness of useful tools, we developed and evaluated a new system, \tool, designed to integrate aspects of peer interaction, software engineering concepts, and user receptivity into automated tool recommendations for developers of real-world applications.
-We evaluated our approach on over 900 GitHub projects and our findings suggest that \tool~is awesome and very effective in improving tool discovery.
+Software contains a variety of useful tools and features designed to increase productivity that are often ignored or undiscovered by users.
+This lack of tool awareness can have dangerous consequences, especially in the software engineering industry.
+Automated recommendation systems have been created to software tool discovery, however these systems are not as effective as user-to-user recommendations.
+To improve the effectiveness of recommender systems, we implemented \textit{\tool}, a novel system which allows toolsmiths to increase discovery of software engineering tools by integrating aspects of peer interactions, and found that our approach is useful in making recommendations and increasing awareness of a static analysis tool to programmers on 800+ GitHub projects.
 \end{abstract}
@@
 
-Software has permeated nearly every area of our society.
+Software is increasingly prevelant throughout society.
 To keep up with the increasing demand for technology, software quality has become an increasingly important metric for software development teams.
@@
 Peer interactions and receptiveness are effective~\cite{vlhcc17}...
+Previous research has shown that user-to-user recommendations are the most effective mode of increasing awareness of tools among software users~\cite{MurphyHill2011PeerInteraction}
 
-To solve the static analysis tool discovery problem, we developed a new recommender system called~\textit{\tool}.
-\tool~was designed to automatically recommend static analysis tools to software engineers.
-Previous research has shown that user-to-user recommendations are the most effective mode of increasing awareness of tools among software users~\cite{MurphyHill2011PeerInteraction}.
+To solve the tool discovery problem, we developed ~\textit{\tool} to automatically recommend useful tools to software developers.
 We designed our system to make suggestions by integrating characteristics of peer interactions and concepts from the software engineering industry.
-To evaluate the effectiveness of our system, we studied the following research questions (RQs): \\
+We seek to answer the following research questions (RQs): \\
 
 \noindent
-\textbf{RQ1:} How often can we expect \tool~to make recommendations?  \\
+\textbf{RQ1:} How applicable is \tool~to real-world software applications?  \\ 
 \textbf{RQ2:} How useful are recommendations from \tool~to developers?  \\
 
-To answer these questions, we evaluated our system on open source Java projects to observe how many tool suggestions would be made based on past changes to the code base.
-We also examined how software developers reacted to receiving tool recommendations from our system.
-The main research contribution of our work is introducing the design and evaluation of a new automated recommendation system \tool, a novel approach to improving the discovery of static analysis tools for software engineers by simulating tool recommendations made between peers.
+To answer these questions, we evaluated our system by recommending a static analysis tool on open source Java projects.
+We observed the frequency of recommendations made based on developer changes to a code base and also examined how software developers reacted to receiving a suggestion from our system.
+This research makes the following contributions:
+
+\begin{itemize}
+ \item a novel automated recommendation system \tool~ that allows researchers to recommend software development tools to GitHub developers, and
+ \item an evaluation of the applicability and usefulness of our approach using the \textsc{Error Prone} static analysis tool
+ \end{itemize}
 
@@
 \section{Tool}
-Our approach to improving tool discovery, \tool, aims to increase awareness and use of programming tools among software developers. This section describes the design and implementation of our system.
+Our approach to improving tool discovery, \tool, aims to increase awareness and use of programming tools among software developers. This section describes the design and implementation of our system.s
 

### 2018-01-30 paper/paper.tex
Updates to introduction

@@
 
-To solve the tool discovery problem, we developed ~\textit{\tool} to automatically recommend useful tools to software developers.
-We designed our system to make suggestions by integrating characteristics of peer interactions and concepts from the software engineering industry.
-We seek to answer the following research questions (RQs): \\
+To help solve the tool discovery problem, we developed \textit{\tool} to automatically recommend useful tools to software developers.
+We designed our system to make suggestions by integrating characteristics of peer interactions found in previous work as well as concepts from software engineering.
+\tool contains a unique workflow that runs specific tools and makes customized recommendations to developers on GitHub\footnote{https://github.com}, the most popular code hosting site for collaborative software development.
+This work seeks to answer the following research questions (RQs): \\
 
@@
 
-To answer these questions, we evaluated our system by recommending a static analysis tool on open source Java projects.
-We observed the frequency of recommendations made based on developer changes to a code base and also examined how software developers reacted to receiving a suggestion from our system.
+To answer these questions, we evaluate \tool by recommending the \textsc{Error Prone}\footnote{http://errorprone.info} static analysis tool on open source Java GitHub projects.
+We observed the frequency of recommendations made and examined how software developers reacted to receiving a suggestion from our system.
 This research makes the following contributions:
@@
 \begin{itemize}
- \item a novel automated recommendation system \tool~ that allows researchers to recommend software development tools to GitHub developers, and
- \item an evaluation of the applicability and usefulness of our approach using the \textsc{Error Prone} static analysis tool
+ \item a novel automated recommendation system \tool~that allows researchers to recommend software development tools to GitHub developers, and
+ \item an evaluation on the applicability and usefulness of our approach using \textsc{Error Prone}
  \end{itemize}
@@
 
-To target this desire of mistake-free code, our initial implementation of \tool~automatically recommends the tool \textsc{Error Prone}.\footnote{http://errorprone.info} \textsc{Error Prone} is a static analysis tool created by Google to check for errors in Java code based on a suite of bug patterns.
+To target this desire of mistake-free code, our initial implementation of \tool~automatically recommends the tool \textsc{Error Prone}.
+\textsc{Error Prone} is a static analysis tool created by Google to check for errors in Java code based on a suite of bug patterns.
 Static analysis tools like \textsc{Error Prone} are useful for debugging and preventing errors in source code for applications, however they are often underutilized by software engineers~\cite{Johnson2013Why}.

### 2018-02-07 com/chbrown13/pull_rec/PullRecommender.java
Search script updates for eval

@@ -3,6 +3,7 @@ package com.chbrown13.pull_rec;
 import com.jcabi.github.*;
 import com.jcabi.http.response.JsonResponse;
 import java.io.*;
+import java.net.*;
 import java.util.*;
 import java.util.concurrent.TimeUnit;
 import javax.json.*;
@@ -13,7 +14,33 @@ import javax.json.*;
  */
 public class PullRecommender {
 
-	private static int year = 2008;
+	private static int year = 2014;
+
+	private static String url = "https://raw.githubusercontent.com/{user}/{repo}/master/pom.xml";
+
+	private static boolean wgetErrorProne(String user, String repo) {
+		String fileUrl = url.replace("{user}", user).replace("{repo}", repo);
+		String s = "";
+		try {
+			URL url = new URL(fileUrl);
+			InputStream in;
+			try {
+				in = url.openStream();
+			} catch (FileNotFoundException e) {
+				//File URL does not exist, possibly new file in PR
+				in = new ByteArrayInputStream("".getBytes("UTF-8"));
+			}
+			BufferedReader br = new BufferedReader(new InputStreamReader(in));
+			while ((s = br.readLine()) != null) {
+				if (s.contains("com.google.errorprone")) {
+					return false;
+				}
+			}
+		} catch (IOException e) {
+			e.printStackTrace();
+		}
+		return true;
+	}
 
 	private static String getDates(int month) {
 		String date = "{y1}-{m1}-01..{y2}-{m2}-01";
@@ -46,71 +73,68 @@ public class PullRecommender {
 				.replace("{m1}", Integer.toString(m1))
 				.replace("{m2}", Integer.toString(m2));
 		}
+		System.out.println(date);
 		return date;
 	}
 
 	public static void main(String[] args) {
 		int n = 0;
 		int x = 0;
-		int month = 2;
+		int month = 1;
+		int pg = 1;
 		final Github github = new RtGithub("chbrown13", "git_down1");
+		ArrayList<String> projects = new ArrayList<String>();
 		try { 
 			while (true) {
 				final JsonResponse resp = github.entry()
 					.uri().path("/search/repositories")
 					.queryParam("q", "language:java created:{date}".replace("{date}", getDates(month)))
+					.queryParam("per_page", 100)
+					.queryParam("page", pg)
 					.queryParam("sort", "forks")
 					.queryParam("order", "desc").back()
 					.fetch()
 					.as(JsonResponse.class);
-				month += 1;
[…]

### 2018-02-07 com/chbrown13/pull_rec/Utils.java
If no log avoid null pointer exception

@@ -511,6 +511,9 @@ public class Utils {
 		}
 		addToolPomPlugin(dirName, tool);
 		String log = compile(dirName);
+		if (log == null) {
+			return null;
+		}
 		return tool.parseOutput(log);
 	}
 

### 2018-02-07 com/chbrown13/pull_rec/PullRecommender.java
Update

@@ -14,7 +14,7 @@ import javax.json.*;
  */
 public class PullRecommender {
 
-	private static int year = 2014;
+	private static int year = 2016;
 
 	private static String url = "https://raw.githubusercontent.com/{user}/{repo}/master/pom.xml";
 

### 2018-02-07 com/chbrown13/pull_rec/Utils.java
Adding email creds

@@ -572,8 +572,10 @@ public class Utils {
 		catch (FileNotFoundException e) {
 		    e.printStackTrace();
 		}
-		setUserName(creds[0]);
-		setPassword(creds[1]);
+		if (filename.contains("github")) {
+			setUserName(creds[0]);
+			setPassword(creds[1]);
+		}
 		return creds;
 	}
 }

### 2018-02-08 com/chbrown13/pull_rec/Utils.java
More logging for vcl tests

@@ -367,11 +367,13 @@ public class Utils {
 	public static String compile(String path) {
 		String output = "";
 		String cmd = MVN_COMPILE.replace("{dir}", path);
+		System.out.println(cmd)
 		try {
 			Process p = Runtime.getRuntime().exec(cmd);	
 			BufferedReader br = new BufferedReader(new InputStreamReader(p.getErrorStream()));
 			String line;
 			while ((line = br.readLine()) != null) {
+				System.out.println(line);
 			    output += line + "\n";
 			}
 		} catch (IOException e) {
@@ -410,7 +412,8 @@ public class Utils {
 						if(qName.equals("plugins")) {
 							writer.write(tool.getPlugin());
 							writer.write("\n</plugins>");	
-							myTool = true;							
+							myTool = true;			
+							System.out.println(tool.getPlugin());				
 						} else if (qName.equals("project") && !myTool) {
 							writer.write(String.join("\n", "<build>", "<plugins>", 
 								tool.getPlugin(), "</plugins>", "</build>", "</project>"));

### 2018-02-08 paper/paper.tex

@@
 \hyphenation{op-tical net-works semi-conduc-tor}
-\IEEEoverridecommandlockouts
 \raggedbottom
@@
 \begin{abstract}
-Software contains a variety of useful tools and features designed to increase productivity that are often ignored or undiscovered by users.
+Software developers have access to a variety of useful tools designed to increase productivity that are often ignored or undiscovered by potential users.
 This lack of tool awareness can have dangerous consequences, especially in the software engineering industry.
-Automated recommendation systems have been created to software tool discovery, however these systems are not as effective as user-to-user recommendations.
-To improve the effectiveness of recommender systems, we implemented \textit{\tool}, a novel system which allows toolsmiths to increase discovery of software engineering tools by integrating aspects of peer interactions, and found that our approach is useful in making recommendations and increasing awareness of a static analysis tool to programmers on 800+ GitHub projects.
+Automated recommendation systems have been created in an attempt to improve software tool discovery, however these systems are still less effective than user-to-user recommendations.
+To increase awareness of helpful tools, we introduce \textit{\tool}, a novel system which integrates concepts from peer interactions and software development processes to increase discovery of software engineering tools, and found that our approach is useful in making recommendations and improving tool discovery of a static analysis tool to Java developers on open source GitHub projects.
 \end{abstract}
@@
 
-Software is increasingly prevelant throughout society.
-To keep up with the increasing demand for technology, software quality has become an increasingly important metric for software development teams.
-Processes such as peer code reviews, unit tests, continuous integration, test automation, and more have been implemented to ensure software maintains a high quality.
+Software is becoming more and more prevalent throughout our society.
+To keep up with the increasing demands for technology, software engineers are making efforts to emphasize \textbf{definition}, or \textit{software quality}.
+This includes more focus on improving metrics that impact both software producers and consumers, such as functionality, reliability, usability, efficiency, maintainability, and portability~\cite{KitchenhamQualityTarget}.
+However, despite increased attention to software quality, defects in code remains a persisting and escalating problem.
 
-Despite increased attention to the quality of code, the process of finding and fixing bugs in software, or debugging, is becoming more time-consuming and costly.
-A study by the National Institute of Standards and Technology reported that software engineers spend 70-80\% of their time at work debugging, and on average it takes 17.4 hours to debug one error~\cite{NIST}.
-Additionally, these errors can cost companies millions of dollars.
-For example, a recent bug found in the cryptocurrency Ethereum resulted in the loss of \$30 million.\footnote{https://qz.com/1034321/ethereum-hack-a-coding-error-led-to-30-million-in-ethereum-being-stolen/} Additionally, studies have shown the price of repairing these code failures becomes more expensive the longer the bug exists~\cite{SEEconomics}.
-%TODO: find better example
+The 2017 Software Fail Watch by Tricentis, a software testing company, discovered that software failures impacted approximaltely half of the world's population (3.7 billion users) and caused \$1.7 trillion in financial losses.\footnote{https://www.tricentis.com/software-fail-watch/} Additionally, the process of finding and fixing bugs in code, or debugging, is becoming increasingly time-consuming and costly.
+A study by the National Institute of Standards and Technology reported that software engineers spend 70-80\% of their time debugging at work, and one error takes an average of 17.4 hours to debug~\cite{NIST}.
+Studies also show the cost of fixing an error becomes more expensive the longer a bug exists in source code~\cite{SEEconomics, SoftwareAssuranceSDLC}.
 
-To make software engineers more effective and efficient in their work, many types of tools have been created to automatically perform code analysis, refactoring, security checks, and more for programmers.
-One such type is static analysis tools.
-Static analysis tools can improve software quality by automatically inspecting code without running the program.
-These tools can be useful for finding code defects early in the development process before code is released.
-According to a report from IBM, the relative cost for fixing errors also drastically increases the longer the fault exists in the code base through the software development lifecycle~\cite{SoftwareAssuranceSDLC}.
-Previous studies also show that static analysis tools are effective in preventing bugs in code to save money for companies in addition to time and effort for developers~\cite{UsingStaticAnalysis}.
+To prevent production errors and improve code quality, researchers and toolsmiths have created software engineering tools to aid developers in their work.
+These useful tools provide a variety of functionality to save time and effort for software engineers in programming tasks, such as finding defects, identifying bugs, making large-scale code changes, suggesting fixes, and checking for security vulnerabilities.
+Research shows that tools for static analysis~\cite{UsingStaticAnalysis}, refactoring~\cite{Murphy-HillFitness}, security, code navigation, and more are effective in preventing defects and improving software quality, ultimately leading to reduced debugging costs and increased developer productivity.
 
-Althouth quality is a primary concern for software producers and consumers, developers often ignore these useful tools which help improve the quality of their code~\cite{Johnson2013Why}.
-There are many barriers to tool adoption, and one of the main reasons useful tools are ignored or underutilized is the discoverability barrier.
-This refers to when users are unaware of a tool's existence within software~\cite{Murphy-HillScreencastingDiscovery}.
-The tool discovery problem will continue to persist as applications become more ``bloated'' with features~\cite{SoftwareBloat}.
-This lack of awareness of static analysis tools can lead to significant amounts of wasted time and money in the software industry.
+Althouth quality is a primary concern for software producers and consumers, developers often ignore useful tools designed to help improve the quality of their code~\cite{Johnson2013Why}.
+There are many barriers to tool adoption, but one of primary reason useful tools are underused or ignored is the discoverability barrier, or when users are unaware of a tool's existence~\cite{Murphy-HillScreencastingDiscovery}.
+This lack of awareness can lead to poor code quality and significant amounts of wasted time and money fixing bugs.
+To improve tool discovery, automated recommendation systems have been created to
+
+%Peer
 
@@
 
-To answer these questions, we evaluate \tool by recommending the \textsc{Error Prone}\footnote{http://errorprone.info} static analysis tool on open source Java GitHub projects.
+To answer these questions, we evaluate \tool~by recommending the \textsc{Error Prone}\footnote{http://errorprone.info} static analysis tool on open source Java GitHub projects.
 We observed the frequency of recommendations made and examined how software developers reacted to receiving a suggestion from our system.

### 2018-02-08 com/chbrown13/pull_rec/Utils.java
typo

@@ -367,7 +367,7 @@ public class Utils {
 	public static String compile(String path) {
 		String output = "";
 		String cmd = MVN_COMPILE.replace("{dir}", path);
-		System.out.println(cmd)
+		System.out.println(cmd);
 		try {
 			Process p = Runtime.getRuntime().exec(cmd);	
 			BufferedReader br = new BufferedReader(new InputStreamReader(p.getErrorStream()));

### 2018-02-08 paper/paper.tex
Intro updates, almost done

@@
 \begin{abstract}
-Software developers have access to a variety of useful tools designed to increase productivity that are often ignored or undiscovered by potential users.
+Software developers have access to numerous tools designed to increase productivity by automatically performing development tasks, but these tools are often ignored or undiscovered by programmers.
 This lack of tool awareness can have dangerous consequences, especially in the software engineering industry.
-Automated recommendation systems have been created in an attempt to improve software tool discovery, however these systems are still less effective than user-to-user recommendations.
-To increase awareness of helpful tools, we introduce \textit{\tool}, a novel system which integrates concepts from peer interactions and software development processes to increase discovery of software engineering tools, and found that our approach is useful in making recommendations and improving tool discovery of a static analysis tool to Java developers on open source GitHub projects.
+Automated recommendation systems were created to improve tool discovery, however these systems are not as effective as user-to-user recommendations.
+To increase awareness of helpful development tools, we introduce \textit{\tool}, a novel system that integrates concepts of peer interactions and software engineering practices to increase tool discovery by effectively making recommendations to developers on open source GitHub projects.
 \end{abstract}
@@
 To keep up with the increasing demands for technology, software engineers are making efforts to emphasize \textbf{definition}, or \textit{software quality}.
-This includes more focus on improving metrics that impact both software producers and consumers, such as functionality, reliability, usability, efficiency, maintainability, and portability~\cite{KitchenhamQualityTarget}.
+Throughout the software development life cycle, more focus is being put on metrics that impact both software producers and consumers such as functionality, reliability, usability, efficiency, maintainability, and portability~\cite{KitchenhamQualityTarget}.
 However, despite increased attention to software quality, defects in code remains a persisting and escalating problem.
@@
 
-To prevent production errors and improve code quality, researchers and toolsmiths have created software engineering tools to aid developers in their work.
-These useful tools provide a variety of functionality to save time and effort for software engineers in programming tasks, such as finding defects, identifying bugs, making large-scale code changes, suggesting fixes, and checking for security vulnerabilities.
-Research shows that tools for static analysis~\cite{UsingStaticAnalysis}, refactoring~\cite{Murphy-HillFitness}, security, code navigation, and more are effective in preventing defects and improving software quality, ultimately leading to reduced debugging costs and increased developer productivity.
+To improve code quality and prevent errors, researchers and toolsmiths have created numerous software engineering tools to aid developers in their work.
+These tools automatically perform a wide variety of software development tasks to save time and effort for programmers.
+Research shows that tools for static analysis~\cite{UsingStaticAnalysis}, refactoring~\cite{Murphy-HillFitness}, security, code navigation, and more are beneficial for preventing errors and improving software quality.
+Ultimately, these useful tools can lead to reduced debugging costs and increased developer productivity.
 
-Althouth quality is a primary concern for software producers and consumers, developers often ignore useful tools designed to help improve the quality of their code~\cite{Johnson2013Why}.
-There are many barriers to tool adoption, but one of primary reason useful tools are underused or ignored is the discoverability barrier, or when users are unaware of a tool's existence~\cite{Murphy-HillScreencastingDiscovery}.
-This lack of awareness can lead to poor code quality and significant amounts of wasted time and money fixing bugs.
-To improve tool discovery, automated recommendation systems have been created to
-
-%Peer
+Althouth quality is a primary concern for software engineers and users, developers rarely use tools designed to improve code~\cite{Johnson2013Why}.
+There are many barriers to tool adoption, and one of the primary reasons useful tools are underused or ignored is the discoverability barrier, or when users are unaware of a tool's existence~\cite{Murphy-HillScreencastingDiscovery}.
+This lack of awareness for software engineering tools can lead to poor code quality, harmed users, and significant amounts of time and money spent fixing errors.
+While many automated approaches have been developed to increase knowledge of useful software tools and features, Murphy-Hill and colleagues found that learning about tools from colleagues during normal work activities, or \textit{peer interactions}, is the most effective mode of tool discovery\cite{MurphyHill2011PeerInteraction}.
 
@@
 
-To help solve the tool discovery problem, we developed \textit{\tool} to automatically recommend useful tools to software developers.
-We designed our system to make suggestions by integrating characteristics of peer interactions found in previous work as well as concepts from software engineering.
-\tool contains a unique workflow that runs specific tools and makes customized recommendations to developers on GitHub\footnote{https://github.com}, the most popular code hosting site for collaborative software development.
-This work seeks to answer the following research questions (RQs): \\
+To help solve the tool discovery problem among software developers, we developed \textit{\tool} to automatically recommend software engineering tools.
+Our system makes recommendations by integrating characteristics of peer interactions and software engineering practices.
+\tool~is designed for toolsmiths to increase awareness of their work by automatically running tools and making customized recommendations to developers of GitHub\footnote{https://github.com} projects.
+This paper seeks to answer the following research questions (RQs): \\
 
@@
 
-To answer these questions, we evaluate \tool~by recommending the \textsc{Error Prone}\footnote{http://errorprone.info} static analysis tool on open source Java GitHub projects.
-We observed the frequency of recommendations made and examined how software developers reacted to receiving a suggestion from our system.
+To answer these questions, we evaluated \tool~by recommending \textsc{Error Prone}\footnote{http://errorprone.info}, an open source static analysis tool for Java code.
+We examined how often recommendations were made and how developers reacted to receiving suggestions from our system.
 This research makes the following contributions:
@@
 \begin{itemize}
- \item a novel automated recommendation system \tool~that allows researchers to recommend software development tools to GitHub developers, and
- \item an evaluation on the applicability and usefulness of our approach using \textsc{Error Prone}
+ \item a novel system for researchers to recommend software engineering tools on GitHub, and
+ \item an evaluation on the effectiveness of \tool~with \textsc{Error Prone}
  \end{itemize}

### 2018-02-08 com/chbrown13/pull_rec/Utils.java
Adding sudo back

@@ -42,7 +42,7 @@ public class Utils {
 
 	public static String SURVEY = "[How useful was this recommendation?](https://ncsu.qualtrics.com/jfe/form/SV_4JGXYBRyb3GeF5X?project={project}&pr={pull})";
 
-	private static String MVN_COMPILE = "mvn -q -f {dir}/pom.xml compile";
+	private static String MVN_COMPILE = "sudo mvn -q -f {dir}/pom.xml compile";
 
 	private static String currentDir = System.getProperty("user.dir");
 

### 2018-02-08 com/chbrown13/pull_rec/Utils.java
More print statements for testing

@@ -541,6 +541,7 @@ public class Utils {
 	 */
 	public static void cd(String dir) throws FileNotFoundException {
 		String cmd = "cd " + dir;
+		System.out.println(cmd);
 		try {
 			Process p = Runtime.getRuntime().exec(cmd);		
 			if(!dir.equals("..")) {
@@ -548,6 +549,7 @@ public class Utils {
 			} else {
 				currentDir = currentDir.substring(0, currentDir.lastIndexOf("/"));
 			}
+			System.out.println(currentDir);
 		} catch (IOException e) {
 			throw new FileNotFoundException("Invalid directory name "+dir);			
 		}

### 2018-02-08 com/chbrown13/pull_rec/Utils.java
VCL fix test mvn

@@ -42,7 +42,7 @@ public class Utils {
 
 	public static String SURVEY = "[How useful was this recommendation?](https://ncsu.qualtrics.com/jfe/form/SV_4JGXYBRyb3GeF5X?project={project}&pr={pull})";
 
-	private static String MVN_COMPILE = "sudo mvn -q -f {dir}/pom.xml compile";
+	private static String MVN_COMPILE = "mvn -q -f {dir}/pom.xml compile";
 
 	private static String currentDir = System.getProperty("user.dir");
 

### 2018-02-08 paper/paper.tex
Intro updating

@@
 Software is becoming more and more prevalent throughout our society.
-To keep up with the increasing demands for technology, software engineers are making efforts to emphasize \textbf{definition}, or \textit{software quality}.
+To keep up with the increasing demands for technology, software engineers are making efforts to emphasize \textbf{---}, or \textit{software quality}.
 Throughout the software development life cycle, more focus is being put on metrics that impact both software producers and consumers such as functionality, reliability, usability, efficiency, maintainability, and portability~\cite{KitchenhamQualityTarget}.
@@
 
-To help solve the tool discovery problem among software developers, we developed \textit{\tool} to automatically recommend software engineering tools.
+To help solve the tool discovery problem among software engineers, we developed \textit{\tool}, a system to automatically recommend development tools.
 Our system makes recommendations by integrating characteristics of peer interactions and software engineering practices.
-\tool~is designed for toolsmiths to increase awareness of their work by automatically running tools and making customized recommendations to developers of GitHub\footnote{https://github.com} projects.
+\tool~is designed for toolsmiths to increase awareness of their work by automatically running tools and making customized recommendations to developers on GitHub\footnote{https://github.com} projects.
 This paper seeks to answer the following research questions (RQs): \\

### 2018-02-09 eval_scripts/setup.sh
Removing extra setup cmds

@@ -2,23 +2,6 @@
 sudo yum -y install epel-release
 sudo yum -y update
 
-# Install commands
-sudo yum -y install wget
-sudo yum -y install unzip
-sudo yum -y install python-pip
-sudo pip install --upgrade pip
-sudo pip install paramiko
-
-# Install Java
-sudo yum -y install java-1.8.0-openjdk.x86_64
-sudo cp /etc/profile /etc/profile_backup
-echo 'export JAVA_HOME=/usr/lib/jvm/jre-1.8.0-openjdk' | sudo tee -a /etc/profile
-echo 'export JRE_HOME=/usr/lib/jvm/jre' | sudo tee -a /etc/profile
-source /etc/profile
-echo $JAVA_HOME
-echo $JRE_HOME
-cd ~
-
 # Install and Start Jenkins
 sudo wget -O /etc/yum.repos.d/jenkins.repo https://pkg.jenkins.io/redhat-stable/jenkins.repo
 sudo rpm --import https://pkg.jenkins.io/redhat-stable/jenkins.io.key
@@ -33,17 +16,6 @@ wget http://localhost:8080/jnlpJars/jenkins-cli.jar
 wget http://mirror.olnevhost.net/pub/apache/maven/maven-3/3.0.5/binaries/apache-maven-3.0.5-bin.tar.gz
 tar xvf apache-maven-3.0.5-bin.tar.gz
 sudo mv apache-maven-3.0.5  /usr/local/apache-maven
-export M2_HOME=/usr/local/apache-maven
-export M2=$M2_HOME/bin 
-export PATH=$M2:$PATH
-source ~/.bashrc
-echo "JAVA_HOME=$(readlink -f /usr/bin/java | sed "s:bin/java::")" | sudo tee -a /etc/profile
-source /etc/profile
-
-# Install Groovy
-sudo yum -y install groovy
-
-# Create Jenkins user
 
 # Install Ansible
 sudo yum -y install ansible
@@ -55,5 +27,5 @@ wget https://raw.githubusercontent.com/chbrown13/PullRecommender/master/eval_scr
 wget https://gist.githubusercontent.com/chbrown13/ca345f0d96401144373b745975724412/raw/72cf4f75ec85bc9ad94c1e072965c797503e52b9/.projects_ssh
 wget https://raw.githubusercontent.com/chbrown13/PullRecommender/master/jenkins.xml
[…]

### 2018-02-09 com/chbrown13/pull_rec/PullRecommender.java
Updates to logging

@@ -49,7 +49,7 @@ public class PullRecommender {
 			email.setMsg(String.join("\n", viewChanges, text));
 			email.addTo("dcbrow10@ncsu.edu");
 			email.send();		
-			System.out.println("Email sent for review.");	
+			System.out.println("Email sent for review: " + subject);	
 		} catch (Exception e) {
 			e.printStackTrace();
 		}

### 2018-02-09 com/chbrown13/pull_rec/PullRecommender.java
Search script updates

@@ -14,8 +14,7 @@ import javax.json.*;
  */
 public class PullRecommender {
 
-	private static int year = 2016;
-
+	private static int year = 2013;
 	private static String url = "https://raw.githubusercontent.com/{user}/{repo}/master/pom.xml";
 
 	private static boolean wgetErrorProne(String user, String repo) {
@@ -82,7 +81,7 @@ public class PullRecommender {
 		int x = 0;
 		int month = 1;
 		int pg = 1;
-		final Github github = new RtGithub("chbrown13", "git_down1");
+		final Github github = new RtGithub("<username>", "<password>");
 		ArrayList<String> projects = new ArrayList<String>();
 		try { 
 			while (true) {

### 2018-02-09 paper/paper.tex
Related work paper updates

@@
 
-%Researchers have explored methods for increasing tool discovery among software users.
-Fischer suggests that some of the more popular methods for raising tool awareness, such as documentation and help menus, are ineffective for increasing adoption of useful tools and features~\cite{ActiveHelpSystems}.
-These \textit{passive help systems} require users to first recognize the system's existence, navigate to the items, and then manually search for help.
-However, users rarely seek help by discovering new functionality and will often just rely on their own previous knowledge~\cite{something}.
-%
-%Active help systems are the preferred method of helping users discover new functionality in software.
-These systems automatically recommend useful tools to software users.
-However, there remains room for improvement among these system-to-user recommendation systems.
-For example, Clippy, an intelligent office assistant for Microsoft Office products, was able to automatically suggest tools and features to Microsoft software users.
-However, the system was found ineffective and eventually removed.
-Peer interactions and receptiveness are effective~\cite{vlhcc17}...
-Previous research has shown that user-to-user recommendations are the most effective mode of increasing awareness of tools among software users~\cite{MurphyHill2011PeerInteraction}
-
 To help solve the tool discovery problem among software engineers, we developed \textit{\tool}, a system to automatically recommend development tools.
@@
 
-Our approach is based on previous research examining how users learn about and discover tools, the lack of tool adoption among software engineers, and existing automated tool recommendation systems.
+Our implementation of \tool~builds on previous research examining tool discovery, lack of tool adoption among software engineers, and automated recommendation systems.
 
-Researchers have explored ways humans learn about new tools.
-Prior work in diffusion of innovations~\cite{Rogers2003Diffusion} and persuasion theory~\cite{Shen2012Persuasion} show that the way messages are communicated impacts reception.
-There are a numerous methods for discovering tools in software, however, research suggests that recommendations from peers, or \textit{peer interactions}, are the most effective.
-Murphy-Hill found that peer interactions were the most effective mode of tool discovery among software engineers compared to chance encounters, tutorials, descriptions, social media, or discussion threads~\cite{MurphyHill2011PeerInteraction}~\cite{Murphy-Hill2015HowDoUsers}.
-Similarly, Welty discovered that software users sought help from colleagues more than search engines and help menus~\cite{Welty2011Help}.
-Our work builds on the results of these studies by integrating qualities of effective peer-to-peer recommendations into an automated recommendation system.
+Researchers have explored how humans learn about new tools.
+There are various methods to discover tools in software, and research suggests recommendations between peers is the most effective way to increase tool awareness.
+Murphy-Hill found that peer interactions were the most effective mode of tool discovery compared to tool encounters, tutorials, descriptions, social media, and discussion threads~\cite{MurphyHill2011PeerInteraction}~\cite{Murphy-Hill2015HowDoUsers}.
+Similarly, Welty discovered that software users sought help from colleagues more often than search engines and help menus~\cite{Welty2011Help}.
+To improve the effectiveness of recommendations from our system, we integrate qualities of peer interactions into \tool.
 
-Previous work has explored the tool adoption problem in software engineering and barriers preventing developers from adopting useful tools for important programming tasks.
+Previous work has also explored the tool discovery problem and barriers preventing users from adopting new tools, specifically in the software engineering industry.
 Researchers have created numerous tools to aid software engineers in their work, but these products are often ignored by developers~\cite{Ivanov2017Gaps}.
@@
 Xiao and colleagues examined barriers and social influences blocking developers from using security tools to detect and prevent vulnerabilities and malicious attacks~\cite{Xiao2014Security}.
-Our project aims to increase software engineer tool adoption by developing \tool~to automatically and effectively recommend useful tools to help complete development tasks.
+Our project aims to increase tool discovery and adoption among developers by automatically recommending useful software enginering tools.
 
-Additionally, there are numerous existing technical approaches created to improve the tool discovery problem.
-Researchers have developed several active help systems using community involvement.
-Gordon and colleagues developed Codepourri, a system using crowdsourcing to collectively create Python tutorials~\cite{Gordon2015Codepourri}.
+There are numerous existing technical approaches created to solve the tool discovery problem.
+Fischer and colleagues found that systems requiring users to explicitly seek help, or passive help systems, are ineffective and active help systems are more useful for increasing tool awareness~\cite{Fischer1984ActiveHelpSystems}.
+Gordon and colleagues developed Codepourri, a system using crowdsourcing to make recommendations for Python code~\cite{Gordon2015Codepourri}.
 Linton and colleagues designed a recommender system called OWL (organization-wide learning) to disseminate tool knowledge using logs throughout a company~\cite{Linton2000OWL}.
@@
 Answer Garden helps users discover new tools based on common questions asked by colleagues~\cite{Ackerman1990AnswerGarden}.
-SpyGlass automatically recommends tools to help users navigate code~\cite{Viriyakattiyaporn2010Spyglass}
-
-Fischer and colleagues examined systems that require users to explicitly seek help from the software, or passive help systems~\cite{Fischer1984ActiveHelpSystems}.
-Fischer concluded technical passive recommendation systems, such as documentation and help menues, are ineffective and inefficient for users.
-Instead, active help systems are more useful for increasing tool awareness.
+SpyGlass automatically recommends tools to help users navigate code~\cite{Viriyakattiyaporn2010Spyglass}.
 We developed \tool~to actively suggest useful programming tools and increase awareness for software engineers.

### 2018-02-09 eval_scripts/eval.py
No longer using paramiko ssh

@@ -1,4 +1,4 @@
-import paramiko
+N = 100
 
 def jenkins(user, repo):
     with open("jenkins.xml") as f:
@@ -6,23 +6,10 @@ def jenkins(user, repo):
     config = config.replace("{user}", user).replace("{repo}", repo)
     return config
 
-def connection():
-    with open(".projects_ssh") as f:
-        connect = f.readlines()
-    return [c.replace("\n", "") for c in connect]
-
-def ssh():
-    ssh = paramiko.SSHClient()
-    ssh.load_system_host_keys()
-    ssh.set_missing_host_key_policy(paramiko.AutoAddPolicy())
-    conn = connection()
-    ssh.connect(conn[0], username=conn[1], password=conn[2])
-    ssh_stdin, stdout, stderr = ssh.exec_command("python projects.py")
-    return stdout.readlines()
-
 def main():
     i = 0
-    projects = [x for x in ssh() if x != '\n']
+    with open("projects.txt") as f:
+        projects = f.readlines()
     for p in projects:
         git = p.replace("\n","").split("/")
         if git:

### 2018-02-09 com/chbrown13/pull_rec/PullRecommender.java
Only write to file if unique

@@ -111,14 +111,14 @@ public class PullRecommender {
 								System.out.print(coords);
 								projects.add(coords);
 								x += 1;	
+								try {
+									PrintWriter out = new PrintWriter(new BufferedWriter(new FileWriter("projects.txt", true)));
+									out.println(coords);
+									out.close();
+								} catch (IOException e) {
+									e.printStackTrace();
+								}
 							}						
-							try {
-								PrintWriter out = new PrintWriter(new BufferedWriter(new FileWriter("projects.txt", true)));
-								out.println(coords);
-								out.close();
-							} catch (IOException e) {
-								e.printStackTrace();
-							}
 						}		
 						n += 1;
 						System.out.println(n);			

### 2018-02-10 com/chbrown13/pull_rec/PullRecommender.java
Search script for eval

@@ -14,7 +14,7 @@ import javax.json.*;
  */
 public class PullRecommender {
 
-	private static int year = 2013;
+	private static int year = 2008;
 	private static String url = "https://raw.githubusercontent.com/{user}/{repo}/master/pom.xml";
 
 	private static boolean wgetErrorProne(String user, String repo) {
@@ -78,8 +78,7 @@ public class PullRecommender {
 
 	public static void main(String[] args) {
 		int n = 0;
-		int x = 0;
-		int month = 1;
+		int month = 2;
 		int pg = 1;
 		final Github github = new RtGithub("<username>", "<password>");
 		ArrayList<String> projects = new ArrayList<String>();
@@ -97,9 +96,10 @@ public class PullRecommender {
 				JsonArray items = resp.json().readObject().getJsonArray("items");
 				System.out.println(pg);
 				pg += 1;
-				if (items == null || items.isEmpty()) {
-					System.out.println(resp);
-					break;
+				if (items.isEmpty()) {
+					pg = 1;
+					month++;
+					continue;
 				} else {
 					final List<JsonObject> repos = items.getValuesAs(JsonObject.class);
 					System.out.println(repos.size());
@@ -110,7 +110,6 @@ public class PullRecommender {
 							if(!projects.contains(coords)) {
 								System.out.print(coords);
 								projects.add(coords);
-								x += 1;	
 								try {
 									PrintWriter out = new PrintWriter(new BufferedWriter(new FileWriter("projects.txt", true)));
 									out.println(coords);
@@ -124,7 +123,7 @@ public class PullRecommender {
 						System.out.println(n);			
 					}	
 				}
-				if (pg % 5 == 0) {
+				if (pg == 5) {
 					pg = 1;
 					month += 1;
 				}		
@@ -133,7 +132,6 @@ public class PullRecommender {
 			e.printStackTrace();
 		}
 		System.out.println(n);
-		System.out.println(x);
 		System.out.println(projects.size());
 	}
 }

### 2018-02-10 eval_scripts/setup.sh
Run eval.py

@@ -27,5 +27,5 @@ wget https://raw.githubusercontent.com/chbrown13/PullRecommender/master/eval_scr
 wget https://gist.githubusercontent.com/chbrown13/ca345f0d96401144373b745975724412/raw/72cf4f75ec85bc9ad94c1e072965c797503e52b9/.projects_ssh
 wget https://raw.githubusercontent.com/chbrown13/PullRecommender/master/jenkins.xml
 wget https://raw.githubusercontent.com/chbrown13/PullRecommender/master/eval_scripts/eval.py
-# python eval.py
+python eval.py
 # sudo ansible-playbook tool-recommender-bot.yml

### 2018-02-11 paper/paper.tex
Updated project selection process in methodology

@@
 
-Our study evaluates the effectiveness of \tool~by analyzing how often our approach makes tool recommendations and how developers respond to recommendations they receive from our system.
+Our study evaluates the effectiveness of \tool~by analyzing how often our system recommends software engineering tools and how developers respond to recommendations from our system.
 
@@
 
-To determine the effectiveness of our approach, we used real-world open source software applications to evaluate \tool.
-Projects for our evaluation were selected from Github, which hosts millions of code repositories online.
-To narrow down the number of projects for our study, we chose repositories that met the following criteria:
+We used real-world open source software applications from GitHub to evaluate \tool.
+To choose projects for our study from the millions of GitHub repositories, we selected projects that met the following criteria:
 
 \begin{itemize}
-\item primarily written in Java,
-\item builds with Maven,
-\item and were ranked among the top 100 forked repositories for every month from February 2008 - December 2017.
+\item primariy written in Java,
+\item ranked as a 1000 forked repositoy for a month in the last 10 years,
+\item builds with Maven, and
+\item do not already utilize \textsc{Error Prone}.
 \end{itemize}
 
-\textsc{Error Prone} currently only analyzes Java code, so our search was restricted to open source Java projects on GitHub.
-Our study focused on Maven projects because it is a popular build system for Java projects and also contains an \textsc{Error Prone} plug-in.
-The current implementation of \tool~automatically implements this plug-in by modifying the \textit{pom.xml} file in the top directory.
-We selected the most forked repositories to collect popular projects with a lot of activity, and forking a repository is suggested as one of the GitHub best practices for contributing to a project\footnote{https://guides.github.com/activities/forking/}.
-Using a GitHub search API with the above constraints, we identified 917 projects for our evaluation.\footnote{\url{https://docs.google.com/spreadsheets/d/1MRmVPiUeDlYMa0UODzMmFbGeYBbahzdeEv1YSgqC1oo/edit?usp=sharing}}
+\textsc{Error Prone} only analyzes Java code, so our evaluation was limited to Java projects.
+We chose the most forked repositories to sample the most popular GitHub projects in terms of developer activity.
+Additionally, GitHub suggests forking a repository as a best practice for contributing and making pull requests to projects\footnote{https://guides.github.com/activities/forking/}.
+Maven is a build automation and dependency management system for Java projects.
+\tool~requires Maven to automatically modify \textit{pom.xml} files by adding the \textsc{Error Prone} plug-in and running the static analysis tool.
+Using a GitHub search API with the above constraints, we identified 2003 projects to use for our evaluation.\footnote{\url{https://docs.google.com/spreadsheets/d/1MRmVPiUeDlYMa0UODzMmFbGeYBbahzdeEv1YSgqC1oo/edit?usp=sharing}}
 
@@
 We designed our evaluation to gather quantitative and qualitative data addressing our research questions.
+To analyze 2000+ repositories simultaneously, we used Ansible\footnote{https://www.ansible.com/} to generate Jenkins jobs with \tool~running on multiple virtual machines.
 
@@
 To answer our first research question, we observed how often our approach makes recommendations on newly opened pull requests.
-To analyze the 917 repositories simultaneously, we used Ansible\footnote{https://www.ansible.com/} to install \tool~as a Jenkins job on multiple virtual machines.
 In addition to the frequency of recommendations, we also tracked instances where \textsc{Error Prone} defects were removed but not reported as fixed according to our fix identification algorithm in Section III.B.2, the number of occurrences where errors were fixed but no other instances of that bug were found in the code, and the false positive rate.

### 2018-02-12 com/chbrown13/pull_rec/PullRecommender.java
Add removed errors to emails too

@@ -17,8 +17,9 @@ public class PullRecommender {
 	private Repo repo;
 	private Set<Integer> prs = new HashSet<Integer>();	
 	private int recs = 0;;
-	private int removed = 0;
-	private int fixes = 0;
+	private int rem = 0;
+	private int fix = 0;
+	private String removed = "";
 
 	public PullRecommender(Repo repo) {
 		this.repo = repo;
@@ -109,6 +110,7 @@ public class PullRecommender {
 	 */
 	private void analyze(Pull.Smart pull) {
 		System.out.println("Analyzing PR #" + Integer.toString(pull.number()) + "...");
+		removed = "";
 		Tool tool = new ErrorProne();		
 		String developer = "";
 		boolean pullRec = false;
@@ -142,14 +144,15 @@ public class PullRecommender {
 				int i = 0;
 				for (Error e: fixed) {
 					if (isFix(baseErrors, pullErrors, e, javaFiles)) {
-						fixes += 1;			
+						fix += 1;			
 						int line = Utils.getFix(pull, e);			
 						System.out.println("Fixed "+ e.getKey() +" in PR #"+Integer.toString(pull.number())
 							+ " reported at line " + e.getLineNumberStr() + " possibly fixed at line " + Integer.toString(line));
 						
 						makeRecommendation(tool, pull, e, line, baseErrors);
 					} else {
-						removed += 1;
+						rem += 1;
+						removed += e.getError() + "\n";
 					}
 				}	
 			}
@@ -178,10 +181,11 @@ public class PullRecommender {
 				if (new Date().getTime() - pull.createdAt().getTime() <= TimeUnit.MILLISECONDS.convert(15, TimeUnit.MINUTES)) {
 					analyze(pull);					
 					requests.add(pull);
-					String out = "Recommendations: {rec}\nFixes: {fix}\nRemoved: {rem}"
+					String out = "Recommendations: {rec}\nFixes: {fix}\nRemoved: {rem}\n{err}"
 						.replace("{rec}", Integer.toString(recs))
-						.replace("{fix}", Integer.toString(fixes - recs))
-						.replace("{rem}", Integer.toString(removed));
+						.replace("{fix}", Integer.toString(fix - recs))
+						.replace("{rem}", Integer.toString(rem))
+						.replace("{err}", removed);
 					sendEmail(out, "New Pull Request", pull.number());						
 				} else {
 					System.out.println("No new pull requests");

### 2018-02-12 paper/paper.tex

@@
 \newcommand{\pseudosection}[1]{\vspace{2mm} \noindent {\bf #1}}
-\newcommand{\pseudosubsection}[1]{\vspace{2mm} {\it #1}}
+\newcommand{\pseudosubsection}[1]{\vspace{2mm} \noindent{\it #1}}
 
@@
 
-\subsection{Design}
+\pseudosection{Peer Interactions}
 Previous research shows that recommendations between peers is an effective way to increase tool discovery and adoption~\cite{MurphyHill2011PeerInteraction}.
@@
 
-\pseudosection{Receptiveness}
+\pseudosubsection{Receptiveness}
 
@@
 
-\pseudosubsection{1. Desire}
+\subsubsection{Desire}
 
@@
 
-\pseudosubsection{2. Familiarity}
+\subsubsection{Familiarity}
 
@@
 
-\subsection{Implementation}
+\pseudosection{Software Engineering}
 
@@
 
-\pseudosubsection{1. Continuous Integration}
+\pseudosubsection{Continuous Integration}
 
@@
 
-\pseudosubsection{2. Fix Identification}
+\pseudosubsection{Fix Identification}
 
@@
 
-\pseudosubsection{3. Fix Localizaton}
+\pseudosubsection{Fix Localizaton}
 
@@
 
-\pseudosubsection{4. Code Review}
+\pseudosubsection{Code Review}
 
@@
 
-We used real-world open source software applications from GitHub to evaluate \tool.
-To choose projects for our study from the millions of GitHub repositories, we selected projects that met the following criteria:
+We used real-world open source software applications to evaluate \tool. To choose study projects from the millions of GitHub repositories, we selected projects that met the following criteria:
 
@@
 \item primariy written in Java,
-\item ranked as a 1000 forked repositoy for a month in the last 10 years,
-\item builds with Maven, and
+\item ranked a top 1000 monthly forked repositoy in the last 10 years,
+\item build using Maven, and
 \item do not already utilize \textsc{Error Prone}.
@@
 
-\textsc{Error Prone} only analyzes Java code, so our evaluation was limited to Java projects.
 We chose the most forked repositories to sample the most popular GitHub projects in terms of developer activity.
-Additionally, GitHub suggests forking a repository as a best practice for contributing and making pull requests to projects\footnote{https://guides.github.com/activities/forking/}.
+Additionally, GitHub suggests forking repositories as a best practice for making contributions and pull requests to projects\footnote{https://guides.github.com/activities/forking/}.
+\textsc{Error Prone} only analyzes Java code, so this evaluation was limited to Java projects.
 Maven is a build automation and dependency management system for Java projects.
@@
 
-\pseudosection{RQ1}
+\pseudosubsection{RQ1}
 
@@
 
-\pseudosection{RQ2}
+\pseudosubsection{RQ2}
 

### 2018-02-19 paper/paper.tex
Updates to heading styles

@@
 
-\pseudosection{Peer Interactions}
+\subsection{Peer Interactions}
 Previous research shows that recommendations between peers is an effective way to increase tool discovery and adoption~\cite{MurphyHill2011PeerInteraction}.
@@
 Below we explain how \tool~was designed to recommend programming tools to software developers based on their desire and familiarity.
+\\
 
@@
 Static analysis tools like \textsc{Error Prone} are useful for debugging and preventing errors in source code for applications, however they are often underutilized by software engineers~\cite{Johnson2013Why}.
+\\
 
@@
 
-\pseudosection{Software Engineering}
+\subsection{Software Engineering}
 

### 2018-02-21 paper/paper.tex

@@
 \raggedbottom
-\newcommand{\tool}{tool-recommender-bot}
+\newcommand{\tool}{\textsl{tool-recommender-bot}}
 \newcommand{\pseudosection}[1]{\vspace{2mm} \noindent {\bf #1}}
@@
 This lack of awareness for software engineering tools can lead to poor code quality, harmed users, and significant amounts of time and money spent fixing errors.
-While many automated approaches have been developed to increase knowledge of useful software tools and features, Murphy-Hill and colleagues found that learning about tools from colleagues during normal work activities, or \textit{peer interactions}, is the most effective mode of tool discovery\cite{MurphyHill2011PeerInteraction}.
+While many automated approaches have been developed to increase knowledge of useful software tools and features, Murphy-Hill and colleagues found that learning about tools from colleagues during normal work activities, or \textit{peer interaction}, is the most effective mode of tool discovery~\cite{MurphyHill2011PeerInteraction}.
 
-To help solve the tool discovery problem among software engineers, we developed \textit{\tool}, a system to automatically recommend development tools.
-Our system makes recommendations by integrating characteristics of peer interactions and software engineering practices.
-\tool~is designed for toolsmiths to increase awareness of their work by automatically running tools and making customized recommendations to developers on GitHub\footnote{https://github.com} projects.
+To help solve the tool discovery problem among software engineers, we developed \tool.
+Our system automatically recommends development tools by integrating characteristics of peer interactions and software engineering practices.
+\tool~is designed for toolsmiths to increase awareness of their products by systematically running their tools and making customized recommendations to developers on GitHub\footnote{https://github.com}, the largest code hosting platform in the world~\cite{GousiosGitHub}.
 This paper seeks to answer the following research questions (RQs): \\
@@
 
-To answer these questions, we evaluated \tool~by recommending \textsc{Error Prone}\footnote{http://errorprone.info}, an open source static analysis tool for Java code.
+To answer these questions, we evaluated \tool~by recommending \textsc{Error Prone}\footnote{http://errorprone.info}, an open source Java static analysis tool.
 We examined how often recommendations were made and how developers reacted to receiving suggestions from our system.
@@
 \section{Tool}
-Our approach to improving tool discovery, \tool, aims to increase awareness and use of programming tools among software developers. This section describes the design and implementation of our system.s
+Our approach to improving tool discovery, \tool, aims to increase awareness and use of programming tools among software developers. This section describes the design and implementation of our system.
 
@@
 However, despite the existence of effective tools for detecting errors, the number of bugs in software is increasing~\cite{HaveThingsChanged}.
-We aim to increase awareness of these tools to improve software quality and developer productivity, ultimately meeting users' and developers' desire for less buggy software.
-
-To target this desire of mistake-free code, our initial implementation of \tool~automatically recommends the tool \textsc{Error Prone}.
-\textsc{Error Prone} is a static analysis tool created by Google to check for errors in Java code based on a suite of bug patterns.
-Static analysis tools like \textsc{Error Prone} are useful for debugging and preventing errors in source code for applications, however they are often underutilized by software engineers~\cite{Johnson2013Why}.
+We aim to increase tool discovery by recommending software engineering tools designed to improve software quality.
 \\
@@
 
-To choose a familiar audience, our approach makes recommendations on Github\footnote{https://github.com}, a popular source code management and version control website that hosts millions of projects and serves millions of users.
-\tool~makes its recommendations on pull requests, or proposed changes to source code submitted by programmers.
-Developers making these changes should be knowledgeable about the changes they propose as well as the code base to which they are contributing.
-Our approach suggests \textsc{Error Prone} when a reported error is fixed by a developer in a pull requests but still exists elsewhere in the code to capitalize on their familiarity with the modifications and encourage the use of static analysis tools to find more bugs.
-
 \subsection{Software Engineering}
 
-\tool~builds on four key concepts to automatically recommend tools to users and improve tool discovery based on our design goals for targeting developer receptivity.
+\tool~incorporates key software engineering industry concepts to improve tool discovery among software developers.
 
@@
 \tool~is implemented as a plugin for Jenkins, ``the leading open source automation server'' for source code deployment and delivery.\footnote{https://jenkins.io/} The system uses Jenkins to clone Github repositories and periodically check for newly-opened pull requests every 15 minutes.
-When a new pull request is found, our system uses Jenkins to automatically run our approach to recommend \textsc{Error Prone}.
+When a new pull request is found, our system uses Jenkins to automatically run our approach to recommend useful software engineering tools.
 
@@
 Our approach uses Maven to automatically handle dependencies and perform the static analysis when the project builds.
-We inject \textsc{Error Prone} as a Maven plugin to repository's \textit{pom.xml} project object model file to add it to the build process.
+We inject the desired software engineering tool as a Maven plugin to repository's \textit{pom.xml} project object model file to add it to the build process.
 \tool~then builds both the original version of the code before the proposed changes were made (base) and the changed version of the repository with the pull request modifications implemented (head) to inspect differences.
@@
 
-\pseudosubsection{Fix Identification}
+\pseudosubsection{Patch Identification}
 
 After analyzing the base and head versions of the code, our approach parses the build output of each version to determine if any reported errors were fixed in the pull request.
-\textsc{Error Prone} identifies faults found in the source code, and we developed an algorithm using that information to determine if changes made to the code in the head version fix the identified bug.
+The software engineering tool identifies faults in the source code, and we take the tool's output and use it in an algorithm we developed to determine if pull request changes fix a reported bug.
 Our technique uses the code differencing tool GumTree~\cite{GumTree} to identify actions (addition, delete, insert, move, and update) performed between pull request versions and parse the code to convert the text into abstract syntax trees.
@@
 
-\pseudosubsection{Fix Localizaton}
-
-When a fix is identified in the pull request, \tool~then aims to find the location of the fix in the head version.
+%\pseudosubsection{Fix Localizaton}
+%
+%When a fix is identified in the pull request, \tool~then aims to find the location of the fix in the head version.
 To find the modified line that fixed a bug, we use GumTree to parse the Java file and convert it into abstract syntax trees.
-We look for the action closest to the offset of the error node calculated from the bug line number reported by \textsc{Error Prone}.
+We look for the action closest to the offset of the error node calculated from the bug line number reported by the software engineering tool, if applicable.
 If the closest action is not a delete, then our approach take the location takes the location of that action.
@@
 
-Code reviews from co-workers are often standard practice in software development.
-Pull requests are the primary method of code contributions and code reviews on Github~\cite{PullRequestReview}.
+Code reviews from co-workers are often standard practice in software development~\cite{CBirdCodeReviewingTrenches}.
+Pull requests are the primary method of development contributions and code reviews on Github~\cite{PullRequestReview}.
 Our approach simulates peer reviews by making recommendations for static analysis tools as a comment to the pull request.
-\tool~automatically runs \textsc{Error Prone} and analyzes the code, providing feedback to developers based on their changes and the output of the tool.
-Github provides functionality for making comments at specific lines of code in a pull request, and \tool~recommends \textsc{Error Prone} as a comment at the fix location line from the previous step.
-Additionally, our system  uses language similar to comments between co-workers in recommendations, such as using ``Good job!'' to compliment developers on their work~\cite{?}.
+\tool~automatically runs software engineering tools and analyzes the code changes, providing feedback to developers based on their changes based on the output from the tool.
+Github provides functionality for making comments at specific lines of code in a pull request, and \tool~recommends the tool as a comment at the fix location line from the previous step.
+Figure 1 presents an example recommendation from our system on a pull request.
+%TODO: Add screenshot
 
-To further increase adoption and use of static analysis tools, we only make a recommendation if \textsc{Error Prone} reports other instances of the same error in the base version of the code.
-In the comment, \tool~automatically adds direct links to at most two separate locations where the defect that was fixed still exists in the code.
-We hope this encourages the developer receiving the recommendation to use \textsc{Error Prone} to fix similar errors and prevent more bugs from being merged into the master code base.
-Figure 1 presents an example recommendation from our system on a pull request review.
-%TODO: Add screenshot
+To increase the likelihood of tool adoption, our system makes recommendations if the tool reports other instances of the fixed error in the latest version of the code.
+In the comment, \tool~automatically adds direct links to at most two separate locations of the same defect.
+Our hope is that this encourages developers to use software engineering toolsin their work to fix the similar errors and prevent additional bugs.
+Additionally, our system uses language similar to a colleage in recommendations.
+For instance, \tool~uses ``Good job!'' to compliment developers for fixing an error in their work~\cite{?}.
 
@@
 Our study evaluates the effectiveness of \tool~by analyzing how often our system recommends software engineering tools and how developers respond to recommendations from our system.
+
+\subsection{Receptiveness}
+
+Our goal is for \tool~to increase awareness of software engineering tools.
+For our initial evaluation in this paper, we target software engineers' desire to produce mistake-free code by automatically recommending \textsc{Error Prone}.
+\textsc{Error Prone} is a static analysis tool that uses a suite of defined bug patterns to detect errors in Java code.
+Static analysis tools like \textsc{Error Prone} are useful for debugging and preventing errors in source code for applications, however they are often underutilized by software engineers~\cite{Johnson2013Why}.
+
+To choose a familiar audience, our approach makes recommendations on Github pull requests, or proposed code changes submitted by users.
+Developers should be knowledgeable and familiar with the changes they propose, as well as the code base to which they are contributing.
+\tool~suggests \textsc{Error Prone} when a reported error is fixed by a developer in a pull request but exists elsewhere in the code.
 

### 2018-02-21 paper/paper.tex
Intro done (don't change until comments)

@@
 
-Software is becoming more and more prevalent throughout our society.
-To keep up with the increasing demands for technology, software engineers are making efforts to emphasize \textbf{---}, or \textit{software quality}.
-Throughout the software development life cycle, more focus is being put on metrics that impact both software producers and consumers such as functionality, reliability, usability, efficiency, maintainability, and portability~\cite{KitchenhamQualityTarget}.
-However, despite increased attention to software quality, defects in code remains a persisting and escalating problem.
+Software is becoming increasingly prevalent in our society.
+To keep up with rising demands for technology, software engineers have made efforts to emphasize \textit{software quality}.
+Throughout the software development life cycle, companies focus on metric that impact both software producers and consumers such as functionality, reliability, usability, efficiency, maintainability, and portability~\cite{KitchenhamQualityTarget}.
+However, despite increased attention to software quality, defective code remains a persisting and escalating problem.
 
-The 2017 Software Fail Watch by Tricentis, a software testing company, discovered that software failures impacted approximaltely half of the world's population (3.7 billion users) and caused \$1.7 trillion in financial losses.\footnote{https://www.tricentis.com/software-fail-watch/} Additionally, the process of finding and fixing bugs in code, or debugging, is becoming increasingly time-consuming and costly.
+The Software Fail Watch by Tricentis discovered that software failures impacted approximaltely half of the world's population (3.7 billion users) and caused \$1.7 trillion in financial losses in 2017.\footnote{https://www.tricentis.com/software-fail-watch/} Additionally, the process of finding and fixing bugs in code, or debugging, is becoming increasingly time-consuming and costly.
 A study by the National Institute of Standards and Technology reported that software engineers spend 70-80\% of their time debugging at work, and one error takes an average of 17.4 hours to debug~\cite{NIST}.
-Studies also show the cost of fixing an error becomes more expensive the longer a bug exists in source code~\cite{SEEconomics, SoftwareAssuranceSDLC}.
+Studies also show the cost of fixing an error becomes more expensive the longer it exists in source code~\cite{SEEconomics, SoftwareAssuranceSDLC}.
 
-To improve code quality and prevent errors, researchers and toolsmiths have created numerous software engineering tools to aid developers in their work.
+To improve code quality and prevent errors, researchers and toolsmiths have created software engineering tools to aid developers in their work.
 These tools automatically perform a wide variety of software development tasks to save time and effort for programmers.
-Research shows that tools for static analysis~\cite{UsingStaticAnalysis}, refactoring~\cite{Murphy-HillFitness}, security, code navigation, and more are beneficial for preventing errors and improving software quality.
-Ultimately, these useful tools can lead to reduced debugging costs and increased developer productivity.
+The Software Engineering Body of Knowledge indicates the importance of development tools used to achieve ``desirable characteristics of software products'', noting they are part of defining software quality~\cite{SWEBOK}.
+Research shows tools for static analysis~\cite{UsingStaticAnalysis}, refactoring~\cite{Murphy-HillFitness}, security, navigation, and more are useful for enhancing code.
+Ultimately, utilizing software enginering tools can lead to reduced debugging costs and increased developer productivity.
 
-Althouth quality is a primary concern for software engineers and users, developers rarely use tools designed to improve code~\cite{Johnson2013Why}.
+Althouth quality is a primary concern for software engineers and users, developers rarely use tools designed to improve quality~\cite{Johnson2013Why}.
 There are many barriers to tool adoption, and one of the primary reasons useful tools are underused or ignored is the discoverability barrier, or when users are unaware of a tool's existence~\cite{Murphy-HillScreencastingDiscovery}.
@@
 
-To answer these questions, we evaluated \tool~by recommending \textsc{Error Prone}\footnote{http://errorprone.info}, an open source Java static analysis tool.
-We examined how often recommendations were made and how developers reacted to receiving suggestions from our system.
+To answer these questions, we evaluated \tool~with \textsc{Error Prone}\footnote{http://errorprone.info}, an open source Java static analysis tool.
+We examined the frequency of recommendations and how developers reacted to receiving suggestions from our system.
 This research makes the following contributions:

### 2018-02-21 paper/paper.tex
Paper notes for future changes
Updated abstract and rewording contributions

@@
 \begin{abstract}
-Software developers have access to numerous tools designed to increase productivity by automatically performing development tasks, but these tools are often ignored or undiscovered by programmers.
-This lack of tool awareness can have dangerous consequences, especially in the software engineering industry.
-Automated recommendation systems were created to improve tool discovery, however these systems are not as effective as user-to-user recommendations.
-To increase awareness of helpful development tools, we introduce \textit{\tool}, a novel system that integrates concepts of peer interactions and software engineering practices to increase tool discovery by effectively making recommendations to developers on open source GitHub projects.
+Toolsmiths have created many tools designed to increase worker productivity by automatically performing tasks, but these tools are often ignored or undiscovered.
+This lack of tool awareness can have significant consequences, especially in the software engineering industry.
+Automated recommendation systems were developed to help improve tool discovery, however these systems are less effective than user-to-user recommendations.
+To increase awareness of helpful development tools, we introduce \textit{\tool}, a new automated recommender system that integrates concepts from peer interactions and software engineering practices for researchers to increase discovery of their tools, and present an evaluation of how our system effectively recommends an open source static analysis tool to Java developers on GitHub projects.
 \end{abstract}
@@
 \begin{itemize}
- \item a novel system for researchers to recommend software engineering tools on GitHub, and
- \item an evaluation on the effectiveness of \tool~with \textsc{Error Prone}
+ \item a novel recommender system for researchers to increase awareness of their software engineering tools, and
+ \item an evaluation of \tool~ recommending \textsc{Error Prone} to GitHub developers
  \end{itemize}
@@
 \section{Related Work}
-
+%TODO: Use related work from FSE committee
 Our implementation of \tool~builds on previous research examining tool discovery, lack of tool adoption among software engineers, and automated recommendation systems.
@@
 %\pseudosubsection{Fix Localizaton}
-%
+%TODO: Delete?
 %When a fix is identified in the pull request, \tool~then aims to find the location of the fix in the head version.

### 2018-02-21 paper/paper.tex
Updating tool description intro

@@
 \section{Tool}
-Our approach to improving tool discovery, \tool, aims to increase awareness and use of programming tools among software developers. This section describes the design and implementation of our system.
+\tool aims to increase discovery and adoption of useful software engineering tools among developers.
+This section describes the design and implementation of our system for making recommendations similar to those from a peer and incorporating software engineering industry practices.
 

### 2018-02-22 com/chbrown13/pull_rec/ErrorProne.java
Using lists instead of sets

@@ -52,18 +52,18 @@ public class ErrorProne extends Tool {
 	}
 	
 	/**
-	 * Parses output from ErrorProne static analysis of code and creates objects.
+	 * Parses output from ErrorProne static analysis of code and creates Errors.
 	 *
 	 * @param msg    ErrorProne output
-	 * @return       List of ErrrorProne
+	 * @return       List of Error objects
 	  */
 	@Override
-	public Set<Error> parseOutput(String msg) {
+	public List<Error> parseOutput(String msg) {
 		String regex = "^[\\w+/]*\\w.java\\:\\d+\\:.*\\:.*";
 		String dir = Utils.getCurrentDir();
 		String[] lines = msg.split("\n");
 		Error temp = null;
-		Set<Error> set = new HashSet<Error>();
+		List<Error> errors = new ArrayList<Error>();
 		for (String line: lines) {
 			if (line.matches("^\\d+\\serror[s]*$") || line.matches("^\\d+\\swarning[s]*$")) {
 				continue;
@@ -73,7 +73,7 @@ public class ErrorProne extends Tool {
 				continue;
 			}
 			else if (line.matches(regex) || line.startsWith(dir)) {
-				if (temp != null && !set.contains(temp)) {	set.add(temp); }
+				if (temp != null && !errors.contains(temp)) {	errors.add(temp); }
 				String[] error = line.split(":");
 				String errorFilePath = error[0];
 				String errorFileName = errorFilePath.substring(errorFilePath.lastIndexOf("/")+1);
@@ -90,8 +90,8 @@ public class ErrorProne extends Tool {
 				temp.addLog(line);
 			}
 		}
-		if (temp != null && !set.contains(temp)) { set.add(temp); }
-		return set;
+		if (temp != null && !errors.contains(temp)) { errors.add(temp); }
+		return errors;
 	}
 
 	/**

### 2018-02-22 com/chbrown13/pull_rec/PullRecommender.java

@@ -19,7 +19,9 @@ public class PullRecommender {
 	private int recs = 0;;
 	private int rem = 0;
 	private int fix = 0;
+	private int noSim = 0;
 	private String removed = "";
+	private String noSimilar = "";
 
 	public PullRecommender(Repo repo) {
 		this.repo = repo;
@@ -63,22 +65,27 @@ public class PullRecommender {
 	 * @param pull	 	Pull request to comment on
 	 * @param error     Error fixed in pull request
 	 */
-	private void makeRecommendation(Tool tool, Pull.Smart pull, Error error, int line, Set<Error> errors) {
+	private void makeRecommendation(Tool tool, Pull.Smart pull, Error error, int line, List<Error> errors) {
 		try {
 			String base = pull.json().getJsonObject("base").getString("sha");
 			String head = pull.json().getJsonObject("head").getString("sha");			
 			String comment = error.generateComment(tool, errors, base);
-			String link = "\n\n" + Utils.SURVEY.replace("{project}", Utils.getProjectName()).replace("{pull}", Integer.toString(pull.number()));
-			comment += link;
-			String args = String.join(" ", Utils.getProjectOwner(), Utils.getProjectName(), 
-				Integer.toString(pull.number()), "\""+comment+"\"", head, error.getLocalFilePath(), 
-				Integer.toString(line)
-			);
+			if (comment != null) {
+				String link = "\n\n" + Utils.SURVEY.replace("{project}", Utils.getProjectName()).replace("{pull}", Integer.toString(pull.number()));
+				comment += link;
+				String args = String.join(" ", Utils.getProjectOwner(), Utils.getProjectName(), 
+					Integer.toString(pull.number()), "\""+comment+"\"", head, error.getLocalFilePath(), 
+					Integer.toString(line)
+				);
 
-			String run = Comment.cmd.replace("{args}", args);
-			sendEmail(String.join("\n", Comment.compile, run), "Recommendation Review", pull.number());
-			recs += 1;
-			prs.add(pull.number());
+				String run = Comment.cmd.replace("{args}", args);
+				sendEmail(String.join("\n", Comment.compile, run), "Recommendation Review", pull.number());
+				recs += 1;
+				prs.add(pull.number());
+			} else {
+				noSim += 1;
+				noSimilar += error.getLog() + "\n";
+			}
 		} catch (IOException e) {
[…]

### 2018-02-22 com/chbrown13/pull_rec/Utils.java

@@ -377,10 +377,10 @@ public class Utils {
 			}
 		}
 		int fix = findFix(file1, file2, getErrorOffset(error, file1));
-		if (fix > 0) {
-			System.out.println(content1);
+		/*if (fix > 0) {
+			System.out.println(conSystem.out.println(content1);
 			System.out.println(content2);
-		}
+		}*/
 		return fix > 0;
 	}
 
@@ -399,7 +399,6 @@ public class Utils {
 			BufferedReader br = new BufferedReader(new InputStreamReader(p.getErrorStream()));
 			String line;
 			while ((line = br.readLine()) != null) {
-				System.out.println(line);
 			    output += line + "\n";
 			}
 		} catch (IOException e) {
@@ -439,7 +438,7 @@ public class Utils {
 							writer.write(tool.getPlugin());
 							writer.write("\n</plugins>");	
 							myTool = true;			
-							System.out.println(tool.getPlugin());				
+							//System.out.println(tool.getPlugin());				
 						} else if (qName.equals("project") && !myTool) {
 							writer.write(String.join("\n", "<build>", "<plugins>", 
 								tool.getPlugin(), "</plugins>", "</build>", "</project>"));
@@ -494,9 +493,9 @@ public class Utils {
 	 * @param author Creator of pull request
 	 * @param tool   Tool to perform analysis and recommend
 	 * @param base   True if checking base repo, false if PR version
-	 * @return       Set errors reported from tool
+	 * @return       List of errors reported from tool
 	 */
-	public static Set<Error> checkout(Pull.Smart pull, Tool tool, boolean base) throws IOException {
+	public static List<Error> checkout(Pull.Smart pull, Tool tool, boolean base) throws IOException {
 		String dirName = projectName;
 		String hash, owner, branch, repo;
 		JsonObject json = pull.json();
@@ -543,6 +542,7 @@ public class Utils {
 		if (log == null) {
 			return null;
 		}
+		System.out.println(log);
 		return tool.parseOutput(log);
 	}
 
@@ -595,7 +595,6 @@ public class Utils {
 	 */
 	public static void cd(String dir) throws FileNotFoundException {
 		String cmd = "cd " + dir;
-		System.out.println(cmd);
 		try {
 			Process p = Runtime.getRuntime().exec(cmd);		
 			if(!dir.equals("..")) {
@@ -603,7 +602,6 @@ public class Utils {
 			} else {
[…]

### 2018-02-24 com/chbrown13/pull_rec/PullRecommender.java
Fixed line numbers for PR comment

@@ -160,7 +160,7 @@ public class PullRecommender {
 						makeRecommendation(tool, pull, e, line, baseErrors);
 					} else {
 						rem += 1;
-						removed += e.getError() + "\n";
+						removed += "-" + e.getError() + "\n";
 					}
 				}	
 			}
@@ -176,7 +176,7 @@ public class PullRecommender {
 	 *
 	 * @return   List of new pull requests
 	 */
-	private ArrayList<Pull.Smart> getPullRequests(int num) {
+	private ArrayList<Pull.Smart> getPullRequests() {
 		System.out.println("Getting new pull requests...");
 		ArrayList<Pull.Smart> requests = new ArrayList<Pull.Smart>();
 		Map<String, String> params = new HashMap<String, String>();
@@ -189,7 +189,7 @@ public class PullRecommender {
 				if (new Date().getTime() - pull.createdAt().getTime() <= TimeUnit.MILLISECONDS.convert(15, TimeUnit.MINUTES)) {
 					analyze(pull);					
 					requests.add(pull);
-					String out = "Recommendations: {rec}\nFixes: {fix}\nRemoved: {rem}\n{err}\nFixed but not exists: {sim}\n{simErr}"
+					String out = "Recommendations: {rec}\nFixes: {fix}\nRemoved: {rem}\n{err}Fixed but not exists: {sim}\n{simErr}"
 						.replace("{rec}", Integer.toString(recs))
 						.replace("{fix}", Integer.toString(fix - recs))
 						.replace("{rem}", Integer.toString(rem))
@@ -218,7 +218,6 @@ public class PullRecommender {
 		RtGithub github = new RtGithub(gitAcct[0], gitAcct[1]);
 		Repo repo = github.repos().get(new Coordinates.Simple(args[0], args[1]));
 		PullRecommender recommender = new PullRecommender(repo);
-		int pull = Integer.parseInt(args[2]);
-		ArrayList<Pull.Smart> requests = recommender.getPullRequests(pull);
+		ArrayList<Pull.Smart> requests = recommender.getPullRequests();
 	}
 }

### 2018-02-24 com/chbrown13/pull_rec/Utils.java

@@ -60,6 +60,8 @@ public class Utils {
 
 	private static int fixLine = -1;
 
+	private static int fixType = -1;
+
 	/**
 	 * Stores current user's Github login
 	 *
@@ -302,11 +304,13 @@ public class Utils {
 					return -1;
 				} 
 			}
+			fixType = 1;
 		} else { //INS or UPD or other
 			temp = closestAction.getNode();
 			while (!searchNode(temp, dst)) {
 				temp = temp.getParent();
 			}
+			fixType = 0;
 		}
 		if (temp == null) {
 			return -1;
@@ -325,23 +329,24 @@ public class Utils {
 		String url = DIFF_URL.replace("{user}", projectOwner)
 			.replace("{repo}", projectName)
 			.replace("{pr}", Integer.toString(pull.number()));
-		int newLine = fixLine;
+		int newLine = fixType;
 		String[] wget = wget(url).split("\n");
 		boolean diff = false;
 		for (String line: wget) {
-			if (line.startsWith("@@") && line.endsWith("@@")) {
+			if (line.contains(err.getFileName())) {
 				diff = true;
+				continue;
+			} 
+			else if (line.startsWith("@@") && line.endsWith("@@")) {
+				//ignore
+				continue;
 			}
 			if (diff) {
 				String l = line.substring(1).trim();
-				if (line.startsWith("+")) {
-					newLine += 1;
-				} else if (line.startsWith("-")) {
-					newLine -= 1;
-				}
 				if (err.getLog().contains(l) && !l.equals("")) {
 					break;
-				}
+				} 					
+				newLine += 1;
 			}
 		}
 		return newLine;

### 2018-02-24 paper/paper.tex
Methodology updates and minor changes

@@
 
-\pseudosubsection{Patch Identification}
+\pseudosubsection{Fix Identification}
 
@@
 \item primariy written in Java,
-\item ranked a top 1000 monthly forked repositoy in the last 10 years,
-\item build using Maven, and
-\item do not already utilize \textsc{Error Prone}.
+\item build using Maven,
+\item do not already use \textsc{Error Prone},
+\item have at least 100 stars,
+\item ranked among the top forked repositories, and
+\item have had 10 pull request opened in the last n days? %TODO: finalize project list
 \end{itemize}
 
-We chose the most forked repositories to sample the most popular GitHub projects in terms of developer activity.
-Additionally, GitHub suggests forking repositories as a best practice for making contributions and pull requests to projects\footnote{https://guides.github.com/activities/forking/}.
 \textsc{Error Prone} only analyzes Java code, so this evaluation was limited to Java projects.
 Maven is a build automation and dependency management system for Java projects.
-\tool~requires Maven to automatically modify \textit{pom.xml} files by adding the \textsc{Error Prone} plug-in and running the static analysis tool.
-Using a GitHub search API with the above constraints, we identified 2003 projects to use for our evaluation.\footnote{\url{https://docs.google.com/spreadsheets/d/1MRmVPiUeDlYMa0UODzMmFbGeYBbahzdeEv1YSgqC1oo/edit?usp=sharing}}
+\tool~requires Maven to automatically modify the \textit{pom.xml} files and run the tool.
+We chose the most forked and starred repositories to retrieve the most popular GitHub projects in terms of developer activity.
+GitHub suggests forking repositories as a best practice for making contributions and pull requests to projects\footnote{https://help.github.com/articles/fork-a-repo/}.
+Stars represent a social aspect of GitHub for users to indicate their favorite projects and repositories they are interested in\footnote{https://help.github.com/articles/about-stars/}.
+Using a GitHub search API, we identified 2003 projects to use for our evaluation.\footnote{\url{https://docs.google.com/spreadsheets/d/1MRmVPiUeDlYMa0UODzMmFbGeYBbahzdeEv1YSgqC1oo/edit?usp=sharing}}
 

### 2018-02-26 eval_scripts/eval.py
Don't need N in eval.py

@@ -1,5 +1,3 @@
-N = 100
-
 def jenkins(user, repo):
     with open("jenkins.xml") as f:
         config = f.read()

### 2018-02-27 paper/paper.tex
Future work and threats updates

@@
 
-An external threat to the validity of our study is that we only observed open source projects hosted on Github in our evaluation.
-Our results may not generalize to closed source software projects and their developers.
-To minimize this, we selected popular real-world software applications on Github owned by organizations to avoid the use of personal development projects.
+An external threat to the validity of our study is that we only observed open source projects, and our results may not generalize to closed source software projects and their developers.
+To minimize this, we evaluated \tool~on popular GitHub software applications with a wide variety of goals.
 Additionally, our recommendation system has limited generalizablility due to the fact we currently only assess recommendations for the Error Prone static analysis tool on Java projects that build with Maven.
-Future work will look to extend \tool~to include different types of tools, programming languages, and build systems.
 
@@
 
-More programming languages (Python, C, C++ etc.)...\\
+To improve discovery of software engineering tools, we aim to increase the practicality and convenience of \tool~for researchers to implement our system with their projects.
+\tool~currently only works for development tools for Java code.
+This disregards useful programming tools that focus on other languages such as...
 
-More types of tools to recommend (static analysis, security, debugging, etc.)... \\
-
-More build systems (ant, gradle, TravisCI, bazel)...\\
+Additionally, our system requires projects that build with Maven. This restriction ignores helpful software engineering tools that implement different build systems, for example,...
 

### 2018-02-27 paper/paper.tex
Updates on Project selection in methodology

@@
 \item do not already use \textsc{Error Prone},
-\item have at least 100 stars,
-\item ranked among the top forked repositories, and
-\item have had 10 pull request opened in the last n days? %TODO: finalize project list
+\item have at least 100 stars, and
+\item ranked among the top forked repositories
 \end{itemize}
 
-\textsc{Error Prone} only analyzes Java code, so this evaluation was limited to Java projects.
-Maven is a build automation and dependency management system for Java projects.
-\tool~requires Maven to automatically modify the \textit{pom.xml} files and run the tool.
-We chose the most forked and starred repositories to retrieve the most popular GitHub projects in terms of developer activity.
+Our evaluation was limited to Java projects since \textsc{Error Prone} only analyzes Java code.
+\tool~requires Maven, a build automation and dependency management system for Java projects, to run tools by automatically modifying the Project Object Model (\textit{pom.xml}) configuration file and building projects.
+We chose the most forked and starred repositories to study the most popular projects on GitHub.
+We target projects that don't use \textsc{Error Prone} to increase awareness for developers who are not knowledgeable about the tool.
+Stars are a social aspect of GitHub where users can indicate favorite projects and repositories of interest\footnote{https://help.github.com/articles/about-stars/}.
 GitHub suggests forking repositories as a best practice for making contributions and pull requests to projects\footnote{https://help.github.com/articles/fork-a-repo/}.
-Stars represent a social aspect of GitHub for users to indicate their favorite projects and repositories they are interested in\footnote{https://help.github.com/articles/about-stars/}.
-Using a GitHub search API, we identified 2003 projects to use for our evaluation.\footnote{\url{https://docs.google.com/spreadsheets/d/1MRmVPiUeDlYMa0UODzMmFbGeYBbahzdeEv1YSgqC1oo/edit?usp=sharing}}
+
+After compiling a list of repositories that met the above criteria, we selected the top 250 projects based on the creation date of their last 10 pull requests.
+We chose projects with more recent pull requests to provide more opportunities for \tool~to make recommendations.
+The evaluation repositories include a wide range of software applications with diversified functions and created by many different companies and developers.
+A list of projects used for this study is publicly available online.\footnote{\url{https://gist.github.com/tool-recommender-bot/1769ccd148508beabcd273a731723860}}
+%TODO: Maybe examples of projects?
 

### 2018-02-27 paper/paper.tex
ACM paper formatting

@@
-\documentclass[conference]{IEEEtran}
+\documentclass[sigconf,review,anonymous]{acmart}
+\acmConference[ESEC/FSE 2018]{The 26th ACM Joint European Software Engineering Conference and Symposium on the Foundations of Software Engineering}{4–9 November, 2018}{Lake Buena Vista, Florida, United States}
 \usepackage{pdftexcmds}
-\usepackage[pdftex]{graphicx}
-\usepackage{multirow}
-\usepackage{pgfplots}
+%\usepackage[pdftex]{graphicx}
+%\usepackage{multirow}
+%\usepackage{pgfplots}
 \usepackage{tikz}
@@
 \usepackage{threeparttable}
-\usepackage[bookmarks=false]{hyperref}
+%\usepackage[bookmarks=false]{hyperref}
 \usepackage{url}
@@
 % Copyright
-%\setcopyright{acmlicensed}
+\setcopyright{acmlicensed}
 
@@
 
-\author{\IEEEauthorblockN{Chris Brown and Emerson Murphy-Hill}
-\IEEEauthorblockA{Department of Computer Science\\
-North Carolina State University\\
-Raleigh, NC\\
-Email: dcbrow10@ncsu.edu, emerson@csc.ncsu.edu}
+\author{Chris Brown and Emerson Murphy-Hill}
+\affiliation{%
+	\institution{North Carolina State University}
+	\city{Raleigh}
+	\state{NC}
 }
+\email{dcbrow10@ncsu.edu, emerson@csc.ncsu.edu}
 
-\maketitle
 \begin{abstract}
@@
 \end{abstract}
+\keywords{Software Engineering; Tool Recommendations; Tool Discovery; Open Source}
 
-\begin{IEEEkeywords}
-Software Engineering; Tool Recommendation; Tool Discovery; Open Source
-\end{IEEEkeywords}
+\maketitle
 

### 2018-02-27 paper/paper.tex
Anonymize and fix headings

@@
 \newcommand{\tool}{\textsl{tool-recommender-bot}}
-\newcommand{\pseudosection}[1]{\vspace{2mm} \noindent {\bf #1}}
-\newcommand{\pseudosubsection}[1]{\vspace{2mm} \noindent{\it #1}}
 
@@
 \section{Tool}
-\tool aims to increase discovery and adoption of useful software engineering tools among developers.
+\tool~aims to increase discovery and adoption of useful software engineering tools among developers.
 This section describes the design and implementation of our system for making recommendations similar to those from a peer and incorporating software engineering industry practices.
@@
 
-To better understand what makes peer interactions an effective mode of tool discovery, our prior work observed how colleagues recommend tools to each other while working on tasks.
-Our results found that \emph{receptiveness} is a significant factor in determining the effectiveness of a tool recommendation, while other characteristics, such as politeness and persuasiveness, do not significantly impact the outcome~\cite{vlhcc17}.
+To better understand what makes peer interactions an effective mode of tool discovery, prior work by Brown and colleagues observed how software users recommend tools to each other while completing tasks.
+They found that \emph{receptiveness} is a significant factor in determining the effectiveness of a tool recommendation while other characteristics, such as politeness and persuasiveness, do not significantly impact recommendation outcome~\cite{vlhcc17}.
 We designed \tool~to integrate user receptivity into our approach for making tool recommendations to increase awareness of programming tools.
 
-\pseudosubsection{Receptiveness}
-
-Previous work emphasizes the importance of receptivity.
+Previous work emphasizes the importance of receptiveness.
 Fogg outlined best practicies for creating persuasive technology to change user behavior, and argued designers must choose a receptive audience~\cite{FoggPersuasive}.
-Our prior work defined receptiveness using two criteria introduced by Fogg: 1) demonstrating a desire and 2) familiarity with the target behavior and technology.
-Below we explain how \tool~was designed to recommend programming tools to software developers based on their desire and familiarity.
-\\
+We define receptiveness using two criteria outlined by Fogg: 1) demonstrating desire and 2) familiarity with target behavior.
+Below we explain how we designed \tool~to recommend programming tools to software developers based on their desire and familiarity.
 
@@
 We aim to increase tool discovery by recommending software engineering tools designed to improve software quality.
-\\
 
@@
 
-\pseudosubsection{Continuous Integration}
+\subsubsection{Continuous Integration}
 
@@
 
-\pseudosubsection{Fix Identification}
+\subsubsection{Fix Identification}
 
@@
 
-\pseudosubsection{Code Review}
+\subsubsection{Code Review}
 
@@
 
-\pseudosubsection{RQ1}
+\subsubsection{RQ1}
 
@@
 
-\pseudosubsection{RQ2}
+\subsubsection{RQ2}
 

### 2018-04-02 com/chbrown13/tool_rec/Recommender.java
Add functionality to use Git API keys for authorization

@@ -352,7 +352,12 @@ public class Recommender {
 
 	public static void main(String[] args) {
 		String[] gitAcct = Utils.getCredentials(".github.creds");
-		RtGithub github = new RtGithub(gitAcct[0], gitAcct[1]);
+		RtGithub github = null;
+		if (gitAcct[1] != null) {
+			github = new RtGithub(gitAcct[0], gitAcct[1]);
+		} else {
+			github = new RtGithub(gitAcct[0]);
+		}
 		Repo repo = github.repos().get(new Coordinates.Simple(args[0], args[1]));
 		Recommender toolBot = new Recommender(repo);
 		toolBot.getCommits();

### 2018-04-02 com/chbrown13/tool_rec/Recommender.java
Add logging to emails

@@ -26,6 +26,7 @@ public class Recommender {
 	private String removed = "";
 	private String introduced = "";
 	private String noSimilar = "";
+	private static String log = "";
 	private int baseErrorCount = 0;
 	private int newErrorCount = 0;
 	private int baseErrorCountFiles = 0;
@@ -84,7 +85,8 @@ public class Recommender {
 			email.setMsg(String.join("\n", viewChanges, text));
 			email.addTo("dcbrow10@ncsu.edu");
 			email.send();		
-			System.out.println("Email sent for review: " + subject);	
+			System.out.println("Email sent for review: " + subject);
+			log += "Email sent for review: " + subject + "\n";	
 		} catch (Exception e) {
 			e.printStackTrace();
 		}
@@ -134,22 +136,26 @@ public class Recommender {
 			List<Error> fixed = new ArrayList<Error>();	
 			List<Error> added = new ArrayList<Error>();
 			System.out.println("base");
+			log += "\nbase";
 			for (Error e: baseErrors) {
 				baseErrorCount += 1;
 				if (files.contains(e.getLocalFilePath())) {
 					baseErrorCountFiles += 1;
 					System.out.println(e.getLog());
+					log += e.getLog();
 					if (!changeErrors.contains(e) || Collections.frequency(baseErrors, e) > Collections.frequency(changeErrors, e)) {
 						fixed.add(e);
 					}
 				}
 			}
 			System.out.println("change");
+			log += "\n\nchange";
 			for (Error e: changeErrors) {
 				newErrorCount += 1;
 				if (files.contains(e.getLocalFilePath())) {
 					newErrorCountFiles += 1;
 					System.out.println(e.getLog());
+					log += e.getLog();
 					if (!baseErrors.contains(e) || Collections.frequency(baseErrors, e) < Collections.frequency(changeErrors, e)) {
 						added.add(e);
 						intro += 1;
@@ -161,11 +167,13 @@ public class Recommender {
 			introduced += Integer.toString(baseErrorCountFiles) + "------" + Integer.toString(newErrorCountFiles) + " (files)"; 
 			for (Error e: fixed) {
 				System.out.println(e.getFilePath());
+				log += e.getFilePath() + "\n";
 				if (Utils.isFix(e)) {
 					fix = true;
 					int line = Utils.getFix(id, e);			
 					System.out.println("Fixed "+ e.getKey() + " reported at line " + 
[…]

### 2018-04-02 com/chbrown13/tool_rec/Recommender.java
Add log to recommend emails too

@@ -118,7 +118,7 @@ public class Recommender {
 				id, "\""+comment+"\"", error.getLocalFilePath(), Integer.toString(line));
 			}
 			String run = Comment.cmd.replace("{args}", args);
-			sendEmail(String.join("\n", Comment.compile, run), "Recommendation Review", id);
+			sendEmail(String.join("\n", Comment.compile, run, "\n" + log), "Recommendation Review", id);
 			recs += 1;
 			fixes.add(id);
 		} else {

### 2018-04-02 paper/paper.tex
Abstract updates to text

@@
 \begin{abstract}
-Toolsmiths have created many tools designed to increase worker productivity by automatically performing tasks, but these tools are often ignored or undiscovered.
-This lack of tool awareness can have significant consequences, especially in the software engineering industry.
-Automated recommendation systems were developed to help improve tool discovery, however these systems are less effective than user-to-user recommendations.
-To increase awareness of helpful development tools, we introduce \textit{\tool}, a new automated recommender system that integrates concepts from peer interactions and software engineering practices for researchers to increase discovery of their tools, and present an evaluation of how our system effectively recommends an open source static analysis tool to Java developers on GitHub projects.
+To increase software user productivity, toolsmiths create tools and features to automatically complete software tasks.
+However, these useful tools are often undiscovered or ignored by users, which can be problematic for industries that rely on worker efficiency and correctness, such as software engineering.
+This paper introduces \tool, a novel automated recommendation system developed for researchers to make recommendations and increase awareness of their products.
+To help improve tool adoption among software engineers, \tool~integrates concepts from peer interactions and software engineering industry practices to suggest tools to developers, and our results suggest that this approach is effective in making tool recommendations to software developers on GitHub repositories.
 \end{abstract}
-\keywords{Software Engineering; Tool Recommendations; Tool Discovery; Open Source}
+\keywords{Software Engineering; Tool Recommendations; Tool Discovery;}
 
@@
 
-Software is becoming increasingly prevalent in our society.
-To keep up with rising demands for technology, software engineers have made efforts to emphasize \textit{software quality}.
-Throughout the software development life cycle, companies focus on metric that impact both software producers and consumers such as functionality, reliability, usability, efficiency, maintainability, and portability~\cite{KitchenhamQualityTarget}.
-However, despite increased attention to software quality, defective code remains a persisting and escalating problem.
+Software is increasingly prevalent in our society.
+To keep up with rising demands for new technology, software engineers are making efforts to emphasize \textit{software quality}.
+Throughout the software development life cycle, companies focus on metrics that impact both software producers and consumers such as functionality, reliability, usability, efficiency, maintainability, and portability~\cite{KitchenhamQualityTarget}.
+However, despite increased attention to improving software quality, buggy code remains a persisting and escalating problem.
 
@@
 \section{Related Work}
-%TODO: Use related work from FSE committee
+%TODO: Use related work from whatever conference committee
 Our implementation of \tool~builds on previous research examining tool discovery, lack of tool adoption among software engineers, and automated recommendation systems.

### 2018-04-03 paper/paper.tex
Reading group abstract and intro changes

@@
 To increase software user productivity, toolsmiths create tools and features to automatically complete software tasks.
-However, these useful tools are often undiscovered or ignored by users, which can be problematic for industries that rely on worker efficiency and correctness, such as software engineering.
+However, these useful tools are often undiscovered or ignored by potential users, which can be problematic for industries, such as software engineering, that rely on worker efficiency and correctness.
 This paper introduces \tool, a novel automated recommendation system developed for researchers to make recommendations and increase awareness of their products.
@@
 
-Software is increasingly prevalent in our society.
+Software is becoming increasingly prevalent in our society.
 To keep up with rising demands for new technology, software engineers are making efforts to emphasize \textit{software quality}.
@@
 
-The Software Fail Watch by Tricentis discovered that software failures impacted approximaltely half of the world's population (3.7 billion users) and caused \$1.7 trillion in financial losses in 2017.\footnote{https://www.tricentis.com/software-fail-watch/} Additionally, the process of finding and fixing bugs in code, or debugging, is becoming increasingly time-consuming and costly.
+The 2017 Software Fail Watch by Tricentis discovered that software failures affected approximaltely half of the world's population impacting 3.7 billion users, and caused \$1.7 trillion in financial losses.\footnote{https://www.tricentis.com/software-fail-watch/} Additionally, the process of finding and fixing bugs in code, or debugging, continues to become increasingly time-consuming and costly.
 A study by the National Institute of Standards and Technology reported that software engineers spend 70-80\% of their time debugging at work, and one error takes an average of 17.4 hours to debug~\cite{NIST}.
@@
 To improve code quality and prevent errors, researchers and toolsmiths have created software engineering tools to aid developers in their work.
-These tools automatically perform a wide variety of software development tasks to save time and effort for programmers.
-The Software Engineering Body of Knowledge indicates the importance of development tools used to achieve ``desirable characteristics of software products'', noting they are part of defining software quality~\cite{SWEBOK}.
-Research shows tools for static analysis~\cite{UsingStaticAnalysis}, refactoring~\cite{Murphy-HillFitness}, security, navigation, and more are useful for enhancing code.
-Ultimately, utilizing software enginering tools can lead to reduced debugging costs and increased developer productivity.
+Prior work shows that tools for static analysis~\cite{UsingStaticAnalysis}, refactoring~\cite{Murphy-HillFitness}, security, and more are beneficial for improving code.
+These tools automatically perform a wide variety of software development tasks to save time and effort for developers.
+Additionally, the Software Engineering Body of Knowledge indicates the importance of development tools, noting they can be used to achieve ``desirable characteristics of software products''~\cite{SWEBOK}.
+Utilizing software enginering tools can reduce software errors and debugging costs while increasing developer productivity.
 
-Althouth quality is a primary concern for software engineers and users, developers rarely use tools designed to improve quality~\cite{Johnson2013Why}.
-There are many barriers to tool adoption, and one of the primary reasons useful tools are underused or ignored is the discoverability barrier, or when users are unaware of a tool's existence~\cite{Murphy-HillScreencastingDiscovery}.
-This lack of awareness for software engineering tools can lead to poor code quality, harmed users, and significant amounts of time and money spent fixing errors.
+Althouth quality is a primary concern for developers and users and many software engineering tools exist to help improve code and prevent bugs, developers rarely use these tools~\cite{Johnson2013Why}.
+One of the primary barriers to tool adoption is the discoverability barrier, where users are unaware of a tool's existence~\cite{Murphy-HillScreencastingDiscovery}.
+This lack of awareness for software engineering tools can lead to poor code quality, inconvenienced users, and significant amounts of time and money spent fixing errors.
 While many automated approaches have been developed to increase knowledge of useful software tools and features, Murphy-Hill and colleagues found that learning about tools from colleagues during normal work activities, or \textit{peer interaction}, is the most effective mode of tool discovery~\cite{MurphyHill2011PeerInteraction}.
@@
 To help solve the tool discovery problem among software engineers, we developed \tool.
-Our system automatically recommends development tools by integrating characteristics of peer interactions and software engineering practices.
+Our system automatically recommends development tools by analyzing developer changes and integrating characteristics of peer interactions and software engineering practices.
 \tool~is designed for toolsmiths to increase awareness of their products by systematically running their tools and making customized recommendations to developers on GitHub\footnote{https://github.com}, the largest code hosting platform in the world~\cite{GousiosGitHub}.
@@
 
-To answer these questions, we evaluated \tool~with \textsc{Error Prone}\footnote{http://errorprone.info}, an open source Java static analysis tool.
+To answer these questions, we evaluated \tool~recommending \textsc{Error Prone}\footnote{http://errorprone.info}, an open source Java static analysis tool.
 We examined the frequency of recommendations and how developers reacted to receiving suggestions from our system.

### 2018-04-03 paper/paper.tex
Pull requests and commits

@@
 \section{Tool}
-\tool~aims to increase discovery and adoption of useful software engineering tools among developers.
-This section describes the design and implementation of our system for making recommendations similar to those from a peer and incorporating software engineering industry practices.
+\tool~aims to increase discovery and adoption of useful software engineering tools among developers. This section describes the design and implementation of our approach.
 
 \subsection{Peer Interactions}
-Previous research shows that recommendations between peers is an effective way to increase tool discovery and adoption~\cite{MurphyHill2011PeerInteraction}.
-Many existing help systems simulate user-to-user recommendations to increase awareness of application tools and features.
+Previous research shows that recommendations between colleagues is the most effective way to increase tool discovery and adoption~\cite{MurphyHill2011PeerInteraction}.
+Murphy-Hill interviewed software engineers and found that user-to-user peer interactions occur less frequently but are much more effective that system-to-user solutions.~\cite{MurphyHill2011PeerInteraction}~\cite{Murphy-Hill2015HowDoUsers}.
 
 To better understand what makes peer interactions an effective mode of tool discovery, prior work by Brown and colleagues observed how software users recommend tools to each other while completing tasks.
-They found that \emph{receptiveness} is a significant factor in determining the effectiveness of a tool recommendation while other characteristics, such as politeness and persuasiveness, do not significantly impact recommendation outcome~\cite{vlhcc17}.
+They found that \emph{receptiveness} is a significant factor in determining the effectiveness of a tool recommendation, while other characteristics such as politeness and persuasiveness do not significantly impact the outcome of a suggestion~\cite{vlhcc17}.
 We designed \tool~to integrate user receptivity into our approach for making tool recommendations to increase awareness of programming tools.
 
-Previous work emphasizes the importance of receptiveness.
+Previous work emphasizes the importance of user receptiveness.
 Fogg outlined best practicies for creating persuasive technology to change user behavior, and argued designers must choose a receptive audience~\cite{FoggPersuasive}.
@@
 However, despite the existence of effective tools for detecting errors, the number of bugs in software is increasing~\cite{HaveThingsChanged}.
-We aim to increase tool discovery by recommending software engineering tools designed to improve software quality.
+\tool~aims to increase tool discovery by recommending software engineering tools designed to promote developers' desires for improving software quality.
+
+Our goal is for \tool~to increase awareness of software engineering tools.
+For our initial evaluation in this paper, we target software engineers' desire to produce mistake-free code by automatically recommending \textsc{Error Prone}.
+\textsc{Error Prone} is a static analysis tool that uses a suite of defined bug patterns to detect errors in Java code.
+Static analysis tools like \textsc{Error Prone} are useful for debugging and preventing errors in source code for applications, however they are often underutilized by software engineers~\cite{Johnson2013Why}.
 
@@
 Choosing an audience familiar with the target behavior is also vital to increasing adoption.
-To increase use of helpful programming tools, such as static analysis tools, our system focuses on making recommendations to software engineers within the context of the projects they develop.
-Familiarity with source code is important for creating software applications.
+To increase use of helpful programming tools, our system focuses on making recommendations to software engineers within the context of the projects they develop.
 Scalabrino and colleagues claim code understandability is one of the most important factors for software development, maintenance, debugging, and testing~\cite{Scalabrino2017Understandability}.
+\tool~uses familiarity with source code to recommend tools to software engineers in code they modify.
+
+To choose a familiar audience, our approach makes recommendations on proposed Github code changes submitted by users.
+Developers should be knowledgeable and familiar with the changes they propose, as well as the code base to which they are contributing.
+\tool~suggests \textsc{Error Prone} when a reported error is fixed by a developer in a pull request or commit, and the same bug exists elsewhere in the code.
 
@@
 
-Our system utilizes continuous integration to recommend useful tools before pull request changes are integrated into the main repository, or merged.
-\tool~is implemented as a plugin for Jenkins, ``the leading open source automation server'' for source code deployment and delivery.\footnote{https://jenkins.io/} The system uses Jenkins to clone Github repositories and periodically check for newly-opened pull requests every 15 minutes.
-When a new pull request is found, our system uses Jenkins to automatically run our approach to recommend useful software engineering tools.
+Our system utilizes continuous integration to recommend useful tools beforecode changes are integrated into the main repository, or merged.
+\tool~is implemented as a plugin for Jenkins, ``the leading open source automation server'' for source code deployment and delivery.\footnote{https://jenkins.io/} The system uses Jenkins to clone Github repositories and periodically check for newly-opened pull requests and commits every 15 minutes.
+When a new code change is found, our system uses Jenkins to automatically run our approach to recommend useful software engineering tools.
 
@@
 We inject the desired software engineering tool as a Maven plugin to repository's \textit{pom.xml} project object model file to add it to the build process.
-\tool~then builds both the original version of the code before the proposed changes were made (base) and the changed version of the repository with the pull request modifications implemented (head) to inspect differences.
+\tool~then builds both the original version of the code before the proposed changes were made (base) and the changed version of the repository with the modifications implemented (head) to inspect differences.
 Using Maven allows \tool~to run on a large number of Java projects that use the popular build tool and also makes our approach extendable to recommend other tools implemented as Maven plugins in future work.
@@
 
-After analyzing the base and head versions of the code, our approach parses the build output of each version to determine if any reported errors were fixed in the pull request.
-The software engineering tool identifies faults in the source code, and we take the tool's output and use it in an algorithm we developed to determine if pull request changes fix a reported bug.
-Our technique uses the code differencing tool GumTree~\cite{GumTree} to identify actions (addition, delete, insert, move, and update) performed between pull request versions and parse the code to convert the text into abstract syntax trees.
+After analyzing the base and head versions of the code, our approach parses the build output of each version to determine if any reported errors were fixed in the code modifications.
+The software engineering tool identifies faults in the source code, and we take the tool's output and use it in an algorithm we developed to determine if GitHub user code changes fix a reported bug.
+Our technique uses the code differencing tool GumTree~\cite{GumTree} to identify actions (addition, delete, insert, move, and update) performed between altered code versions and parse the source code to convert the text into abstract syntax trees.
 
@@
 %TODO: Delete?
-%When a fix is identified in the pull request, \tool~then aims to find the location of the fix in the head version.
+%When a fix is identified in the changed version of code, \tool~then aims to find the location of the fix in the head version.
 To find the modified line that fixed a bug, we use GumTree to parse the Java file and convert it into abstract syntax trees.
@@
 Otherwise, if the line was removed our algorithm searches for the closest sibling node or if none exists then the location of the parent.
-Additionally, the line of the fix had to be converted to the equivalent position in the pull request diff file displaying the changes between file versions, or number of lines below the "@@" header\footnote{https://developer.github.com/v3/pulls/comments/\#create-a-comment}, before moving on to the next phase.
+Additionally, the line of the fix had to be converted to the equivalent position in the pull request or commit diff file displaying the changes between file versions, or number of lines below the "@@" header\footnote{https://developer.github.com/v3/pulls/comments/\#create-a-comment}, before moving on to the next phase.
 
@@
 Code reviews from co-workers are often standard practice in software development~\cite{CBirdCodeReviewingTrenches}.
-Pull requests are the primary method of development contributions and code reviews on Github~\cite{PullRequestReview}.
-Our approach simulates peer reviews by making recommendations for static analysis tools as a comment to the pull request.
+Pull requests and commits are the primary methods of development contributions and code updates on GitHub~\cite{PullRequestReview}.
+Our approach simulates peer reviews by making recommendations for static analysis tools as a comment to the pull request or commit.
 \tool~automatically runs software engineering tools and analyzes the code changes, providing feedback to developers based on their changes based on the output from the tool.
-Github provides functionality for making comments at specific lines of code in a pull request, and \tool~recommends the tool as a comment at the fix location line from the previous step.
+Github allows users to make comments on specific lines of code changed in pull requests and commits.
+\tool~leverages this functionality by recommending the tool as a comment at the fix location line from the previous step.
 Figure 1 presents an example recommendation from our system on a pull request.
@@
 Our study evaluates the effectiveness of \tool~by analyzing how often our system recommends software engineering tools and how developers respond to recommendations from our system.
-
-\subsection{Receptiveness}
-
-Our goal is for \tool~to increase awareness of software engineering tools.
-For our initial evaluation in this paper, we target software engineers' desire to produce mistake-free code by automatically recommending \textsc{Error Prone}.
-\textsc{Error Prone} is a static analysis tool that uses a suite of defined bug patterns to detect errors in Java code.
-Static analysis tools like \textsc{Error Prone} are useful for debugging and preventing errors in source code for applications, however they are often underutilized by software engineers~\cite{Johnson2013Why}.
-
-To choose a familiar audience, our approach makes recommendations on Github pull requests, or proposed code changes submitted by users.
-Developers should be knowledgeable and familiar with the changes they propose, as well as the code base to which they are contributing.
-\tool~suggests \textsc{Error Prone} when a reported error is fixed by a developer in a pull request but exists elsewhere in the code.
 
@@
 Stars are a social aspect of GitHub where users can indicate favorite projects and repositories of interest\footnote{https://help.github.com/articles/about-stars/}.
-GitHub suggests forking repositories as a best practice for making contributions and pull requests to projects\footnote{https://help.github.com/articles/fork-a-repo/}.
 
-After compiling a list of repositories that met the above criteria, we selected the top 250 projects based on the creation date of their last 10 pull requests.
-We chose projects with more recent pull requests to provide more opportunities for \tool~to make recommendations.
-The evaluation repositories include a wide range of software applications with diversified functions and created by many different companies and developers.
+After using a GitHub search API to find projects that met the above criteria, we compiled a list of 789 code repositories.
+The evaluation projects include a wide range of software applications with diversified functions and created by many different companies and developers.
 A list of projects used for this study is publicly available online.\footnote{\url{https://gist.github.com/tool-recommender-bot/1769ccd148508beabcd273a731723860}}
@@
 
-To answer our first research question, we observed how often our approach makes recommendations on newly opened pull requests.
+To answer our first research question, we observed how often our approach makes recommendations on commits and pull requests.
 In addition to the frequency of recommendations, we also tracked instances where \textsc{Error Prone} defects were removed but not reported as fixed according to our fix identification algorithm in Section III.B.2, the number of occurrences where errors were fixed but no other instances of that bug were found in the code, and the false positive rate.
@@
 To prevent unnecessary recommendations from our system, we manually reviewed all instances where \tool~reported a recommendation should be made.
-After inspecting each reported pull request, we determined whether it was an appropriate case for our system to make a recommendation to developers.
-If so, we proceeded to post the comment recommending \textsc{Error Prone} on the pull request.
+After inspecting each repository modification, \tool~determined whether it was an appropriate case to make a recommendation to the developer.
+If so, we proceeded to post the comment recommending \textsc{Error Prone} on the code change.
 Otherwise, we noted the instance of a false positive in our approach and did not make a recommendation.
@@
 To gather data on the usefulness of our system, we sent a follow-up survey to developers.
-Survey participants were users who received a recommendation from \tool~on their pull request.
+Survey participants were users who received a recommendation from \tool~on their pull request or commit.
 We asked developers about their awareness of \textsc{Error Prone} and how likely they are to use the tool in the future.
@@
 Effective tool recommendation systems should have ample opportunities to regularly make recommendations to users.
-To determine how often \tool~automatically recommends \textsc{Error Prone}, we observed the number of pull request comments made by our tool.
+To determine how often \tool~automatically recommends \textsc{Error Prone}, we observed the number of recommendation comments made by our tool.
 Our evaluation lasted for [some period of time], and we calculated the amount of true positive recommendations during that time span to measure the recommendation rate for each GitHub repository used in our study.

### 2018-04-03 paper/paper.tex
Reading group updates

@@
 
-To determine if an error was fixed, we take several things into consideration: First, our approach ignores instances where only delete actions were detected between the base and head versions of a file.
-This avoids making recommendations in situations where bugs were removed but not necessarily fixed in refactoring tasks, such as deleting and moving code, renaming classes, etc.
-Second, we ignore occurrences of deprecated classes because, similarly, the error reported was not fixed but removed.
-Third, we do not consider error fixes that were made by changes to a different file because we want to make recommendations where the developer is familiar with the changes that occurred.
-These help us minimize the number of false positives and errant recommendations in our approach.
+To determine if an error was fixed, we take several things into consideration: First, our approach ignores errors that are reported as fixed but were not located in files modified by the developer.
+This ensures that the GitHub user will be familiar with the code change and error fix.
+Second, we ignore instances where only delete actions were detected between the base and head versions of a file.
+This avoids making recommendations in situations where bugs are removed but not fixed.
+For example, a refactoring task such as renaming a class is presented in the GitHub diff as removing code from the original file.
+This can eliminate bugs reported by Error Prone between code versions, but may also just move the error to another location in the source code.
+Similarly, we also ignore deprecated classes because the error reported was not fixed.
+These conditions help us minimize the number of false positives and prevent errant recommendations in our approach.
 
@@
 \item do not already use \textsc{Error Prone},
-\item have at least 100 stars, and
-\item ranked among the top forked repositories
+\item ranked among the top starred repositories
 \end{itemize}
@@
 \tool~requires Maven, a build automation and dependency management system for Java projects, to run tools by automatically modifying the Project Object Model (\textit{pom.xml}) configuration file and building projects.
-We chose the most forked and starred repositories to study the most popular projects on GitHub.
-We target projects that don't use \textsc{Error Prone} to increase awareness for developers who are not knowledgeable about the tool.
-Stars are a social aspect of GitHub where users can indicate favorite projects and repositories of interest\footnote{https://help.github.com/articles/about-stars/}.
+Our approach targets projects that don't use \textsc{Error Prone} to increase awareness for developers who are not already knowledgeable about the tool.
+We chose the most starred repositories to study the most popular projects on GitHub.Stars are a social aspect of GitHub where users can indicate favorite projects and repositories of interest\footnote{https://help.github.com/articles/about-stars/}.
 
+To get the most popular repositories, we filtered GitHub projects by separating them based on the amount of stars between numbers in the Fibonnaci sequence.
+This allowed us to get a higher concentration of projects with lower number of stars while less projects will have a large number of stars.
+For filtering of repositories, we sorted the top 100 projects by the most recently updated.
 After using a GitHub search API to find projects that met the above criteria, we compiled a list of 789 code repositories.
-The evaluation projects include a wide range of software applications with diversified functions and created by many different companies and developers.
+The projects used for our evaluation include a wide range of software applications providing a variety of services.
 A list of projects used for this study is publicly available online.\footnote{\url{https://gist.github.com/tool-recommender-bot/1769ccd148508beabcd273a731723860}}
@@
 We designed our evaluation to gather quantitative and qualitative data addressing our research questions.
-To analyze 2000+ repositories simultaneously, we used Ansible\footnote{https://www.ansible.com/} to generate Jenkins jobs with \tool~running on multiple virtual machines.
+To analyze 700+ repositories simultaneously, we used Ansible\footnote{https://www.ansible.com/} to generate Jenkins jobs with \tool~running on multiple virtual machines.
 
@@
 Previous research has shown that survey participants are more motivated to answer truthfullly if they know they are contributing to research~\cite{Krosnick1991Research}.
+
+To futher examine the effectiveness of \tool, we compared our approach to sending email recommendations to developers.
+To study this, we found similar instances of code fixes by GitHub users where our system would recommend a tool and, instead of making the recommendation with \tool~on the pull request or commit, send an email suggesting \textsc{Error Prone} to the developers.
+The emails also contained the recommendation feedback survey for developers, and we compared results to see how software engineers responded to receiving a recommendation by email vs.
+on GitHub from \tool.
 

### 2018-04-03 paper/paper.tex
Reading group 4/3

@@
 Our evaluation was limited to Java projects since \textsc{Error Prone} only analyzes Java code.
-\tool~requires Maven, a build automation and dependency management system for Java projects, to run tools by automatically modifying the Project Object Model (\textit{pom.xml}) configuration file and building projects.
-Our approach targets projects that don't use \textsc{Error Prone} to increase awareness for developers who are not already knowledgeable about the tool.
-We chose the most starred repositories to study the most popular projects on GitHub.Stars are a social aspect of GitHub where users can indicate favorite projects and repositories of interest\footnote{https://help.github.com/articles/about-stars/}.
+To determine if a repository was a Maven project, we automatically checked if a Project Object Model (\textit{pom.xml}) configuration file was located in the home directory.
+We also checked to make sure that the pom.xml did not already contain the \textsc{Error Prone} plugin.
+Our approach targets projects that don't use \textsc{Error Prone} to recommend the tool to developers who are less likely to be knowledgeable about the tool.
+We chose the most starred repositories to study the most popular projects on GitHub.
+Stars are a social aspect of GitHub where users can indicate favorite projects and repositories of interest\footnote{https://help.github.com/articles/about-stars/}.
 
-To get the most popular repositories, we filtered GitHub projects by separating them based on the amount of stars between numbers in the Fibonnaci sequence.
+To get the most popular repositories, we filtered GitHub projects by the amount of stars based on numbers in the Fibonnaci sequence.
 This allowed us to get a higher concentration of projects with lower number of stars while less projects will have a large number of stars.
@@
 After using a GitHub search API to find projects that met the above criteria, we compiled a list of 789 code repositories.
-The projects used for our evaluation include a wide range of software applications providing a variety of services.
+The projects used for our evaluation include a wide range of software applications providing a variety of services from large software companies such as Google and Apache to individual developers.
 A list of projects used for this study is publicly available online.\footnote{\url{https://gist.github.com/tool-recommender-bot/1769ccd148508beabcd273a731723860}}
@@
 Otherwise, we noted the instance of a false positive in our approach and did not make a recommendation.
+In situations where one commit or pull request provided multiple opportunities for a recommendation, the authors would examine the changes and select one of the errors reported as fixed to recommend \textsc{Error Prone} to the developer.
 
@@
 on GitHub from \tool.
+To send a recommendation via email, the developer must have an email address publicly available on the GitHub user profile.
 
@@
 Effective tool recommendation systems should have ample opportunities to regularly make recommendations to users.
-To determine how often \tool~automatically recommends \textsc{Error Prone}, we observed the number of recommendation comments made by our tool.
-Our evaluation lasted for [some period of time], and we calculated the amount of true positive recommendations during that time span to measure the recommendation rate for each GitHub repository used in our study.
+To determine how often \tool~automatically recommends \textsc{Error Prone}, we observed the total number of new pull requests and commits, and compared it to the amount recommendations made by our tool.
+We calculated the rate of true positive recommendations during the span of our study to measure the recommendation rate for each GitHub repository used in our evaluation.
 To calculate the false positive rate, we compared the number of unnecessary instances where our tool proposed a recommendation found by researchers to the total number of instances where a recommendation reported by \tool.
@@
 
-For our second research question, we accumulated responses from developers in our follow-up survey to determine the usefulness of our system.
+For our second research question, we accumulated responses from developers in our follow-up survey presented in recommendations from \tool~and by email to determine the usefulness of our system.
 We utilized a five-point Likert scale for participants to rank how knowledgeable they were about the existence of \textsc{Error Prone} before the recommendation and how likely they are to use \textsc{Error Prone} for future development tasks.
@@
 These responses were used to analyze developers' reactions to our automated recommendation.
-Finally, researchers analyzed and independently coded open-ended responses from participants to further analyze the effectiveness of our system based on developer feedback.
+Finally, researchers analyzed and independently coded open-ended responses from participants to further analyze the effectiveness of our approach based on feedback from software developers.
 
@@
 
-Non-java changes, documentation, errors removed not fixed, error fixed everywhere in code...
+Non-java changes, number of errors removed but not fixed, number of errors fixed without another instance in the code, manual inspection of pull requests and commits...
 
@@
 
-Internal\\
+An internal threat to the validity of this work is our use of code differencing to determine if developers intended to fix a bug in a commit or pull request.
+We cannot definitively determine the intentions of GitHub developers making changes to a repository, however two authors analyzed the code changes and came to an agreement on if the modified patch was a fix before making a recommendation to the developer.
+Additionally, although we used a Likert scale to measure if GitHub users who received a recommendation were likely to use \textsc{Error Prone} in the future, we did not measure if the tool was actually adopted by the developers for future tasks.
 
-An external threat to the validity of our study is that we only observed open source projects, and our results may not generalize to closed source software projects and their developers.
-To minimize this, we evaluated \tool~on popular GitHub software applications with a wide variety of goals.
-Additionally, our recommendation system has limited generalizablility due to the fact we currently only assess recommendations for the Error Prone static analysis tool on Java projects that build with Maven.
+Our evaluation has limited generalizablility due to the fact we only assessed recommendations for the \textsc{Error Prone} static analysis tool.
+This restricted our study to evaluate Java projects and a specific set of errors that can be reported by the tool.
+We selected \textsc{Error Prone} because it is able to report a wide variety of errors based on bug patterns for Java code.
+Another external threat to the validity of this study is the projects selected for our evaluation.
+We only examined open source repositories on GitHub, and these results may not generalize to developers of closed source software or projects on other code hosting sites, such as BitBucket.\footnote{http://bitbucket.org} To minimize this threat, we evaluated \tool~on a large number of popular software applications on GitHub that provide many different services from a wide variety of software companies and developers.
 
@@
 
-To improve discovery of software engineering tools, we aim to increase the practicality and convenience of \tool~for researchers to implement our system with their projects.
-\tool~currently only works for development tools for Java code.
-This disregards useful programming tools that focus on other languages such as...
-
-Additionally, our system requires projects that build with Maven. This restriction ignores helpful software engineering tools that implement different build systems, for example,...
+To improve discovery of software engineering tools, we plan to increase the practicality of \tool~for researchers to implement our system with their projects.
+A next step is to extend our approach to work with multiple static analysis tools, such as Checkstyle\footnote{http://checkstyle.sourceforge.net/} for Java.
+This will allow us to have more opportunities to make recommendations to developers based on the output from different tools.
+Additionally, we plan to update our system to work with software engineering tools that integrate as plugins for different build systems such as Gradle\footnote{https://gradle.org/} and Travis CI\footnote{https://travis-ci.org/}, as opposed to just Maven projects.
+Future work will also extend \tool~to work with different types of tools to increase adoption and usage, for example Find Security Bugs\footnote{https://find-sec-bugs.github.io/} which is useful for finding security vulnerabilities in Java web applications.
+Finally, future work will consist of expanding \tool~to work with software engineering tools for different programming languages, such as the Pylint\footnote{https://www.pylint.org/} static analysis tool for Python, clang\footnote{https://clang.llvm.org/} compiler and static analyzer for C and C++, and more.
 

### 2018-04-03 paper/paper.tex
Reading group 4/3

@@
 Using Maven allows \tool~to run on a large number of Java projects that use the popular build tool and also makes our approach extendable to recommend other tools implemented as Maven plugins in future work.
+This also allows our system to easily be integrated into continuous integration builds for software applications to analyze code and recommend development tools to software engineers.
 
@@
 Similarly, we also ignore deprecated classes because the error reported was not fixed.
-These conditions help us minimize the number of false positives and prevent errant recommendations in our approach.
+These conditions help us minimize the number of false positives and prevent errant recommendations to developers in our approach.
 
@@
 
-We used real-world open source software applications to evaluate \tool. To choose study projects from the millions of GitHub repositories, we selected projects that met the following criteria:
+We used real-world open source software applications to evaluate \tool. To choose projects for this study from the millions of GitHub repositories online, we used the following criteria:
 
@@
 \item do not already use \textsc{Error Prone},
-\item ranked among the top starred repositories
+\item ranked among the most popular and most recently updated repositories
 \end{itemize}
 
-Our evaluation was limited to Java projects since \textsc{Error Prone} only analyzes Java code.
-To determine if a repository was a Maven project, we automatically checked if a Project Object Model (\textit{pom.xml}) configuration file was located in the home directory.
-We also checked to make sure that the pom.xml did not already contain the \textsc{Error Prone} plugin.
-Our approach targets projects that don't use \textsc{Error Prone} to recommend the tool to developers who are less likely to be knowledgeable about the tool.
-We chose the most starred repositories to study the most popular projects on GitHub.
-Stars are a social aspect of GitHub where users can indicate favorite projects and repositories of interest\footnote{https://help.github.com/articles/about-stars/}.
+Our evaluation was limited to Java projects since \textsc{Error Prone} can only analyze Java source code.
+To determine if a repository used Maven as a build system, we automatically checked if a Project Object Model (\textit{pom.xml}) configuration file was located in the home directory.
+We also checked to make sure that the pom.xml did not already contain the \textsc{Error Prone} plugin to avoid projects that already use \textsc{Error Prone}.
+We selected projects that don't use \textsc{Error Prone} to increase awareness of the tool in recommendations.
+Developers are less likely to know about the tool if the projects they contribute to do not implement it in their build.
 
 To get the most popular repositories, we filtered GitHub projects by the amount of stars based on numbers in the Fibonnaci sequence.
-This allowed us to get a higher concentration of projects with lower number of stars while less projects will have a large number of stars.
-For filtering of repositories, we sorted the top 100 projects by the most recently updated.
+We chose the most starred repositories to study the most popular projects on GitHub.
+Stars are a social aspect of GitHub where users can indicate their favorite projects and repositories of interest\footnote{https://help.github.com/articles/about-stars/}.
+Using Fibonacci numbers allowed us to get a higher concentration of projects with a lower amount of stars, while fewer projects will have a very large number of stars.
+To filter of repositories, we grouped projects with 1 or 2 stars, 2 or 3 stars, between 3 and 5 stars, between 5 and 8 stars, etc., and sorted the top 100 projects in each group by when they were most recently updated.
 After using a GitHub search API to find projects that met the above criteria, we compiled a list of 789 code repositories.
@@
 We designed our evaluation to gather quantitative and qualitative data addressing our research questions.
-To analyze 700+ repositories simultaneously, we used Ansible\footnote{https://www.ansible.com/} to generate Jenkins jobs with \tool~running on multiple virtual machines.
+
+\subsubsection{Setup}
+
+To analyze 700+ GitHub repositories simultaneously, we used Ansible\footnote{https://www.ansible.com/} to generate Jenkins jobs running \tool~on multiple virtual machines.
 
@@
 To prevent unnecessary recommendations from our system, we manually reviewed all instances where \tool~reported a recommendation should be made.
-After inspecting each repository modification, \tool~determined whether it was an appropriate case to make a recommendation to the developer.
-If so, we proceeded to post the comment recommending \textsc{Error Prone} on the code change.
-Otherwise, we noted the instance of a false positive in our approach and did not make a recommendation.
-In situations where one commit or pull request provided multiple opportunities for a recommendation, the authors would examine the changes and select one of the errors reported as fixed to recommend \textsc{Error Prone} to the developer.
+After inspecting each repository modification, \tool~determines whether it is an appropriate case to make a recommendation to the developer.
+For this study, we streamlined this process to send an email for the authors to review if a recommendation was proposed by our system.
+After the authors reviewed the code changes, if we deemed it was a true positive case we proceeded to use \tool~to post the comment recommending \textsc{Error Prone} to the developer on the pull request or commit.
+Otherwise, we noted the instance of a false positive in our approach and did not make the recommendation.
+In situations where one repository code change provided multiple opportunities for a recommendation, the authors examined each of the changes and selected one of the errors reported as fixed to recommend to the developer.
 
@@
 We calculated the rate of true positive recommendations during the span of our study to measure the recommendation rate for each GitHub repository used in our evaluation.
-To calculate the false positive rate, we compared the number of unnecessary instances where our tool proposed a recommendation found by researchers to the total number of instances where a recommendation reported by \tool.
+To calculate the false positive rate, we compared the number of unnecessary instances where our tool proposed a recommendation found by the authors to the total number of instances where a recommendation reported by \tool.
 
@@
 Finally, researchers analyzed and independently coded open-ended responses from participants to further analyze the effectiveness of our approach based on feedback from software developers.
+We measured the response rate by observing the total number of recommendations made, the total number of survey responses, and the positive and negative responses from developers who received a recommendation via \tool~and via email.
 

### 2018-04-03 com/chbrown13/tool_rec/Recommender.java
Add tool log to email

@@ -75,6 +75,7 @@ public class Recommender {
 			viewChanges += "files/";
 		}
 		String[] emailAcct = Utils.getCredentials(".email.creds");
+		text += "\n" + log;
 		try {
 			email.setHostName("smtp.googlemail.com");
 			email.setSmtpPort(465);
@@ -118,7 +119,7 @@ public class Recommender {
 				id, "\""+comment+"\"", error.getLocalFilePath(), Integer.toString(line));
 			}
 			String run = Comment.cmd.replace("{args}", args);
-			sendEmail(String.join("\n", Comment.compile, run, "\n" + log), "Recommendation Review", id);
+			sendEmail(String.join("\n", Comment.compile, run), "Recommendation Review", id);
 			recs += 1;
 			fixes.add(id);
 		} else {
@@ -286,7 +287,6 @@ public class Recommender {
 			.replace("{simErr}", noSimilar)
 			.replace("{intro}", Integer.toString(intro))
 			.replace("{new}", introduced);
-		out += "\n" + log;
 		sendEmail(out, "New " + type, id);
 		System.out.println(out);
 		reset();

### 2018-04-04 com/chbrown13/tool_rec/Recommender.java
Better output to view in emails

@@ -143,7 +143,7 @@ public class Recommender {
 				if (files.contains(e.getLocalFilePath())) {
 					baseErrorCountFiles += 1;
 					System.out.println(e.getLog());
-					log += e.getLog();
+					log += "*" + e.getLog();
 					if (!changeErrors.contains(e) || Collections.frequency(baseErrors, e) > Collections.frequency(changeErrors, e)) {
 						fixed.add(e);
 					}
@@ -156,7 +156,7 @@ public class Recommender {
 				if (files.contains(e.getLocalFilePath())) {
 					newErrorCountFiles += 1;
 					System.out.println(e.getLog());
-					log += e.getLog();
+					log += "*" + e.getLog();
 					if (!baseErrors.contains(e) || Collections.frequency(baseErrors, e) < Collections.frequency(changeErrors, e)) {
 						added.add(e);
 						intro += 1;

### 2018-04-04 paper/paper.tex

@@
 \begin{abstract}
-To increase software user productivity, toolsmiths create tools and features to automatically complete software tasks.
-However, these useful tools are often undiscovered or ignored by potential users, which can be problematic for industries, such as software engineering, that rely on worker efficiency and correctness.
-This paper introduces \tool, a novel automated recommendation system developed for researchers to make recommendations and increase awareness of their products.
-To help improve tool adoption among software engineers, \tool~integrates concepts from peer interactions and software engineering industry practices to suggest tools to developers, and our results suggest that this approach is effective in making tool recommendations to software developers on GitHub repositories.
+To increase software engineer productivity, toolsmiths create tools and features to automatically complete software development tasks.
+However, these useful tools are often undiscovered or ignored by developers which is problematic for software applications that rely on programmer efficiency and correctness.
+This paper introduces \tool, an automated recommendation system created for researchers to increase awareness of their products by making recommendations to developers on online collaboration websites.
+To help improve tool adoption among software engineers, \tool~uses a novel approach and original design principles to integrate concepts of user-to-user suggestions and industry practices in tool recommendations to developers, and our results suggest this approach is more effective in making tool recommendations to software developers on GitHub repositories.
 \end{abstract}
-\keywords{Software Engineering; Tool Recommendations; Tool Discovery;}
+\keywords{Tool Recommendations; Tool Discovery;}
 
@@
 
-Software is becoming increasingly prevalent in our society.
-To keep up with rising demands for new technology, software engineers are making efforts to emphasize \textit{software quality}.
-Throughout the software development life cycle, companies focus on metrics that impact both software producers and consumers such as functionality, reliability, usability, efficiency, maintainability, and portability~\cite{KitchenhamQualityTarget}.
-However, despite increased attention to improving software quality, buggy code remains a persisting and escalating problem.
-
-The 2017 Software Fail Watch by Tricentis discovered that software failures affected approximaltely half of the world's population impacting 3.7 billion users, and caused \$1.7 trillion in financial losses.\footnote{https://www.tricentis.com/software-fail-watch/} Additionally, the process of finding and fixing bugs in code, or debugging, continues to become increasingly time-consuming and costly.
-A study by the National Institute of Standards and Technology reported that software engineers spend 70-80\% of their time debugging at work, and one error takes an average of 17.4 hours to debug~\cite{NIST}.
-Studies also show the cost of fixing an error becomes more expensive the longer it exists in source code~\cite{SEEconomics, SoftwareAssuranceSDLC}.
+To keep up with rising demands for technology, software engineers emphasize \textit{software quality}.
+Throughout the software development life cycle, development teams monitor code metrics that impact expectations of software producers and consumers~\cite{KitchenhamQualityTarget}.
+However, despite increased attention to software quality, buggy code remains a problem.
+The Software Fail Watch by Tricentis suggests software failures impacted 3.7 billion users and caused \$1.7 trillion in financial losses in 2017.\footnote{https://www.tricentis.com/software-fail-watch/} Additionally, the process of finding and fixing bugs, or debugging, is a time-consuming and costly activity.
+The National Institute of Standards and Technology reports software engineers spend 70-80\% of work time debugging and the average time to debug one error is 17.4 hours~\cite{NIST}.
+Fixing defects early in the development process is also important since studies show debugging costs increase the longer a bug remains in code~\cite{SEEconomics, SoftwareAssuranceSDLC}.
 
 To improve code quality and prevent errors, researchers and toolsmiths have created software engineering tools to aid developers in their work.
-Prior work shows that tools for static analysis~\cite{UsingStaticAnalysis}, refactoring~\cite{Murphy-HillFitness}, security, and more are beneficial for improving code.
-These tools automatically perform a wide variety of software development tasks to save time and effort for developers.
-Additionally, the Software Engineering Body of Knowledge indicates the importance of development tools, noting they can be used to achieve ``desirable characteristics of software products''~\cite{SWEBOK}.
+Prior work shows that tools for static analysis~\cite{UsingStaticAnalysis}, refactoring~\cite{Murphy-HillFitness}, security, and more are beneficial for improving code and preventing bugs.
+These tools can automatically perform a wide variety of software development tasks to save time and effort for developers.
+Additionally, the Software Engineering Body of Knowledge recommends using development tools because they can be used to achieve ``desirable characteristics of software products''~\cite{SWEBOK}.
 Utilizing software enginering tools can reduce software errors and debugging costs while increasing developer productivity.
 
-Althouth quality is a primary concern for developers and users and many software engineering tools exist to help improve code and prevent bugs, developers rarely use these tools~\cite{Johnson2013Why}.
+Although quality is a concern for developers and users, many helpful software engineering tools go unused by developers.
 One of the primary barriers to tool adoption is the discoverability barrier, where users are unaware of a tool's existence~\cite{Murphy-HillScreencastingDiscovery}.
 This lack of awareness for software engineering tools can lead to poor code quality, inconvenienced users, and significant amounts of time and money spent fixing errors.
-While many automated approaches have been developed to increase knowledge of useful software tools and features, Murphy-Hill and colleagues found that learning about tools from colleagues during normal work activities, or \textit{peer interaction}, is the most effective mode of tool discovery~\cite{MurphyHill2011PeerInteraction}.
+While many automated approaches have been developed to increase knowledge of useful software tools and features, Murphy-Hill and colleagues found that developers prefer learning about tools from colleagues during normal work activities, or \textit{peer interaction}, compared to other modes of tool discovery~\cite{MurphyHill2011PeerInteraction}.
+Similarly, Welty discovered that software users sought help from colleagues more often than search engines and help menus~\cite{Welty2011Help}.
 
@@
 Our system automatically recommends development tools by analyzing developer changes and integrating characteristics of peer interactions and software engineering practices.
-\tool~is designed for toolsmiths to increase awareness of their products by systematically running their tools and making customized recommendations to developers on GitHub\footnote{https://github.com}, the largest code hosting platform in the world~\cite{GousiosGitHub}.
-This paper seeks to answer the following research questions (RQs): \\
+\tool~is designed for toolsmiths to increase awareness of their products by systematically running their tools and making customized recommendations to developers, the largest code hosting platform in the world~\cite{GousiosGitHub}.
+This paper presents the novel approach and design of our system and evaluates the effectiveness of our tool in a real-world scenario.
 
-\noindent
-\textbf{RQ1:} How applicable is \tool~to real-world software applications?  \\ 
-\textbf{RQ2:} How useful are recommendations from \tool~to developers?  \\
+%\noindent
+%TODO: Research questions?
+%\textbf{RQ1:} How applicable is \tool~to real-world software applications?  \\ 
+%\textbf{RQ2:} How useful are recommendations from \tool~to developers?  \\
 
-To answer these questions, we evaluated \tool~recommending \textsc{Error Prone}\footnote{http://errorprone.info}, an open source Java static analysis tool.
-We examined the frequency of recommendations and how developers reacted to receiving suggestions from our system.
+To evaluate \tool, we conducted a study making recommendations for \textsc{Error Prone}\footnote{http://errorprone.info}, an open source static analysis tool, to developers on the GitHub\footnote{https://github.com} code hosting platform.
+We calculated the effectiveness of \tool~by measuring the frequency of recommendations and how developers reacted to receiving suggestions from our system.
 This research makes the following contributions:
@@
 \begin{itemize}
- \item a novel recommender system for researchers to increase awareness of their software engineering tools, and
- \item an evaluation of \tool~ recommending \textsc{Error Prone} to GitHub developers
+ \item a novel approach for recommender systems to increase awareness of software engineering tools, and
+ \item an evaluation of \tool~ recommending \textsc{Error Prone} to developers on GitHub.
  \end{itemize}
@@
 %TODO: Use related work from whatever conference committee
-Our implementation of \tool~builds on previous research examining tool discovery, lack of tool adoption among software engineers, and automated recommendation systems.
-
-Researchers have explored how humans learn about new tools.
-There are various methods to discover tools in software, and research suggests recommendations between peers is the most effective way to increase tool awareness.
-Murphy-Hill found that peer interactions were the most effective mode of tool discovery compared to tool encounters, tutorials, descriptions, social media, and discussion threads~\cite{MurphyHill2011PeerInteraction}~\cite{Murphy-Hill2015HowDoUsers}.
-Similarly, Welty discovered that software users sought help from colleagues more often than search engines and help menus~\cite{Welty2011Help}.
-To improve the effectiveness of recommendations from our system, we integrate qualities of peer interactions into \tool.
+Our implementation of \tool~builds on previous research examining recommendation systems in software engineering, techniques for learning new tools and features, approaches for tool recommendations, and existing systems that recommend software engineering tools.
 
@@
 
-\section{Tool}
-\tool~aims to increase discovery and adoption of useful software engineering tools among developers. This section describes the design and implementation of our approach.
+\section{Approach}
+
+\tool~aims to increase discovery and adoption of useful software engineering tools by implementing three design pillars: \textit{commend}, \textit{apprehend}, and \textit{recommend}.
+
+\subsection{Commend}
+
+\subsection{Apprehend}
+
+\subsection{Recommend}
+
+\section{Design}
+
+Previous research peer interactions influenced our three design pillars for \tool.
 
 \subsection{Peer Interactions}
-Previous research shows that recommendations between colleagues is the most effective way to increase tool discovery and adoption~\cite{MurphyHill2011PeerInteraction}.
-Murphy-Hill interviewed software engineers and found that user-to-user peer interactions occur less frequently but are much more effective that system-to-user solutions.~\cite{MurphyHill2011PeerInteraction}~\cite{Murphy-Hill2015HowDoUsers}.
+Previous research shows that recommendations between colleagues are the most effective way to increase tool discovery and adoption~\cite{MurphyHill2011PeerInteraction}.
+Murphy-Hill interviewed software engineers and found that user-to-user peer interactions occur less frequently in the workplace but are more effective than system-to-user solutions.~\cite{MurphyHill2011PeerInteraction}~\cite{Murphy-Hill2015HowDoUsers}.
 
@@
 
-The primary desire of software users is to have enjoyable and problem-free experiences with software.
-Developers of these applications also have similar desires, to create high-quality and functioning programs for users.
+A key desire of software users is to have enjoyable and problem-free experiences with software.
+Producers of software applications also have a similar desire to create high-quality functioning programs for users.
 A 2002 study revealed that software engineers demonstrate this desire by spending the majority of the software development process and 70-80\% of their time testing and debugging code~\cite{NIST}.
@@
 
+\section{Implementation Walkthrough}
+
+\section{Implementation Description}
+
 \subsection{Software Engineering}
@@
 
-\subsubsection{Fix Identification}
+\subsubsection{Debugging}
 
@@
 
-%\pseudosubsection{Fix Localizaton}
-%TODO: Delete?
-%When a fix is identified in the changed version of code, \tool~then aims to find the location of the fix in the head version.
+When a fix is identified in the changed version of code, \tool~then aims to find the location of the fix in the head version.
 To find the modified line that fixed a bug, we use GumTree to parse the Java file and convert it into abstract syntax trees.
@@
 After using a GitHub search API to find projects that met the above criteria, we compiled a list of 789 code repositories.
+Out of those projects, one repository failed due to broken Unicode text.
+%TODO: find other failed projects w/ errors
 The projects used for our evaluation include a wide range of software applications providing a variety of services from large software companies such as Google and Apache to individual developers.

### 2018-04-04 paper/paper.tex
More updates from reading group feedback

@@
 However, these useful tools are often undiscovered or ignored by developers which is problematic for software applications that rely on programmer efficiency and correctness.
-This paper introduces \tool, an automated recommendation system created for researchers to increase awareness of their products by making recommendations to developers on online collaboration websites.
-To help improve tool adoption among software engineers, \tool~uses a novel approach and original design principles to integrate concepts of user-to-user suggestions and industry practices in tool recommendations to developers, and our results suggest this approach is more effective in making tool recommendations to software developers on GitHub repositories.
+This paper introduces \tool, an automated recommendation system designed for researchers to increase awareness of their products by making recommendations to developers.
+To help improve tool adoption among software engineers, we developed implemented a novel approach and design principles that integrate concepts of user-to-user suggestions and industry practices in \tool, and our results suggest this approach is more effective in making tool recommendations compared to other styles.
 \end{abstract}
@@
 Throughout the software development life cycle, development teams monitor code metrics that impact expectations of software producers and consumers~\cite{KitchenhamQualityTarget}.
-However, despite increased attention to software quality, buggy code remains a problem.
+However, despite increased attention to software quality, buggy code remains a problem and the number of defects in software is increasing~\cite{HaveThingsChanged}.
 The Software Fail Watch by Tricentis suggests software failures impacted 3.7 billion users and caused \$1.7 trillion in financial losses in 2017.\footnote{https://www.tricentis.com/software-fail-watch/} Additionally, the process of finding and fixing bugs, or debugging, is a time-consuming and costly activity.
@@
 Additionally, the Software Engineering Body of Knowledge recommends using development tools because they can be used to achieve ``desirable characteristics of software products''~\cite{SWEBOK}.
-Utilizing software enginering tools can reduce software errors and debugging costs while increasing developer productivity.
+Software enginering tools are useful for reducing software errors and debugging costs while increasing developer productivity.
 
-Although quality is a concern for developers and users, many helpful software engineering tools go unused by developers.
-One of the primary barriers to tool adoption is the discoverability barrier, where users are unaware of a tool's existence~\cite{Murphy-HillScreencastingDiscovery}.
-This lack of awareness for software engineering tools can lead to poor code quality, inconvenienced users, and significant amounts of time and money spent fixing errors.
-While many automated approaches have been developed to increase knowledge of useful software tools and features, Murphy-Hill and colleagues found that developers prefer learning about tools from colleagues during normal work activities, or \textit{peer interaction}, compared to other modes of tool discovery~\cite{MurphyHill2011PeerInteraction}.
-Similarly, Welty discovered that software users sought help from colleagues more often than search engines and help menus~\cite{Welty2011Help}.
+Although software quality is important, development tools created to improve code are often ignored~\cite{Ivanov2017Gaps}.
+Previous work explores barriers preventing software engineers from adopting new tools: Tilley and colleagues studied challenges of adopting research-off-the-shelf tools in industry~\cite{Tilley2003ROTS}; Johnson and colleagues reported reasons why software engineers don't use static analysis tools~\cite{Johnson2013Why}; and Xiao and colleagues examined barriers of using security tools to prevent vulnerabilities and malicious attacks~\cite{Xiao2014Security}.
+One of the main barriers to tool adoption is the discoverability barrier, where users are unaware tools exist~\cite{Murphy-HillScreencastingDiscovery}.
+Lack of software engineering tool usage can lead to poor code quality, inconvenienced users, and significant amounts of time and money spent fixing errors.
+Many existing automated approaches have been implemented to increase awareness of software tools and features, but Murphy-Hill and colleagues found that developers prefer learning about tools from colleagues during normal work activities, or \textit{peer interaction}~\cite{MurphyHill2011PeerInteraction}.
 
@@
 
-To evaluate \tool, we conducted a study making recommendations for \textsc{Error Prone}\footnote{http://errorprone.info}, an open source static analysis tool, to developers on the GitHub\footnote{https://github.com} code hosting platform.
-We calculated the effectiveness of \tool~by measuring the frequency of recommendations and how developers reacted to receiving suggestions from our system.
+To implement our approach for \tool, we conducted a study making recommendations for \textsc{Error Prone}\footnote{http://errorprone.info}, an open source static analysis tool, to developers on GitHub\footnote{https://github.com}, a popular code hosting website.
+We measured the effectiveness of \tool~by observing the frequency of recommendations, rate of true and false positive recommendations, and how developers react to receiving suggestions from our system.
 This research makes the following contributions:
@@
 Our implementation of \tool~builds on previous research examining recommendation systems in software engineering, techniques for learning new tools and features, approaches for tool recommendations, and existing systems that recommend software engineering tools.
-
-Previous work has also explored the tool discovery problem and barriers preventing users from adopting new tools, specifically in the software engineering industry.
-Researchers have created numerous tools to aid software engineers in their work, but these products are often ignored by developers~\cite{Ivanov2017Gaps}.
-Tilley and colleagues studied the challenges of adopting these research-of-the-shelf tools in industry~\cite{Tilley2003ROTS}.
-Johnson and colleagues reported reasons why software engineers don't use static analysis tools to help find and prevent bugs in their code~\cite{Johnson2013Why}.
-Xiao and colleagues examined barriers and social influences blocking developers from using security tools to detect and prevent vulnerabilities and malicious attacks~\cite{Xiao2014Security}.
-Our project aims to increase tool discovery and adoption among developers by automatically recommending useful software enginering tools.
 
@@
 
-\tool~aims to increase discovery and adoption of useful software engineering tools by implementing three design pillars: \textit{commend}, \textit{apprehend}, and \textit{recommend}.
+\tool~uses three design pillars to increase adoption of useful software engineering tools among developers: \textit{commend}, \textit{apprehend}, and \textit{recommend}.
 
@@
 
-Previous research peer interactions influenced our three design pillars for \tool.
+Our three design pillars for \tool~were inspired by previous research in tool recommendations.
 
 \subsection{Peer Interactions}
-Previous research shows that recommendations between colleagues are the most effective way to increase tool discovery and adoption~\cite{MurphyHill2011PeerInteraction}.
-Murphy-Hill interviewed software engineers and found that user-to-user peer interactions occur less frequently in the workplace but are more effective than system-to-user solutions.~\cite{MurphyHill2011PeerInteraction}~\cite{Murphy-Hill2015HowDoUsers}.
 
-To better understand what makes peer interactions an effective mode of tool discovery, prior work by Brown and colleagues observed how software users recommend tools to each other while completing tasks.
-They found that \emph{receptiveness} is a significant factor in determining the effectiveness of a tool recommendation, while other characteristics such as politeness and persuasiveness do not significantly impact the outcome of a suggestion~\cite{vlhcc17}.
-We designed \tool~to integrate user receptivity into our approach for making tool recommendations to increase awareness of programming tools.
+Research suggests recommendations between colleagues is the most effective mode of tool discovery.
+Murphy-Hill and colleagues interviewed software engineers and found that, even though peer interactions occur less frequently in the workplace, developers prefer these user-to-user recommendations over system-to-user interactions.~\cite{MurphyHill2011PeerInteraction}~\cite{Murphy-Hill2015HowDoUsers}.
+Similarly, Welty discovered that software users sought help from colleagues more often than search engines and help menus~\cite{Welty2011Help}.
 
-Previous work emphasizes the importance of user receptiveness.
-Fogg outlined best practicies for creating persuasive technology to change user behavior, and argued designers must choose a receptive audience~\cite{FoggPersuasive}.
-We define receptiveness using two criteria outlined by Fogg: 1) demonstrating desire and 2) familiarity with target behavior.
-Below we explain how we designed \tool~to recommend programming tools to software developers based on their desire and familiarity.
+To better understand what makes peer interactions an effective mode of tool discovery, Brown and colleagues observed how software users recommend tools to each other while completing tasks to study characteristics of peer interactions.
+Their results suggest \emph{receptiveness} is a significant factor in determining the outcome of a tool recommendation, while other characteristics such as politeness and persuasiveness are not as important~\cite{vlhcc17}.
+Fogg argues that a receptive audience is vital for designing persuasive technology, and defines receptiveness as: 1) demonstrating a desire and 2) familiarity with a target behavior~\cite{FoggPersuasive}.
+Below we explain how our design pillars for \tool~to recommend programming tools to software developers based on their desire and familiarity.
 
-\subsubsection{Desire}
+\subsubsection{Demonstrate Desire}
 
-A key desire of software users is to have enjoyable and problem-free experiences with software.
-Producers of software applications also have a similar desire to create high-quality functioning programs for users.
-A 2002 study revealed that software engineers demonstrate this desire by spending the majority of the software development process and 70-80\% of their time testing and debugging code~\cite{NIST}.
-To aid developers in finding, fixing, and preventing various issues in code, many different types of tools have been created to help accomplish these tasks.
-However, despite the existence of effective tools for detecting errors, the number of bugs in software is increasing~\cite{HaveThingsChanged}.
+Software developers and users both desire high-quality code without errors.
+This desire is demonstrated by the fact software engineers spend the majority their time testing and debugging code~\cite{NIST}.
+Our \textit{commend}
+
 \tool~aims to increase tool discovery by recommending software engineering tools designed to promote developers' desires for improving software quality.
@@
 \section{Implementation Walkthrough}
+
+Don't mention Error Prone or GitHub until here (other than intro).
 

### 2018-04-04 paper/paper.tex
Reading group feedback changes

@@
 To increase software engineer productivity, toolsmiths create tools and features to automatically complete software development tasks.
-However, these useful tools are often undiscovered or ignored by developers which is problematic for software applications that rely on programmer efficiency and correctness.
-This paper introduces \tool, an automated recommendation system designed for researchers to increase awareness of their products by making recommendations to developers.
-To help improve tool adoption among software engineers, we developed implemented a novel approach and design principles that integrate concepts of user-to-user suggestions and industry practices in \tool, and our results suggest this approach is more effective in making tool recommendations compared to other styles.
+However, these useful tools are often undiscovered or ignored by developers, which is problematic for software applications that rely on programmer efficiency and correctness.
+This paper introduces a new approach to making software engineering tool recommendations that integrates characteristics from user-to-user suggestions and industry practices for researchers to increase awareness of their products among developers.
+To help improve tool adoption among software engineers, we implemented this approach in \tool, an automated recommendation system, and found our design is more effective for increasing tool discovery compared to other styles of tool recommendations.
 \end{abstract}
@@
 
-To keep up with rising demands for technology, software engineers emphasize \textit{software quality}.
-Throughout the software development life cycle, development teams monitor code metrics that impact expectations of software producers and consumers~\cite{KitchenhamQualityTarget}.
-However, despite increased attention to software quality, buggy code remains a problem and the number of defects in software is increasing~\cite{HaveThingsChanged}.
+To maintain and meet rising demands for technology, software engineers emphasize \textit{software quality} throughout the development process, monitoring metrics that impact software producers and consumers~\cite{KitchenhamQualityTarget}.
+However, despite increased attention to quality, buggy code remains a problem as the number of software errors increases~\cite{HaveThingsChanged}.
 The Software Fail Watch by Tricentis suggests software failures impacted 3.7 billion users and caused \$1.7 trillion in financial losses in 2017.\footnote{https://www.tricentis.com/software-fail-watch/} Additionally, the process of finding and fixing bugs, or debugging, is a time-consuming and costly activity.
-The National Institute of Standards and Technology reports software engineers spend 70-80\% of work time debugging and the average time to debug one error is 17.4 hours~\cite{NIST}.
-Fixing defects early in the development process is also important since studies show debugging costs increase the longer a bug remains in code~\cite{SEEconomics, SoftwareAssuranceSDLC}.
+The National Institute of Standards and Technology reported software engineers spend 70-80\% of work time debugging and on average one error takes 17.4 hours to debug~\cite{NIST}.
+Finding and fixing defects early during development is also important since studies show debugging costs increase the longer a bug remains in code~\cite{SEEconomics, SoftwareAssuranceSDLC}.
 
-To improve code quality and prevent errors, researchers and toolsmiths have created software engineering tools to aid developers in their work.
-Prior work shows that tools for static analysis~\cite{UsingStaticAnalysis}, refactoring~\cite{Murphy-HillFitness}, security, and more are beneficial for improving code and preventing bugs.
+To improve code quality, researchers and toolsmiths have created software engineering tools to aid developers in their work.
+Research shows that tools for static analysis~\cite{UsingStaticAnalysis}, refactoring~\cite{Murphy-HillFitness}, security, and more are beneficial for improving code and preventing bugs.
 These tools can automatically perform a wide variety of software development tasks to save time and effort for developers.
@@
 
-To help solve the tool discovery problem among software engineers, we developed \tool.
-Our system automatically recommends development tools by analyzing developer changes and integrating characteristics of peer interactions and software engineering practices.
-\tool~is designed for toolsmiths to increase awareness of their products by systematically running their tools and making customized recommendations to developers, the largest code hosting platform in the world~\cite{GousiosGitHub}.
-This paper presents the novel approach and design of our system and evaluates the effectiveness of our tool in a real-world scenario.
+To help solve the tool discovery problem among software engineers, we developed an approach for making automated tool recommendations.
+Our approach integrates characteristics of peer interactions and software engineering practices, and can accomodate many different types of software engineering tools to make customized suggestions to developers.
+Our technique is based on three main design pillars- \textit{commend}, \textit{apprehend}, and \textit{recommend}.
+These principles differentiate our approach from existing recommender methods and help improve the effectiveness of automated tool recommendations.
 
@@
 
-To implement our approach for \tool, we conducted a study making recommendations for \textsc{Error Prone}\footnote{http://errorprone.info}, an open source static analysis tool, to developers on GitHub\footnote{https://github.com}, a popular code hosting website.
-We measured the effectiveness of \tool~by observing the frequency of recommendations, rate of true and false positive recommendations, and how developers react to receiving suggestions from our system.
+To evaluate our approach, we implemented \tool.
+Our initial implementation of \tool~for this study recommends \textsc{Error Prone}\footnote{http://errorprone.info}, an open source static analysis tool for Java code, to developers on GitHub\footnote{https://github.com}, a popular code hosting and collaboration website.
+We measured the effectiveness of our system by observing the frequency of recommendations and how developers reacted to receiving suggestions from our system.
 This research makes the following contributions:
@@
  \item a novel approach for recommender systems to increase awareness of software engineering tools, and
- \item an evaluation of \tool~ recommending \textsc{Error Prone} to developers on GitHub.
+ \item an implementation and evaluation of \tool~recommending a static analysis tool to developers.
  \end{itemize}
@@
 
-\tool~uses three design pillars to increase adoption of useful software engineering tools among developers: \textit{commend}, \textit{apprehend}, and \textit{recommend}.
+Our approach uses three design pillars to increase awareness of software engineering tools.
+Our technique \textit{commends} developers for their work, \textit{apprehends} additional opportunities for improvement, and \textit{recommends} useful development tools to improve the code.
 

### 2018-04-05 paper/paper.tex
Reading group feedback approach, desc, w

@@
 %TODO: Use related work from whatever conference committee
-Our implementation of \tool~builds on previous research examining recommendation systems in software engineering, techniques for learning new tools and features, approaches for tool recommendations, and existing systems that recommend software engineering tools.
+This work builds on previous research examining recommendation systems in software engineering, techniques for learning new tools, approaches for tool recommendations, and existing automated recommendation systems that recommend software engineering tools.
 
@@
 
+\section{Motivation}
+
+Our tool recommendation approach is motivated by previous research in tool discovery and peer interactions.
+
+\subsection{Peer Interactions}
+
+Research suggests recommendations between colleagues is the most effective mode of tool discovery.
+Murphy-Hill and colleagues interviewed software engineers and found that, even though they appear less frequently in the workplace, developers prefer peer interactions over system-to-user recommendations.~\cite{MurphyHill2011PeerInteraction}~\cite{Murphy-Hill2015HowDoUsers}.
+Similarly, Welty discovered that software users sought help from colleagues more often than search engines and help menus~\cite{Welty2011Help}.
+
+To better understand what makes peer interactions effective, Brown and colleagues observed how software users recommend tools to each other while completing tasks.
+Their results suggest \emph{receptiveness} is a significant factor in determining the outcome of tool recommendations, while other characteristics such as politeness and persuasiveness are not as important~\cite{vlhcc17}.
+Fogg argues a receptive audience is vital for designing persuasive technology, and describes receptiveness as: 1) demonstrating a desire and 2) familiarity with acquiring a target behavior~\cite{FoggPersuasive}.
+In this research, our target behavior is the adoption of useful development tools and these two criteria for receptiveness influenced the design principles for our approach for recommending software engineering tools.
+
 \section{Approach}
 
-Our approach uses three design pillars to increase awareness of software engineering tools.
-Our technique \textit{commends} developers for their work, \textit{apprehends} additional opportunities for improvement, and \textit{recommends} useful development tools to improve the code.
+Our approach uses three design pillars to increase awareness of software engineering tools: \textit{commend} developers on their work, \textit{apprehend} additional opportunities for improvement, and \textit{recommend} useful development tools to enhance the quality of the code.
+
+\subsection{Commend}
+
+Brown and colleages defined demonstrating a desire to adopt a particular behavior as users expressing interest in ``discovering, using, or learning more information'' about a new practice.
+In software engineering, developers desire to write high-quality programs without errors.
+This desire is demonstrated by the fact software engineers spend the majority their time testing and debugging programs~\cite{NIST}.
+Our approach capitalizes on developers' desires to produce mistake-free code by commending developers for their work.
+Futhermore, psychology research shows that people respond better to praise than blame~\cite{PraiseAndBlame}.
+To help improve tool adoption among software engineers, our approach analyzes code changes made by developers to determine their intentions, then compliments the developer on their attempt to improve the code quality.
+
+%\tool~aims to increase tool discovery by recommending software engineering tools designed to promote developers' desires for improving software quality.
+
+%Our goal is for \tool~to increase awareness of software engineering tools.
+For our initial evaluation in this paper, we  recommending \textsc{Error Prone}.
+\textsc{Error Prone} is a static analysis tool that uses a suite of defined bug patterns to detect errors in Java code.
+Static analysis tools like \textsc{Error Prone} are useful for debugging and preventing errors in source code for applications, however they are often underutilized by software engineers~\cite{Johnson2013Why}.
+
+\subsection{Apprehend}
+
+Familiarity is also a key part of receptiveness and important in increasing adoption of a target behavior.
+Fogg suggests users are more likely to adopt a target behavior if they are familiar with it~\cite{FoggPersuasive}.
+To improve usage of software engineering tools, our approach integrates familiarity.
+First, we make recommendations based on developers' contributions to recent projects.
+Scalabrino and colleagues claim code understandability is one of the most important factors for software development, maintenance, debugging, and testing~\cite{Scalabrino2017Understandability}.
+Developers should be familiar with the project before making changes to the code base.
+More specifically, our approach apprehends similar pieces of code the developer may also want to change.
+After analyzing the code changes and commending the developer on their work, our approach analyzes the entire code base to search for similar opportunities for improvement.
+
+%To choose a familiar audience, our approach makes recommendations on proposed Github code changes submitted by users.
+Developers should be knowledgeable and familiar with the changes they propose, as well as the code base to which they are contributing.
+\tool~suggests \textsc{Error Prone} when a reported error is fixed by a developer in a pull request or commit, and the same bug exists elsewhere in the code.
+
+\subsection{Recommend}
+
+After integrating user receptiveness into our design, the final step is to make a recommendation.
+
+\section{Implementation Walkthrough}
+
+To implement our approach, we developed \tool~to recommend \textsc{Error Prone} to GitHub developers.
+This section gives an overview describing the general process of how the automated recommendation system works.
 
@@
 
-\section{Design}
-
-Our three design pillars for \tool~were inspired by previous research in tool recommendations.
-
-\subsection{Peer Interactions}
-
-Research suggests recommendations between colleagues is the most effective mode of tool discovery.
-Murphy-Hill and colleagues interviewed software engineers and found that, even though peer interactions occur less frequently in the workplace, developers prefer these user-to-user recommendations over system-to-user interactions.~\cite{MurphyHill2011PeerInteraction}~\cite{Murphy-Hill2015HowDoUsers}.
-Similarly, Welty discovered that software users sought help from colleagues more often than search engines and help menus~\cite{Welty2011Help}.
-
-To better understand what makes peer interactions an effective mode of tool discovery, Brown and colleagues observed how software users recommend tools to each other while completing tasks to study characteristics of peer interactions.
-Their results suggest \emph{receptiveness} is a significant factor in determining the outcome of a tool recommendation, while other characteristics such as politeness and persuasiveness are not as important~\cite{vlhcc17}.
-Fogg argues that a receptive audience is vital for designing persuasive technology, and defines receptiveness as: 1) demonstrating a desire and 2) familiarity with a target behavior~\cite{FoggPersuasive}.
-Below we explain how our design pillars for \tool~to recommend programming tools to software developers based on their desire and familiarity.
-
-\subsubsection{Demonstrate Desire}
-
-Software developers and users both desire high-quality code without errors.
-This desire is demonstrated by the fact software engineers spend the majority their time testing and debugging code~\cite{NIST}.
-Our \textit{commend}
-
-\tool~aims to increase tool discovery by recommending software engineering tools designed to promote developers' desires for improving software quality.
-
-Our goal is for \tool~to increase awareness of software engineering tools.
-For our initial evaluation in this paper, we target software engineers' desire to produce mistake-free code by automatically recommending \textsc{Error Prone}.
-\textsc{Error Prone} is a static analysis tool that uses a suite of defined bug patterns to detect errors in Java code.
-Static analysis tools like \textsc{Error Prone} are useful for debugging and preventing errors in source code for applications, however they are often underutilized by software engineers~\cite{Johnson2013Why}.
-
-\subsubsection{Familiarity}
-
-Choosing an audience familiar with the target behavior is also vital to increasing adoption.
-To increase use of helpful programming tools, our system focuses on making recommendations to software engineers within the context of the projects they develop.
-Scalabrino and colleagues claim code understandability is one of the most important factors for software development, maintenance, debugging, and testing~\cite{Scalabrino2017Understandability}.
-\tool~uses familiarity with source code to recommend tools to software engineers in code they modify.
-
-To choose a familiar audience, our approach makes recommendations on proposed Github code changes submitted by users.
-Developers should be knowledgeable and familiar with the changes they propose, as well as the code base to which they are contributing.
-\tool~suggests \textsc{Error Prone} when a reported error is fixed by a developer in a pull request or commit, and the same bug exists elsewhere in the code.
-
-\section{Implementation Walkthrough}
-
-Don't mention Error Prone or GitHub until here (other than intro).
-
 \section{Implementation Description}
 
-\subsection{Software Engineering}
+This sections provides technical details on the implementation of our approach in \tool.
+The design of our system is motivated by current practices in the software engineering industry to make \tool~similar to a peer for developers.
 
-\tool~incorporates key software engineering industry concepts to improve tool discovery among software developers.
+\subsection{Continuous Integration}
 
-\subsubsection{Continuous Integration}
+To analyze developer changes, our system utilizes continuous integration concepts and tools to observe code modifications to GitHub repositories.
+\tool~is implemented as a plugin for Jenkins, ``the leading open source automation server'' for source code deployment and delivery.\footnote{https://jenkins.io/} We use Jenkins to periodically check for new modifications, commits and pull requests, to GitHub projects every 15 minutes.
+Our system ignores any commits or pull requests from developers that do not modify a Java file.
+When a new code change is found, Jenkins to automatically analyze the patch and run our approach.
 
-Our system utilizes continuous integration to recommend useful tools beforecode changes are integrated into the main repository, or merged.
-\tool~is implemented as a plugin for Jenkins, ``the leading open source automation server'' for source code deployment and delivery.\footnote{https://jenkins.io/} The system uses Jenkins to clone Github repositories and periodically check for newly-opened pull requests and commits every 15 minutes.
-When a new code change is found, our system uses Jenkins to automatically run our approach to recommend useful software engineering tools.
+To analyze the source code, we target projects that use the Maven~\footnote{https://maven.apache.org/} build automation and software dependency management tool for Java applications.
+We automatically inject \textsc{Error Prone} as a Maven plugin to a repository's project object model file (\textit{pom.xml}) and run the build process with the tool.
+\tool~builds both the original version of the code before the proposed changes were made (base) and the changed version of the repository with the modifications from the developer (head) to inspect differences.
+The base and head versions of the source code are tracked using the JGit Java API.\footnote{https://eclipse.org/jgit/}
 
-To analyze the source code, we target projects that use the Maven~\footnote{https://maven.apache.org/} build automation and software management tool for Java applications.
-Our approach uses Maven to automatically handle dependencies and perform the static analysis when the project builds.
-We inject the desired software engineering tool as a Maven plugin to repository's \textit{pom.xml} project object model file to add it to the build process.
-\tool~then builds both the original version of the code before the proposed changes were made (base) and the changed version of the repository with the modifications implemented (head) to inspect differences.
-Using Maven allows \tool~to run on a large number of Java projects that use the popular build tool and also makes our approach extendable to recommend other tools implemented as Maven plugins in future work.
-This also allows our system to easily be integrated into continuous integration builds for software applications to analyze code and recommend development tools to software engineers.
+\subsection{Debugging}
 
-\subsubsection{Debugging}
+Before commending developers on their work, \tool~must debug to find errors and determine if proposed code changes are a fix.
+After building the base and head versions with \textsc{Error Prone}, our system parses the output of each build to determine if any faults reported were removed between versions of code.
+To determine if a change fixes a defect, we developed an algorithm using the code differencing tool GumTree~\cite{GumTree}.
+GumTree allows us to identify actions (addition, delete, insert, move, and update) performed between the altered versions of the project.
 
-After analyzing the base and head versions of the code, our approach parses the build output of each version to determine if any reported errors were fixed in the code modifications.
-The software engineering tool identifies faults in the source code, and we take the tool's output and use it in an algorithm we developed to determine if GitHub user code changes fix a reported bug.
-Our technique uses the code differencing tool GumTree~\cite{GumTree} to identify actions (addition, delete, insert, move, and update) performed between altered code versions and parse the source code to convert the text into abstract syntax trees.
+To determine if an error was fixed, we take several things into consideration: First, we ignore errors that are removed but were not located in a file modified by the developer.
+This ensures that the GitHub user will be familiar with the code changed and potential error fixed.
+Second, we ignore changes where only delete actions were detected between the base and head versions of a file.
+This avoids making recommendations in situations where defects were only removed by developers.
+For example, deleting a class will remove errors reported by \textsc{Error Prone} in the source code, however the intention was not to fix the bugs.
+Thus, for a change to be considered a fix there must be new code added or existing code modified by the developer.
+Similarly, we also ignore classes that are deprecated by developers.
+These conditions were put in place minimize false positives and prevent errant recommendations to software engineers in our approach.
 
-To determine if an error was fixed, we take several things into consideration: First, our approach ignores errors that are reported as fixed but were not located in files modified by the developer.
-This ensures that the GitHub user will be familiar with the code change and error fix.
-Second, we ignore instances where only delete actions were detected between the base and head versions of a file.
-This avoids making recommendations in situations where bugs are removed but not fixed.
-For example, a refactoring task such as renaming a class is presented in the GitHub diff as removing code from the original file.
-This can eliminate bugs reported by Error Prone between code versions, but may also just move the error to another location in the source code.
-Similarly, we also ignore deprecated classes because the error reported was not fixed.
-These conditions help us minimize the number of false positives and prevent errant recommendations to developers in our approach.
+When a fix is identified in the changed version of code, \tool~finds the location of the fix in the head version.
+To find the modified line of code that fixed a bug, we use GumTree to parse the source code and convert it to abstract syntax trees.
+We look for the action closest to the offset of the error node determined from the line number reported by \textsc{Error Prone}.
+If the closest action is not a delete, then our approach uses the location of that action.
+Otherwise, our algorithm iteratively searches for the closest sibling node or parent nodes that is not a delete action.
+To apprehend different opportunities for similar changes, we iterate through the list of errors reported by \textsc{Error Prone} in the head version of code and look for instances of the same error that was fixed by the developer.
 
-When a fix is identified in the changed version of code, \tool~then aims to find the location of the fix in the head version.
-To find the modified line that fixed a bug, we use GumTree to parse the Java file and convert it into abstract syntax trees.
-We look for the action closest to the offset of the error node calculated from the bug line number reported by the software engineering tool, if applicable.
-If the closest action is not a delete, then our approach take the location takes the location of that action.
-Otherwise, if the line was removed our algorithm searches for the closest sibling node or if none exists then the location of the parent.
-Additionally, the line of the fix had to be converted to the equivalent position in the pull request or commit diff file displaying the changes between file versions, or number of lines below the "@@" header\footnote{https://developer.github.com/v3/pulls/comments/\#create-a-comment}, before moving on to the next phase.
+\subsection{Code Reviews}
 
-\subsubsection{Code Review}
+Code reviews between developers are a standard procedure of software engineering teams to improve code quality~\cite{CodeReviewingTrenches}.
+This practice also applies to GitHub projects, with many repositories requiring approval from another developer before changes can be merged into the main code base~\cite{PullRequestReview}.
+Our approach simulates peer code reviews by making recommendations for static analysis tools as a comment on pull requests and commits.
+Github allows users to make comments on specific lines of code in situ with the code changes.
+\tool~determines where to automatically make recommendation comments by converting the line number of the identified fix to the equivalent position in the diff file, or textual representation of code changes made in a commit or pull request, represented by the number of lines below the ``@@'' symbol in the header\footnote{https://developer.github.com/v3/pulls/comments/\#create-a-comment}.
 
-Code reviews from co-workers are often standard practice in software development~\cite{CBirdCodeReviewingTrenches}.
-Pull requests and commits are the primary methods of development contributions and code updates on GitHub~\cite{PullRequestReview}.
-Our approach simulates peer reviews by making recommendations for static analysis tools as a comment to the pull request or commit.
-\tool~automatically runs software engineering tools and analyzes the code changes, providing feedback to developers based on their changes based on the output from the tool.
-Github allows users to make comments on specific lines of code changed in pull requests and commits.
-\tool~leverages this functionality by recommending the tool as a comment at the fix location line from the previous step.
-Figure 1 presents an example recommendation from our system on a pull request.
-%TODO: Add screenshot
-
-To increase the likelihood of tool adoption, our system makes recommendations if the tool reports other instances of the fixed error in the latest version of the code.
-In the comment, \tool~automatically adds direct links to at most two separate locations of the same defect.
-Our hope is that this encourages developers to use software engineering toolsin their work to fix the similar errors and prevent additional bugs.
-Additionally, our system uses language similar to a colleage in recommendations.
-For instance, \tool~uses ``Good job!'' to compliment developers for fixing an error in their work~\cite{?}.
+To increase the likelihood of tool adoption, \tool~implements our approach by commending developers on their changes, apprehending chances for similar modifications, and recommending software engineering tools to find even more related errors.
+In the comment, \tool~uses language similar to a peer to compliment the author's code contribution.
+For instance, our system uses ``Good job!'' to commend developers for fixing an error.
+Additionally, our system presents similar instances of the fixed error found elsewhere in the code.
+\tool~automatically adds direct links to at most two different locations of the same defect where a similar fix can be applied.
+Finally, we recommend \textsc{Error Prone} and provide information about the tool to encourage developers to use software engineering tools in their future work to fix more related errors and more.
 
@@
 
-We designed our evaluation to gather quantitative and qualitative data addressing our research questions.
+To evaluate the effectiveness of our approach, we compared \tool~to different styles and mediums of tool recommendations
 
@@
 
-\subsubsection{RQ1}
+\subsubsection{Quantitative}
 
@@
 
-\subsubsection{RQ2}
+\subsubsection{Qualitative}
 
@@
 
-\subsection{How often can we expect \tool~to make recommendations?}
+\subsection{Quantitative}
 
@@
 
-\subsection{How useful are recommendations from \tool~to developers?}
+\subsection{Qualitative}
 

### 2018-04-17 paper/paper.tex
Updates to implementation walkthrough and approach

@@
 %\usepackage[pdftex]{graphicx}
-%\usepackage{multirow}
-%\usepackage{pgfplots}
+\usepackage{multirow}
+\usepackage{pgfplots}
 \usepackage{tikz}
@@
 
+\section{Approach}
+
+Our approach uses three design pillars to increase awareness of software engineering tools: \textit{commend} developers on their work, \textit{apprehend} additional opportunities for improvement, and \textit{recommend} useful development tools to enhance the quality of the code.
+
+\subsection{Commend}
+
+The first design principle of our approach finds places where a tool would be useful.
+To do this, our technique commends developers for their updates making improvements to code.
+We analyze code changes made by developers and then praise them for their work when they improve the quality of code.
+Additionally, psychology research also suggests people respond better to praise than blame~\cite{PraiseAndBlame}.
+Our approach applauds developers when they produce good work rather than rebuke them for making mistakes when they introduce new issues.
+
+To determine improvements in code quality, our approach monitors problems reported by the output of software engineering tools.
+For example, suppose we want to use our approach to increase awareness of useful refactoring tools.
+To do this, our technique will inspect code changes made by developers to determine if a refactoring activity occurs.
+If a refactoring activity is detected, then we commend the programmer for their work to improve the quality of the code.
+
+%Our goal is for \tool~to increase awareness of software engineering tools. For our initial evaluation in this paper, we  recommending \textsc{Error Prone}.
+
+\subsection{Apprehend}
+
+Next, our approach finds additional places to recommend useful software engineering tools.
+To find other opportunities for recommendations, we apprehend instances where developers can make source code improvements similar to their previous code changes and based on development tool analysis from the commend phase.
+This design principle helps reduce effort and provides information-related needs to software engineers, which Fischer suggests is a goal for help systems~\cite{Fischer1984ActiveHelpSystems}.
+
+After commending software engineers for their work, our approach automatically finds opportunities to make similar changes to improve the code.
+For example, after the programmer completes the refactoring task, we analyze the entire updated version of the code base to find other places where the same refactoring activity is applicable.
+
+%To choose a familiar audience, our approach makes recommendations on proposed Github code changes submitted by users.
+
+\subsection{Recommend}
+
+The final step of our approach is to recommend useful software engineering tools to developers.
+The recommendation to developers includes commending them for improving code quality and apprehending new opportunities for similar improvements.
+In our example, the recommendation to the developer will praise them for their work refactoring the code, provide additional places in the code where they can make similar refactoring changes, and then suggest the refactoring tool which is useful for detecting even more instances for refactoring activities.
+Our goal is that through commending and apprehending, we can improve the effectiveness of recommendations for software engineering tools and increase adoption among developers.
+
+%TODO: Non-lossy image
+%TODO: More interesting error
+\begin{figure*}
+	\includegraphics[width=\textwidth]{images/screenshot.png}
+	\caption{Screenshot of recommendation from \tool}	
+	\label{fig:tool} 
+\end{figure*}
+
 \section{Motivation}
@@
 
-\section{Approach}
-
-Our approach uses three design pillars to increase awareness of software engineering tools: \textit{commend} developers on their work, \textit{apprehend} additional opportunities for improvement, and \textit{recommend} useful development tools to enhance the quality of the code.
-
-\subsection{Commend}
+\subsubsection{Demonstrate Desire}
 
@@
 Our approach capitalizes on developers' desires to produce mistake-free code by commending developers for their work.
-Futhermore, psychology research shows that people respond better to praise than blame~\cite{PraiseAndBlame}.
 To help improve tool adoption among software engineers, our approach analyzes code changes made by developers to determine their intentions, then compliments the developer on their attempt to improve the code quality.
 
-%\tool~aims to increase tool discovery by recommending software engineering tools designed to promote developers' desires for improving software quality.
-
-%Our goal is for \tool~to increase awareness of software engineering tools.
-For our initial evaluation in this paper, we  recommending \textsc{Error Prone}.
-\textsc{Error Prone} is a static analysis tool that uses a suite of defined bug patterns to detect errors in Java code.
-Static analysis tools like \textsc{Error Prone} are useful for debugging and preventing errors in source code for applications, however they are often underutilized by software engineers~\cite{Johnson2013Why}.
-
-\subsection{Apprehend}
+\subsubsection{Familiarity}
 
@@
 Developers should be familiar with the project before making changes to the code base.
-More specifically, our approach apprehends similar pieces of code the developer may also want to change.
-After analyzing the code changes and commending the developer on their work, our approach analyzes the entire code base to search for similar opportunities for improvement.
+More specifically, our approach apprehends code the developer may also want to change based on their previous update.
 
-%To choose a familiar audience, our approach makes recommendations on proposed Github code changes submitted by users.
-Developers should be knowledgeable and familiar with the changes they propose, as well as the code base to which they are contributing.
-\tool~suggests \textsc{Error Prone} when a reported error is fixed by a developer in a pull request or commit, and the same bug exists elsewhere in the code.
+\section{Implementation Walkthrough}
+
+To implement our approach, we developed \tool~to recommend the \textsc{Error Prone} static analysis tool to developers on GitHub.
+This section provides a general overview of how our automated recommendation system works.
+
+\subsection{Commend}
+
+First, a GitHub user makes a change to a repository.
+\tool~automatically analyzes to commits and pull requests GitHub projects to find opportunities to commend developers when bugs reported by \textsc{Error Prone} are removed.
+\textsc{Error Prone} is a static analysis tool that uses a suite of defined bug patterns to detect errors in Java code.
+Static analysis tools like \textsc{Error Prone} are useful for debugging and preventing errors in source code for applications, however they are often underutilized by software engineers~\cite{Johnson2013Why}.
+More details on how our implementation determines a bug fix can be found in Section 6.2.
+
+\subsection{Apprehend}
+
+Next, \tool~apprehends places where similar opportunities to the code can be made.
+GitHub should be knowledgeable and familiar with the changes they propose, as well as the code base to which they are contributing.
+\tool~suggests \textsc{Error Prone} when a reported bug is fixed by a developer in a commit or pull request, but the same error still exists elsewhere in the code.
 
@@
 
-After integrating user receptiveness into our design, the final step is to make a recommendation.
-
-\section{Implementation Walkthrough}
-
-To implement our approach, we developed \tool~to recommend \textsc{Error Prone} to GitHub developers.
-This section gives an overview describing the general process of how the automated recommendation system works.
-
-\subsection{Commend}
-
-\subsection{Apprehend}
-
-\subsection{Recommend}
+Finally, \tool~recommends \textsc{Error Prone} to the GitHub user at the location of their fix in the code.
+We commend developers by telling them ``Good job!'' and presenting the error they fixed.
+\tool~ provides the apprehended opportunities for similar code changes as links to buggy lines with the same error in other parts of the code.
+Finally, we provide a link to the \textsc{Error Prone} website for users to learn more about the tool if they are interested.
+Figure \ref{fig:tool} provides a sample recommendation from \tool~to a developer for \textsc{Error Prone} on a GitHub pull request.
 
@@
 This sections provides technical details on the implementation of our approach in \tool.
-The design of our system is motivated by current practices in the software engineering industry to make \tool~similar to a peer for developers.
+The design of our system is motivated by current practices in the software engineering industry to make \tool~more similar to a peer for developers.
 
@@
 
-\subsection{Code Reviews}
+\subsection{Code Review}
 
@@
 \tool~determines where to automatically make recommendation comments by converting the line number of the identified fix to the equivalent position in the diff file, or textual representation of code changes made in a commit or pull request, represented by the number of lines below the ``@@'' symbol in the header\footnote{https://developer.github.com/v3/pulls/comments/\#create-a-comment}.
+An example of a comment from \tool~is displayed in Figure \ref{fig:tool}.
 
@@
 
-To evaluate the effectiveness of our approach, we compared \tool~to different styles and mediums of tool recommendations
+To evaluate the effectiveness of our approach, we compared \tool~to different styles and mediums of tool recommendations.
 
@@
 
-To analyze 700+ GitHub repositories simultaneously, we used Ansible\footnote{https://www.ansible.com/} to generate Jenkins jobs running \tool~on multiple virtual machines.
+To analyze 700+ GitHub repositories simultaneously, we set up \tool~on virtual machines.
+We used Ansible\footnote{https://www.ansible.com/} to automatically generate and provision Jenkins jobs for every project.
+To limit the load on each machine, we ran our study in parallel by dividing the Jenkins jobs among \textit{n} virtual CentOS images.
+The scripts and instructions to used setup our study environment for \tool~are publicly available to view online.
 
-\subsubsection{Quantitative}
+To test the effectiveness of our approach, we used four different recommendation styles based on our design principles of commending developers for their work and apprehending opportunities to make similar changes.
+The four recommendation styles include commending and apprehending, commending only, apprehending only, and neither commending nor apprehending.
+In each case, a recommendation was always made.
+We adapted \tool~to make recommendations without commending or without apprehending.
+%TODO: Without commendation,...
+Without apprehending, our system simply commends the developer for their fix and does not link to similar errors found in other parts of the code.
+For the final recommendation without commending or apprehending, we decided to send recommendations to developers by email without commending them for their patch and not providing other instances to make a similar fix.
+An overview of each style is presented in Table~\ref{table:styles}.
 
-To answer our first research question, we observed how often our approach makes recommendations on commits and pull requests.
-In addition to the frequency of recommendations, we also tracked instances where \textsc{Error Prone} defects were removed but not reported as fixed according to our fix identification algorithm in Section III.B.2, the number of occurrences where errors were fixed but no other instances of that bug were found in the code, and the false positive rate.
+\begin{table*}
+\begin{center}
+\caption{Study Recommendation Styles}
+\begin{tabular*}{\textwidth}{ c|c|p{5cm}|p{5cm}| }
+  \multicolumn{2}{ c }{\textbf{}} & \multicolumn{2}{ c }{\textbf{Commend}} \\ \cline{2-4}
+ & & Yes & No \\ \cline{2-4}
+\multirow{2}{*}{\textbf{Apprehend}} 
+	 & Yes & \tool  & Modified \tool~(without commending) \\ \cline{2-4}
+	 & No & Modified \tool~(without apprehending) &  Email  \\ \cline{2-4}
+\end{tabular*}
+\label{table:styles}
+\end{center}
+\end{table*}
+
+\subsubsection{Recommendation Review}
 
@@
 
-\subsubsection{Qualitative}
+\subsubsection{Debriefing}
 
@@
 \subsubsection{Quantitative}
+
+To determine the effectiveness of our approach, we observed how often\tool~makes recommendations on commits and pull requests.
+In addition to the frequency of recommendations, we also tracked instances where \textsc{Error Prone} defects were removed but not reported as fixed according to our fix identification algorithm in Section III.B.2, the number of occurrences where errors were fixed but no other instances of that bug were found in the code, and the false positive rate.
 
@@
 \subsection{Qualitative}
+
+\subsubsection{Recommend}
+
+\subsubsection{Commend, Recommend}
+
+\subsubsection{Apprehend, Recommend}
+
+\subsubsection{Commend, Apprehend, Recommend}
 
@@
 
-To improve discovery of software engineering tools, we plan to increase the practicality of \tool~for researchers to implement our system with their projects.
-A next step is to extend our approach to work with multiple static analysis tools, such as Checkstyle\footnote{http://checkstyle.sourceforge.net/} for Java.
+The main goal of our future work is to increase the practicality of \tool~for researchers and toolsmiths to implement our approach with their tools.
+A next step is to implement our approach with multiple static analysis tools, such as Checkstyle\footnote{http://checkstyle.sourceforge.net/} for Java.
 This will allow us to have more opportunities to make recommendations to developers based on the output from different tools.

### 2018-04-17 paper/paper.tex
Implementation description more details added

@@
 To analyze the source code, we target projects that use the Maven~\footnote{https://maven.apache.org/} build automation and software dependency management tool for Java applications.
-We automatically inject \textsc{Error Prone} as a Maven plugin to a repository's project object model file (\textit{pom.xml}) and run the build process with the tool.
-\tool~builds both the original version of the code before the proposed changes were made (base) and the changed version of the repository with the modifications from the developer (head) to inspect differences.
-The base and head versions of the source code are tracked using the JGit Java API.\footnote{https://eclipse.org/jgit/}
+We clone the GitHub repository, automatically inject \textsc{Error Prone} as a Maven plugin to a repository's project object model file (\textit{pom.xml}), and then run the build process with the static analysis tool.
+\tool~builds both the original version of the code before the proposed changes (base) and the updated version of the repository with the modifications from the developer (head) to inspect differences in the \textsc{Error Prone} output.
+The JGit Java API\footnote{https://eclipse.org/jgit/} is used to clone projects and checkout the base and head versions of the code for our analysis.
 
@@
 \tool~determines where to automatically make recommendation comments by converting the line number of the identified fix to the equivalent position in the diff file, or textual representation of code changes made in a commit or pull request, represented by the number of lines below the ``@@'' symbol in the header\footnote{https://developer.github.com/v3/pulls/comments/\#create-a-comment}.
+Our system uses the jcabi Object Oriented GitHub API\footnote{http://github.jcabi.com/} to automatically comment on GitHub commits and pull requests.
 An example of a comment from \tool~is displayed in Figure \ref{fig:tool}.

### 2018-04-17 eval_scripts/setup.sh
Updating evaluation scripts

@@ -21,17 +21,29 @@ sudo yum -y install ansible
 echo "localhost ansible_connection=local" > hosts
 sudo mv hosts /etc/ansible/hosts
 
-# Start tool-recommender-bot study
-wget https://raw.githubusercontent.com/chbrown13/PullRecommender/master/eval_scripts/tool-recommender-bot.yml
-wget https://raw.githubusercontent.com/chbrown13/tool-recommender-bot/master/eval_scripts/delete.yml
-wget https://raw.githubusercontent.com/chbrown13/PullRecommender/master/jenkins.xml
-wget https://raw.githubusercontent.com/chbrown13/PullRecommender/master/eval_scripts/eval.py
+# Download files and dependencies
+wget -q https://raw.githubusercontent.com/chbrown13/PullRecommender/master/eval_scripts/tool-recommender-bot.yml
+wget -q https://raw.githubusercontent.com/chbrown13/tool-recommender-bot/master/eval_scripts/delete.yml
+wget -q https://raw.githubusercontent.com/chbrown13/PullRecommender/master/jenkins.xml
+wget -q https://raw.githubusercontent.com/chbrown13/PullRecommender/master/eval_scripts/eval.py
+wget -q https://repo1.maven.org/maven2/com/google/errorprone/error_prone_ant/2.2.0/error_prone_ant-2.2.0.jar
+wget -q https://github.com/GumTreeDiff/gumtree/releases/download/2.0.0/gumtree.jar
+wget -q https://repo.eclipse.org/content/groups/releases//org/eclipse/jgit/org.eclipse.jgit/4.9.0.201710071750-r/org.eclipse.jgit-4.9.0.201710071750-r.jar
+wget -q http://central.maven.org/maven2/com/jcraft/jsch/0.1.46/jsch-0.1.46.jar
+wget -q http://central.maven.org/maven2/org/apache/commons/commons-email/1.3.1/commons-email-1.3.1.jar
+wget -q http://central.maven.org/maven2/javax/mail/mail/1.4.7/mail-1.4.7.jar
+
+# Create jenkins config files
 python eval.py
 
-## Manual Steps ##
+### Manual Steps ###
 # Go to http://<ip>:8080/ 
-# Install suggested plugins
-# Follow instructions to start jenkins and create admin user
-# Enable anonymous authorization (Configure Global Security Settings, Anyone can do anything)
-# Disable requiretty in visudo
[…]

### 2018-04-18 paper/paper.tex
Intro and some related work updates

@@
 
-Although software quality is important, development tools created to improve code are often ignored~\cite{Ivanov2017Gaps}.
-Previous work explores barriers preventing software engineers from adopting new tools: Tilley and colleagues studied challenges of adopting research-off-the-shelf tools in industry~\cite{Tilley2003ROTS}; Johnson and colleagues reported reasons why software engineers don't use static analysis tools~\cite{Johnson2013Why}; and Xiao and colleagues examined barriers of using security tools to prevent vulnerabilities and malicious attacks~\cite{Xiao2014Security}.
-One of the main barriers to tool adoption is the discoverability barrier, where users are unaware tools exist~\cite{Murphy-HillScreencastingDiscovery}.
-Lack of software engineering tool usage can lead to poor code quality, inconvenienced users, and significant amounts of time and money spent fixing errors.
-Many existing automated approaches have been implemented to increase awareness of software tools and features, but Murphy-Hill and colleagues found that developers prefer learning about tools from colleagues during normal work activities, or \textit{peer interaction}~\cite{MurphyHill2011PeerInteraction}.
+Although software quality is important, development tools created to improve code quality are often ignored by software engineers~\cite{Ivanov2017Gaps}.
+Previous work explores barriers preventing software developers from adopting new tools, and researchers have studied challenges to adopting tools for debugging~\cite{CaoDebugging}, static analysis~\cite{Johnson2013Why}, security~\cite{Xiao2014Security}, refactoring~\cite{MurpyHillBarriersRefactoring}, documentation~\cite{ForwardDocumentationRelevance}, and more in their work.
+One of the main barriers to tool adoption is the discoverability barrier, where users are unaware of a tool's existence~\cite{Murphy-HillScreencastingDiscovery}.
+This lack of tool awareness in the software engineering industry can lead to the production of poor-quality applications, inconvenienced users, and significant amounts of time and money spent fixing errors.
+Many existing automated approaches have been implemented to increase awareness of software tools and features, but Murphy-Hill and colleagues found that developers prefer learning about tools from colleagues during normal work activities, or \textit{peer interactions}~\cite{MurphyHill2011PeerInteraction}.
 
 To help solve the tool discovery problem among software engineers, we developed an approach for making automated tool recommendations.
-Our approach integrates characteristics of peer interactions and software engineering practices, and can accomodate many different types of software engineering tools to make customized suggestions to developers.
-Our technique is based on three main design pillars- \textit{commend}, \textit{apprehend}, and \textit{recommend}.
-These principles differentiate our approach from existing recommender methods and help improve the effectiveness of automated tool recommendations.
+Our approach integrates characteristics of peer interactions and software engineering practices to suggest useful tools to developers.
+We base our technique on three main design pillars- \textit{commend}, \textit{apprehend}, and \textit{recommend}.
+These principles differentiate our approach from existing techniques because they can be applied to many different types of software engineering tools and integrate user receptiveness to make customized recommendations to developers.
 
@@
 To evaluate our approach, we implemented \tool.
-Our initial implementation of \tool~for this study recommends \textsc{Error Prone}\footnote{http://errorprone.info}, an open source static analysis tool for Java code, to developers on GitHub\footnote{https://github.com}, a popular code hosting and collaboration website.
-We measured the effectiveness of our system by observing the frequency of recommendations and how developers reacted to receiving suggestions from our system.
+The initial implementation of \tool~for this study recommends \textsc{Error Prone}\footnote{http://errorprone.info}, an open source static analysis tool for Java code, to developers on GitHub\footnote{https://github.com}, a popular code hosting and collaboration website.
+We measured the effectiveness of our system by observing the frequency of recommendations and how developers reacted to receiving suggestions for tools from our system.
 This research makes the following contributions:
@@
 %TODO: Use related work from whatever conference committee
-This work builds on previous research examining recommendation systems in software engineering, techniques for learning new tools, approaches for tool recommendations, and existing automated recommendation systems that recommend software engineering tools.
+This project builds on previous research examining the intersection between recommendation systems and software engineering.
 
-There are numerous existing technical approaches created to solve the tool discovery problem.
+Previous research has also studied techniques developers use to learn new information.
+Piorkowski and colleagues applied Information Foraging Theory to software engineers to determined how developers seek information~\cite{FlemingReactiveInformationForaging}.
+This research differs from these approaches by presenting and implementing a new technique
+
+Prior work has examined help systems for soft in software engineering.
+
+Researchers have created many different approaches for tool recommendations.
 Fischer and colleagues found that systems requiring users to explicitly seek help, or passive help systems, are ineffective and active help systems are more useful for increasing tool awareness~\cite{Fischer1984ActiveHelpSystems}.
+
+There are several existing automated approaches created to solve the tool discovery problem among software developers.
 Gordon and colleagues developed Codepourri, a system using crowdsourcing to make recommendations for Python code~\cite{Gordon2015Codepourri}.

### 2018-04-19 paper/paper.tex
Updates to related work section

@@
 
-Although software quality is important, development tools created to improve code quality are often ignored by software engineers~\cite{Ivanov2017Gaps}.
-Previous work explores barriers preventing software developers from adopting new tools, and researchers have studied challenges to adopting tools for debugging~\cite{CaoDebugging}, static analysis~\cite{Johnson2013Why}, security~\cite{Xiao2014Security}, refactoring~\cite{MurpyHillBarriersRefactoring}, documentation~\cite{ForwardDocumentationRelevance}, and more in their work.
-One of the main barriers to tool adoption is the discoverability barrier, where users are unaware of a tool's existence~\cite{Murphy-HillScreencastingDiscovery}.
+Although software quality is important, software engineering tools created to improve code quality are often ignored by developers~\cite{Ivanov2017Gaps}.
+Previous work explores barriers preventing software engineers from utilizing useful tools for debugging~\cite{CaoDebugging}, static analysis~\cite{Johnson2013Why}, security~\cite{Xiao2014Security}, refactoring~\cite{MurpyHillBarriersRefactoring}, documentation~\cite{ForwardDocumentationRelevance}, and more to help complete programming tasks.
+Additionally, Tilley and colleagues presented challenges for professional software developers in industry adopting software engineering tools created by researchers, or research-off-the-shelf (ROTS) software~\cite{Tilley2003ROTS}.
+One barrier to tool adoption is the discoverability barrier, where users are unaware of a tool's existence~\cite{Murphy-HillScreencastingDiscovery}.
 This lack of tool awareness in the software engineering industry can lead to the production of poor-quality applications, inconvenienced users, and significant amounts of time and money spent fixing errors.
@@
 %TODO: Use related work from whatever conference committee
-This project builds on previous research examining the intersection between recommendation systems and software engineering.
+This project builds on previous work by researchers examining recommendation systems in software engineering.
 
-Previous research has also studied techniques developers use to learn new information.
-Piorkowski and colleagues applied Information Foraging Theory to software engineers to determined how developers seek information~\cite{FlemingReactiveInformationForaging}.
-This research differs from these approaches by presenting and implementing a new technique
-
-Prior work has examined help systems for soft in software engineering.
-
-Researchers have created many different approaches for tool recommendations.
+Previous research has explored different approaches for recommending tools to software users.
+Gordon and colleagues developed Codepourri, a system that uses \textit{crowdsourcing} to make recommendations for Python code~\cite{Gordon2015Codepourri}.
+<gamification> <idea gardening> Linton and colleagues implemented organization-wide learning (OWL) by using system logs make recommendations to employees throughout a company~\cite{Linton2000OWL}.
+Maltzahn and colleagues developed ToolBox, a ``community sensitive help system'' to recommend Unix commands~\cite{Maltzahn1995Toolbox}.
 Fischer and colleagues found that systems requiring users to explicitly seek help, or passive help systems, are ineffective and active help systems are more useful for increasing tool awareness~\cite{Fischer1984ActiveHelpSystems}.
 
-There are several existing automated approaches created to solve the tool discovery problem among software developers.
-Gordon and colleagues developed Codepourri, a system using crowdsourcing to make recommendations for Python code~\cite{Gordon2015Codepourri}.
-Linton and colleagues designed a recommender system called OWL (organization-wide learning) to disseminate tool knowledge using logs throughout a company~\cite{Linton2000OWL}.
-ToolBox was developed as a ``community sensitive help system'' by Maltzahn to recommend Unix commands~\cite{Maltzahn1995Toolbox}.
-Answer Garden helps users discover new tools based on common questions asked by colleagues~\cite{Ackerman1990AnswerGarden}.
+Prior work has also studied various techniques to see how software developers learn new information.
+Piorkowski and colleagues applied \textit{information foraging theory} to software engineers to determined how developers seek information~\cite{FlemingReactiveInformationForaging}.
+Cockburn and Williams studied pair programming and found it was beneficial for increasing knowledge as a result of 84\% of software engineers they surveyed found it helped them learn `` faster and better
+because [they were] always working with a partner''~\cite{Cockburn2001PairProgramming}.
+<collaborative filtering>, Answer Garden helps users discover new tools based on common questions asked by colleagues~\cite{Ackerman1990AnswerGarden}.
+Our research presents and implements a novel approach for making tool recommendations to software engineers to increase awareness of useful development tools to help them complete programming tasks.
+
+Toolsmiths have developed automated tools to increase tool discovery among software developers.
 SpyGlass automatically recommends tools to help users navigate code~\cite{Viriyakattiyaporn2010Spyglass}.
@@
 Our approach differs from existing recommendation systems in the design and implementation of our tool.
+
+Existing research has also focused on recommendation styles for tools.
+<Mike>.
+This research introduces a novel and distinctive recommendation style based on three unique design principles to increase awareness of useful software engineering tools among developers.
 

### 2018-04-21 com/chbrown13/tool_rec/ErrorProne.java
pull request updates (fix detection needs work)

@@ -60,17 +60,20 @@ public class ErrorProne extends Tool {
 	 */
 	@Override
 	public List<Error> parseOutput(String msg) {
+		List<Error> errors = new ArrayList<Error>();
+		if (msg == null || msg.isEmpty()) {
+			return errors;
+		}
 		String regex = "^[\\w+/]*\\w.java\\:\\d+\\:.*\\:.*";
 		String dir = Utils.getCurrentDir();
 		String[] lines = msg.split("\n");
 		Error temp = null;
-		List<Error> errors = new ArrayList<Error>();
 		for (String line: lines) {
+			//System.out.println(line.matches(regex)+"##"+line);
 			if (line.matches("^\\d+\\serror[s]*$") || line.matches("^\\d+\\swarning[s]*$")) {
 				continue;
 			}
-			else if (line.startsWith("[ERROR] ") || line.startsWith("[INFO] ") ||
-						line.startsWith("[WARNING] ")) { //Maven build error
+			else if (line.startsWith("[INFO] ") || line.startsWith("[ERROR]") || line.startsWith("[WARNING] ")) { //Maven build error
 				continue;
 			}
 			else if (line.matches(regex) || line.startsWith(dir)) {
@@ -93,6 +96,7 @@ public class ErrorProne extends Tool {
 			}
 		}
 		if (temp != null && !errors.contains(temp)) { errors.add(temp); }
+		System.out.println(errors.size());
 		return errors;
 	}
 

### 2018-04-21 com/chbrown13/tool_rec/Recommender.java

@@ -1,6 +1,12 @@
 package com.chbrown13.tool_rec;
 
-import com.jcabi.github.*;
+import com.jcabi.github.Branch;
+import com.jcabi.github.Coordinates;
+import com.jcabi.github.Pull;
+import com.jcabi.github.Pull.Smart;
+import com.jcabi.github.Repo;
+import com.jcabi.github.RepoCommit;
+import com.jcabi.github.RtGithub;
 import com.jcabi.http.response.*;
 import com.jcabi.http.Request;
 import java.io.*;
@@ -10,6 +16,13 @@ import java.util.*;
 import java.util.concurrent.TimeUnit;
 import javax.json.*;
 import org.apache.commons.mail.*;
+import org.eclipse.jgit.api.*;
+import org.eclipse.jgit.api.errors.JGitInternalException;
+import org.eclipse.jgit.api.ResetCommand.ResetType;
+import org.eclipse.jgit.errors.*;
+import org.eclipse.jgit.lib.*;
+import org.eclipse.jgit.revwalk.*;
+import org.eclipse.jgit.transport.*;
 
 
 /**
@@ -18,6 +31,7 @@ import org.apache.commons.mail.*;
 public class Recommender {
 
 	private Repo repo;
+	private Git git;
 	private Set<String> fixes = new HashSet<String>();	
 	private int recs = 0;
 	private int rem = 0;
@@ -32,14 +46,14 @@ public class Recommender {
 	private int baseErrorCountFiles = 0;
 	private int newErrorCountFiles = 0;
 	private Tool tool = null;
-	private Object change = null;
 	private static String type = "";
 
 	public static final String PULL = "pull";
 	public static final String COMMIT = "commit";
 
-	public Recommender(Repo repo) {
+	public Recommender(Repo repo, Git git) {
 		this.repo = repo;
+		this.git = git;
 		Utils.setProjectName(repo.coordinates().repo());
 		Utils.setProjectOwner(repo.coordinates().user());
 	}
@@ -57,6 +71,12 @@ public class Recommender {
 		recs = 0;
 		rem = 0;
 		fix = 0;
+		log = "";
+	}
+
+	private void log(String msg) {
+		System.out.println(msg);
+		log += "\n\n" + msg + "\n";
 	}
 
 	/**
@@ -86,8 +106,7 @@ public class Recommender {
 			email.setMsg(String.join("\n", viewChanges, text));
 			email.addTo("dcbrow10@ncsu.edu");
[…]

### 2018-04-21 com/chbrown13/tool_rec/Utils.java

@@ -41,6 +41,7 @@ public class Utils {
 	public static String BASE_COMMENT = "Good job! The {desc} {tool} reported an error [1] used to be here, but you fixed it.{similar}Check out {link} for more information.\n\n\n[1] {fixed}";
 	public static String SURVEY = "[How useful was this recommendation?](https://ncsu.qualtrics.com/jfe/form/SV_4JGXYBRyb3GeF5X?project={project}&pr={id})";
 	private static String MVN_COMPILE = "mvn -q -f {dir}/pom.xml compile";
+	private static String MVN_CLEAN = "mvn -q -f {dir}/pom.xml clean";
 	private static String currentDir = System.getProperty("user.dir");
 	private static boolean myTool = false;
 	private static boolean xmlProfile = false;
@@ -392,10 +393,21 @@ public class Utils {
 	 */
 	public static String compile(String path) {
 		String output = "";
-		String cmd = MVN_COMPILE.replace("{dir}", path);
+		BufferedReader br = null;
+		String compile = MVN_COMPILE.replace("{dir}", path);
+		String clean = MVN_CLEAN.replace("{dir}", path);
+		System.out.println(clean + "\n" + compile);
 		try {
-			Process p = Runtime.getRuntime().exec(cmd);	
-			BufferedReader br = new BufferedReader(new InputStreamReader(p.getErrorStream()));
+			try {
+				Process p1 = Runtime.getRuntime().exec(clean);
+				p1.waitFor();
+				Process p2 = Runtime.getRuntime().exec(compile);	
+				p2.waitFor();
+				br = new BufferedReader(new InputStreamReader(p2.getErrorStream()));
+			} catch (InterruptedException ie) {
+				ie.printStackTrace();
+				return null;
+			}
 			String line;
 			while ((line = br.readLine()) != null) {
 			    output += line + "\n";
@@ -440,7 +452,7 @@ public class Utils {
 				public void endElement(String uri, String localName,
 					String qName) throws SAXException {
 					try {
-						if (qName.equals("plugins") && !xmlReporting) {
+						if (qName.equals("plugins") && !myTool) {
 							writer.write(tool.getPlugin());
 							myTool = true;			
 						} else if (qName.equals("project") && !myTool) {
@@ -466,6 +478,15 @@ public class Utils {
 				}
 			};
 			saxParser.parse(file, handler);
+		} catch (FileNotFoundException fnf) {
+			System.out.println("No pom.xml");
[…]

### 2018-04-21 com/chbrown13/tool_rec/ErrorProne.java
Switching to jgit checkouts instead of multiple clones

@@ -69,11 +69,11 @@ public class ErrorProne extends Tool {
 		String[] lines = msg.split("\n");
 		Error temp = null;
 		for (String line: lines) {
-			//System.out.println(line.matches(regex)+"##"+line);
 			if (line.matches("^\\d+\\serror[s]*$") || line.matches("^\\d+\\swarning[s]*$")) {
 				continue;
 			}
-			else if (line.startsWith("[INFO] ") || line.startsWith("[ERROR]") || line.startsWith("[WARNING] ")) { //Maven build error
+			else if (line.startsWith("[INFO] ") || line.startsWith("[ERROR]") || line.startsWith("[WARNING] ")
+				|| line.startsWith("Note:")) { //Maven build log
 				continue;
 			}
 			else if (line.matches(regex) || line.startsWith(dir)) {

### 2018-04-21 com/chbrown13/tool_rec/Recommender.java

@@ -66,7 +66,9 @@ public class Recommender {
 		introduced = "";
 		noSimilar = "";
 		baseErrorCount = 0;
+		baseErrorCountFiles = 0;
 		newErrorCount = 0;
+		newErrorCountFiles = 0;
 		intro = 0;
 		recs = 0;
 		rem = 0;
@@ -182,9 +184,9 @@ public class Recommender {
 			log(Integer.toString(baseErrorCount) + "------" + Integer.toString(newErrorCount) + "\n"); 
 			log(Integer.toString(baseErrorCountFiles) + "------" + Integer.toString(newErrorCountFiles) + " (files)"); 
 			for (Error e: fixed) {
-				if (Utils.isFix(e)) {
+				if (Utils.isFix(e, base, head)) {
 					fix = true;
-					int line = Utils.getFix(id, e);			
+					int line = Utils.getFix(id, type, e);			
 					log("Fixed "+ e.getKey() + " reported at line " + e.getLineNumberStr() + 
 						" possibly fixed at line " + Integer.toString(line));
 					makeRecommendation(tool, id, e, line, changeErrors, base, head);
@@ -231,16 +233,12 @@ public class Recommender {
 			JsonObject head = pull.json().getJsonObject("head");
 			String hash = pull.json().getJsonObject("base").getString("sha");
 			String newHash = head.getString("sha");
-			log += "\n\n"+ "  "+hash+"\n\n";
-			log += "\n\n"+ "  "+newHash+"\n\n";
-			//System.out.println("checkout");
 			git.checkout().setName(hash).call();
-			System.out.println(hash);
 			List<Error> baseErrors = Utils.checkout(git, hash, tool);
+			log("base: " + hash);
 			git.checkout().setName(newHash).call();
 			List<Error> changeErrors = Utils.checkout(git, newHash, tool);
-			System.out.println(newHash);
-			//git.reset().setMode(ResetType.HARD).call();
+			log("head: " + newHash);
 			System.out.println(baseErrors.size());
 			System.out.println(changeErrors.size());
 			checkFix(baseErrors, changeErrors, javaFiles, hash, newHash, Integer.toString(pull.number()));
@@ -260,29 +258,6 @@ public class Recommender {
 		tool = new ErrorProne();		
 		List<String> javaFiles = new ArrayList<String>();
 		try {
-			/*JsonArray files = commit.json().getJsonArray("files");
-			for (int i = 0; i < files.size(); i++) {
[…]

### 2018-04-21 com/chbrown13/tool_rec/Utils.java

@@ -144,10 +144,10 @@ public class Utils {
 	 * Get the character offset of an error based on the reported line
 	 * 
 	 * @param error   Error reported by ErrorProne
-	 * @param srcFile Filename of source code
+	 * @param source  Filename of source code
 	 * @return        character offset where error begins
 	 */
-	private static int getErrorOffset(Error error, String srcFile) {
+	private static int getErrorOffset(Error error, String source) {
 		String log = error.getLog();
 		String prev = null;
 		int loc;
@@ -161,7 +161,7 @@ public class Utils {
 			}
 			prev = line;
 		}
-		File file = new File(srcFile);
+		File file = new File(source);
 		try {
 			int i = 0;
 		    Scanner sc = new Scanner(file);
@@ -318,17 +318,23 @@ public class Utils {
 	/**
 	 * Returns line number of code fix
 	 * 
-	 * @param id   ID of code change (pullrequest number or commit hash)
+	 * @param id   ID of code change (PR number or commit hash)
+	 * @param type Type of code change
 	 * @param err  Error fixed by user
 	 * @return     Line number of what is considered a fix or null if none
      */
-	public static int getFix(String id, Error err) {
-		String url = diff.replace("{id}", id);
+	public static int getFix(String id, String type, Error error) {
+		String url = null;
+		if (type.equals(Recommender.PULL)) {
+			url = PULL_DIFF.replace("{user}", projectOwner).replace("{repo}", projectName).replace("{id}", id);
+		} else if (type.equals(Recommender.COMMIT)) {
+			url = COMMIT_DIFF.replace("{user}", projectOwner).replace("{repo}", projectName).replace("{id}", id);
+		} 
 		int newLine = fixType;
 		String[] wget = wget(url).split("\n");
 		boolean found = false;
 		for (String line: wget) {
-			if (line.contains(err.getFileName())) {
+			if (line.contains(error.getFileName())) {
 				found = true;
 				continue;
 			} 
@@ -338,7 +344,7 @@ public class Utils {
 			}
 			if (found) {
 				String l = line.substring(1).trim();
-				if (err.getLog().contains(l) && !l.equals("")) {
+				if (error.getLog().contains(l) && !l.equals("")) {
 					break;
 				} 					
 				newLine += 1;
@@ -354,34 +360,22 @@ public class Utils {
 	 * @param error  Error in question
 	 * @return       True if error prone bug was fixed, else false
 	 */
[…]

### 2018-04-21 com/chbrown13/tool_rec/Recommender.java
Reset after commit check

@@ -272,7 +272,7 @@ public class Recommender {
 			log("head: " + hash);
 			System.out.println(baseErrors.size());
 			System.out.println(changeErrors.size());
-			//git.reset().setMode(ResetType.HARD).call();
+			git.reset().setMode(ResetType.HARD).call();
 			checkFix(baseErrors, changeErrors, javaFiles, oldHash, hash, hash);
 		} catch (Exception e) {
 			e.printStackTrace();

### 2018-04-21 com/chbrown13/tool_rec/Recommender.java
Reset after pull requests too

@@ -241,6 +241,7 @@ public class Recommender {
 			log("head: " + newHash);
 			System.out.println(baseErrors.size());
 			System.out.println(changeErrors.size());
+			git.reset().setMode(ResetType.HARD).call();
 			checkFix(baseErrors, changeErrors, javaFiles, hash, newHash, Integer.toString(pull.number()));
 		} catch (Exception e) {
 			e.printStackTrace();

### 2018-04-21 com/chbrown13/tool_rec/Recommender.java
15 minutes

@@ -350,7 +350,7 @@ public class Recommender {
 				RevCommit commit = revCommits.next();
 				long commitTime = (long) commit.getCommitTime() * 1000;
 				long now = new Date().getTime();
-				if (now - commitTime <= TimeUnit.MILLISECONDS.convert(1500, TimeUnit.MINUTES)) {
+				if (now - commitTime <= TimeUnit.MILLISECONDS.convert(15, TimeUnit.MINUTES)) {
 					System.out.println(ObjectId.toString(commit.getId()));
 					analyze(git, commit);
 					commits.add(commit);

### 2018-04-22 paper/paper.tex
Minor intro updates

@@
 Although software quality is important, software engineering tools created to improve code quality are often ignored by developers~\cite{Ivanov2017Gaps}.
-Previous work explores barriers preventing software engineers from utilizing useful tools for debugging~\cite{CaoDebugging}, static analysis~\cite{Johnson2013Why}, security~\cite{Xiao2014Security}, refactoring~\cite{MurpyHillBarriersRefactoring}, documentation~\cite{ForwardDocumentationRelevance}, and more to help complete programming tasks.
-Additionally, Tilley and colleagues presented challenges for professional software developers in industry adopting software engineering tools created by researchers, or research-off-the-shelf (ROTS) software~\cite{Tilley2003ROTS}.
+Tilley and colleagues suggest tool adoption should be one of the most important goals of software engineering research, and present challenges preventing professional developers from adopting programming tools created by researchers, or research-off-the-shelf (ROTS) software~\cite{Tilley2003ROTS}.
+Furthermore, researchers have explored barriers preventing software engineers from utilizing useful tools for debugging~\cite{CaoDebugging}, static analysis~\cite{Johnson2013Why}, security~\cite{Xiao2014Security}, refactoring~\cite{MurpyHillBarriersRefactoring}, documentation~\cite{ForwardDocumentationRelevance}, and more.
 One barrier to tool adoption is the discoverability barrier, where users are unaware of a tool's existence~\cite{Murphy-HillScreencastingDiscovery}.
-This lack of tool awareness in the software engineering industry can lead to the production of poor-quality applications, inconvenienced users, and significant amounts of time and money spent fixing errors.
-Many existing automated approaches have been implemented to increase awareness of software tools and features, but Murphy-Hill and colleagues found that developers prefer learning about tools from colleagues during normal work activities, or \textit{peer interactions}~\cite{MurphyHill2011PeerInteraction}.
+This lack of tool awareness in the software engineering industry can lead to poor-quality applications, inconvenienced users, and wasted time and money fixing errors.
+Automated approaches have been developed to increase awareness of software tools and features, however Murphy-Hill and colleagues found that developers prefer learning about tools from colleagues during normal work activities, or \textit{peer interactions}~\cite{MurphyHill2011PeerInteraction}.
 
@@
 Our approach integrates characteristics of peer interactions and software engineering practices to suggest useful tools to developers.
-We base our technique on three main design pillars- \textit{commend}, \textit{apprehend}, and \textit{recommend}.
-These principles differentiate our approach from existing techniques because they can be applied to many different types of software engineering tools and integrate user receptiveness to make customized recommendations to developers.
+We base our technique on three design pillars: \textit{commend}, \textit{apprehend}, and \textit{recommend}.
+These principles allow our approach to be applied to a variety software engineering tools and to make customized recommendations to developers.
+Our goal is for researchers and toolsmiths to implement this approach to increase awareness and adoption of their tools.
 
@@
 The initial implementation of \tool~for this study recommends \textsc{Error Prone}\footnote{http://errorprone.info}, an open source static analysis tool for Java code, to developers on GitHub\footnote{https://github.com}, a popular code hosting and collaboration website.
-We measured the effectiveness of our system by observing the frequency of recommendations and how developers reacted to receiving suggestions for tools from our system.
+We measure the effectiveness of our approach by observing the frequency of recommendations and how developers react to receiving suggestions for tools from our system compared to other recommendation methods.
 This research makes the following contributions:

### 2018-04-22 com/chbrown13/tool_rec/ErrorProne.java
Extracting out checkout code into its own method

@@ -64,19 +64,20 @@ public class ErrorProne extends Tool {
 		if (msg == null || msg.isEmpty()) {
 			return errors;
 		}
+		boolean compile = true;
 		String regex = "^[\\w+/]*\\w.java\\:\\d+\\:.*\\:.*";
 		String dir = Utils.getCurrentDir();
 		String[] lines = msg.split("\n");
 		Error temp = null;
 		for (String line: lines) {
-			if (line.matches("^\\d+\\serror[s]*$") || line.matches("^\\d+\\swarning[s]*$")) {
+			if (line.matches("^\\d+\\serror[s]*$") || line.matches("^\\d+\\swarning[s]*$") || line.startsWith("Note:")) {
 				continue;
 			}
-			else if (line.startsWith("[INFO] ") || line.startsWith("[ERROR]") || line.startsWith("[WARNING] ")
-				|| line.startsWith("Note:")) { //Maven build log
+			else if (line.startsWith("[INFO] ") || line.startsWith("[ERROR]") || line.startsWith("[WARNING] ")) {
+				//Maven build log
+				compile = false;
 				continue;
-			}
-			else if (line.matches(regex) || line.startsWith(dir)) {
+			} else if (line.matches(regex) || line.startsWith(dir)) {
 				if (temp != null && !errors.contains(temp)) {	errors.add(temp); }
 				String[] error = line.split(":");
 				String errorFilePath = error[0];
@@ -96,7 +97,9 @@ public class ErrorProne extends Tool {
 			}
 		}
 		if (temp != null && !errors.contains(temp)) { errors.add(temp); }
-		System.out.println(errors.size());
+		if (errors.size() == 0 && !compile) {
+			return null;
+		}
 		return errors;
 	}
 

### 2018-04-22 com/chbrown13/tool_rec/Recommender.java

@@ -17,7 +17,7 @@ import java.util.concurrent.TimeUnit;
 import javax.json.*;
 import org.apache.commons.mail.*;
 import org.eclipse.jgit.api.*;
-import org.eclipse.jgit.api.errors.JGitInternalException;
+import org.eclipse.jgit.api.errors.*;
 import org.eclipse.jgit.api.ResetCommand.ResetType;
 import org.eclipse.jgit.errors.*;
 import org.eclipse.jgit.lib.*;
@@ -33,6 +33,7 @@ public class Recommender {
 	private Repo repo;
 	private Git git;
 	private Set<String> fixes = new HashSet<String>();	
+	private List<String> changes = new ArrayList<String>();
 	private int recs = 0;
 	private int rem = 0;
 	private int fix = 0;
@@ -40,13 +41,14 @@ public class Recommender {
 	private String removed = "";
 	private String introduced = "";
 	private String noSimilar = "";
-	private static String log = "";
 	private int baseErrorCount = 0;
 	private int newErrorCount = 0;
 	private int baseErrorCountFiles = 0;
 	private int newErrorCountFiles = 0;
 	private Tool tool = null;
 	private static String type = "";
+	private static String log = "";
+	
 
 	public static final String PULL = "pull";
 	public static final String COMMIT = "commit";
@@ -152,7 +154,7 @@ public class Recommender {
 	/**
 	 * Checks if the change is actually a fix or not
 	 */
-	private boolean checkFix(List<Error> baseErrors, List<Error> changeErrors, List<String> files, String base, String head, String id) {
+	private boolean checkFix(List<Error> baseErrors, List<Error> changeErrors, String base, String head, String id) {
 		boolean fix = false;
 		if(baseErrors != null && changeErrors != null) {
 			List<Error> fixed = new ArrayList<Error>();	
@@ -200,21 +202,62 @@ public class Recommender {
 	}
 
 	/**
+	 * Checkout code versions and get errors for each
+	 * 
+	 * @param git   Git repository object
+	 * @param base  Commit hash for base version
+	 * @param head  Commit hash for changed version
+	 * @param id    Code change id
+	 */
+	private boolean checkout (Git git, String base, String head, String id) {
+		this.changes.add(base);
+		this.changes.add(head);
+		List<Error> baseErrors = null;
+		List<Error> changeErrors = null;
+		try {
+			git.checkout().setName(base).call();
[…]

### 2018-04-22 com/chbrown13/tool_rec/Utils.java

@@ -509,83 +509,26 @@ public class Utils {
 	}
 
 	/**
-	 * Checkout git repository with same user and project
+	 * Get errors from software engineering tool
 	 * 
 	 * @param git    Current instance of git repo
 	 * @param hash   Hash of GitHub change
 	 * @param tool   Tool to recommend
 	 * @return       List of errors reported from tool
 	 */
-	public static List<Error> checkout(Git git, String hash, Tool tool) {
+	public static List<Error> getErrors(Git git, String hash, Tool tool) {
 		String log = null;
+		List<Error> errors = null;
 		try {
 			addToolPomPlugin(projectName, tool);
 			log = compile(projectName);
 			System.out.println(log);
+			errors = tool.parseOutput(log);
 		} catch (Exception e) {
 			e.printStackTrace();
 		}
-		return tool.parseOutput(log);
+		return errors;
 	}
-
-	/**
-	 * Checkout specific version of a git repository to analyze
-	 * 
-	 * @param hash   Hash of GitHub change
-	 * @param owner  GitHub user
-	 * @param repo   Name of repository
-	 * @param tool   Tool to recommend
-	 * @param base   True if original version of repo
-	 * @param type   Type of code change (PULL or COMMIT)
-	 * @return       List of errors reported from tool
-	 *
-	public static List<Error> checkout(String hash, String owner, String repo, Tool tool, boolean base, String type) throws IOException {
-		String dirName = projectName;
-		Git git = null;
-		try {
-			if(base) {
-				dirName += "1";
-				if (type.equals(Recommender.PULL)) {
-					diff = PULL_DIFF.replace("{user}", owner).replace("{repo}", repo);
-				} else {
-					diff = COMMIT_DIFF.replace("{user}", owner).replace("{repo}", repo);
-				}
-			} else {
-				dirName += "2";
-			}
-		} catch (Exception e) {
-			e.printStackTrace();
-			return null;
-		}
-		System.out.println(dirName+" "+owner+" "+hash);
-		try {
-			git.checkout().setName(hash).call();
-		} catch (Exception e) {
-			e.printStackTrace();
-			return null;
-		}
-		addToolPomPlugin(dirName, tool);
-		String log = compile(dirName);
-		if (log == null) {
-			return null;
-		}
-		//System.out.println(log);
-		return tool.parseOutput(log);
-	}*/
-
-	/**
-	 * Remove temp repo directories
-	 *
[…]

### 2018-04-22 com/chbrown13/tool_rec/Recommender.java
Remove jcabi Branch import

@@ -1,6 +1,5 @@
 package com.chbrown13.tool_rec;
 
-import com.jcabi.github.Branch;
 import com.jcabi.github.Coordinates;
 import com.jcabi.github.Pull;
 import com.jcabi.github.Pull.Smart;

### 2018-04-26 eval_scripts/eval.py
Fixes for eval scripts

@@ -1,4 +1,4 @@
-DIR = "/home/dcbrow10/"
+DIR = "/home/dcbrow10"
 
 def jenkins(user, repo):
     with open("jenkins.xml") as f:

### 2018-04-27 paper/paper.tex
RW updates and added paragraph to methodology about rec review

@@
 %TODO: Use related work from whatever conference committee
-This project builds on previous work by researchers examining recommendation systems in software engineering.
+This project builds on previous work by researchers studying recommendations in software engineering.
 
-Previous research has explored different approaches for recommending tools to software users.
-Gordon and colleagues developed Codepourri, a system that uses \textit{crowdsourcing} to make recommendations for Python code~\cite{Gordon2015Codepourri}.
-<gamification> <idea gardening> Linton and colleagues implemented organization-wide learning (OWL) by using system logs make recommendations to employees throughout a company~\cite{Linton2000OWL}.
+%Learning in SE
+Previous research has examined techniques to improve how software engineers learn new information.
+Cockburn and Williams studied the software engineering practice of \textit{pair programming}, and found that 84\% of participants found the practice to be beneficial for increasing knowledge and helped them learn `` faster and better because [they were] always working with a partner''~\cite{Cockburn2001PairProgramming}.
+Gordon and colleagues developed Codepourri, a system that uses \textit{crowdsourcing} to create visual Python tutorials to improve information presented to learners~\cite{Gordon2015Codepourri}.
+Piorkowski and colleagues applied \textit{information foraging theory} to software engineers to determine how developers debug and propose software engineering tools integrate this process into their workflow~\cite{FlemingReactiveInformationForaging}.
+This project also seeks to improve software engineer learning, however our approach specifically aims to increase awareness of useful software engineering tools to help developers in their work.
+
+%Other existing approaches
+Researchers have also developed approaches to improve recommendations to software engineers.
+Fischer and colleagues encourage the use of \textit{active help systems} to guide users over passive help systems that require users to explicitly seek help~\cite{Fischer1984ActiveHelpSystems}.
+Cao and colleagues introduced \textit{idea gardening}, an approach for helping end-user programmers overcome barriers.
+Linton and colleagues implemented organization-wide learning (OWL) by using system logs make recommendations to employees throughout a company~\cite{Linton2000OWL}.
+Our work builds on research in this area by introducing a distinctive recommendation approach with three original design principles to make tool suggestions to developers more effective.
+
+%Other existing tools
+More specifically, researchers and toolsmiths have developed automated recommender systems to increase awareness of software engineering tools.
 Maltzahn and colleagues developed ToolBox, a ``community sensitive help system'' to recommend Unix commands~\cite{Maltzahn1995Toolbox}.
-Fischer and colleagues found that systems requiring users to explicitly seek help, or passive help systems, are ineffective and active help systems are more useful for increasing tool awareness~\cite{Fischer1984ActiveHelpSystems}.
+SpyGlass automatically recommends tools to help users navigate code~\cite{Viriyakattiyaporn2010Spyglass}.
+To improve the effectiveness of automated system-to-user recommendations, we implemented \tool~to evaluate our novel approach based on design principles derived from user-to-user recommendations.
 
-Prior work has also studied various techniques to see how software developers learn new information.
-Piorkowski and colleagues applied \textit{information foraging theory} to software engineers to determined how developers seek information~\cite{FlemingReactiveInformationForaging}.
-Cockburn and Williams studied pair programming and found it was beneficial for increasing knowledge as a result of 84\% of software engineers they surveyed found it helped them learn `` faster and better
-because [they were] always working with a partner''~\cite{Cockburn2001PairProgramming}.
-<collaborative filtering>, Answer Garden helps users discover new tools based on common questions asked by colleagues~\cite{Ackerman1990AnswerGarden}.
-Our research presents and implements a novel approach for making tool recommendations to software engineers to increase awareness of useful development tools to help them complete programming tasks.
-
-Toolsmiths have developed automated tools to increase tool discovery among software developers.
-SpyGlass automatically recommends tools to help users navigate code~\cite{Viriyakattiyaporn2010Spyglass}.
-We developed \tool~to actively suggest useful programming tools and increase awareness for software engineers.
-Our approach differs from existing recommendation systems in the design and implementation of our tool.
-
-Existing research has also focused on recommendation styles for tools.
-<Mike>.
-This research introduces a novel and distinctive recommendation style based on three unique design principles to increase awareness of useful software engineering tools among developers.
+%Other existing evaluations
+Existing research has also focused on different recommendation styles for software engineering tools.
+Murphy-Hill and colleagues outlined existing ways to make recommendations to present and evaluate new algorithms based on collaborative filtering and feature discovery~\cite{Murphy-HillDeveloperFluency}.
+Winters and colleagues analyzed different styles of tool recommendationsand found that suggestion style impacts tool adoption for software developers~\cite{Mike Winters}.
+This research introduces a brand new recommendation style and measures the effectiveness of our approach by comparing it to other various styles of recommendations.
 
@@
 
+\subsubsection{Recommendation Styles}
+
 To test the effectiveness of our approach, we used four different recommendation styles based on our design principles of commending developers for their work and apprehending opportunities to make similar changes.
@@
 
-Johnson and colleagues discovered one of the primary barriers to static analysis tool usage among software engineers is false positives in the output~\cite{Johnson2013Why}.
-To prevent unnecessary recommendations from our system, we manually reviewed all instances where \tool~reported a recommendation should be made.
-After inspecting each repository modification, \tool~determines whether it is an appropriate case to make a recommendation to the developer.
-For this study, we streamlined this process to send an email for the authors to review if a recommendation was proposed by our system.
-After the authors reviewed the code changes, if we deemed it was a true positive case we proceeded to use \tool~to post the comment recommending \textsc{Error Prone} to the developer on the pull request or commit.
-Otherwise, we noted the instance of a false positive in our approach and did not make the recommendation.
-In situations where one repository code change provided multiple opportunities for a recommendation, the authors examined each of the changes and selected one of the errors reported as fixed to recommend to the developer.
+We manually reviewed each instance where \tool~reported a recommendation to a developer for two reasons.
+First, we wanted to ensure that only one \textsc{Error Prone} recommendation was made to each project.
+This avoids biasing our results by minimizing the chance other GitHub users working on the same project discover the tool from a comment made to that repository.
+Additionally, in some cases one commit or pull request provided multiple opportunities for a recommendation.
+In this case, the authors examined each instance and selected one of errors reported  to make a recommendation on.
+
+Next, we inspected cases to avoid making uneccesary recommendations to developers.
+Johnson and colleagues discovered one of the primary barriers of static analysis tool usage for software engineers is false positive output~\cite{Johnson2013Why}.
+To prevent multple comments on one project and false positives from our system, we modified \tool~to send an email to the researchers with the proposed recommendation.
+After checking the code changes, we proceeded to use \tool~to post the comment recommending \textsc{Error Prone} to the developer on their pull request or commit if the fix was deemed to be a true positive and the repository had not previously received a recommendation.
+Otherwise, we noted the instance as a false positive in our implementation and did not make a recommendation.
 

### 2018-05-03 paper/paper.tex
Related work updates

@@
 Tilley and colleagues suggest tool adoption should be one of the most important goals of software engineering research, and present challenges preventing professional developers from adopting programming tools created by researchers, or research-off-the-shelf (ROTS) software~\cite{Tilley2003ROTS}.
-Furthermore, researchers have explored barriers preventing software engineers from utilizing useful tools for debugging~\cite{CaoDebugging}, static analysis~\cite{Johnson2013Why}, security~\cite{Xiao2014Security}, refactoring~\cite{MurpyHillBarriersRefactoring}, documentation~\cite{ForwardDocumentationRelevance}, and more.
+Furthermore, researchers have explored barriers preventing software engineers from utilizing useful tools for debugging~\cite{Cao2010Debugging}, static analysis~\cite{Johnson2013Why}, security~\cite{Xiao2014Security}, refactoring~\cite{Murphy-HillBarriersRefactoring}, documentation~\cite{ForwardDocumentationRelevance}, and more.
 One barrier to tool adoption is the discoverability barrier, where users are unaware of a tool's existence~\cite{Murphy-HillScreencastingDiscovery}.
 This lack of tool awareness in the software engineering industry can lead to poor-quality applications, inconvenienced users, and wasted time and money fixing errors.
-Automated approaches have been developed to increase awareness of software tools and features, however Murphy-Hill and colleagues found that developers prefer learning about tools from colleagues during normal work activities, or \textit{peer interactions}~\cite{MurphyHill2011PeerInteraction}.
+Automated approaches have been developed to increase awareness of software tools and features, however Murphy-Hill and colleagues found that developers prefer learning about tools from colleagues during normal work activities, or \textit{peer interactions}~\cite{Murphy-Hill2011PeerInteraction}.
 
@@
 
-%Learning in SE
-Previous research has examined techniques to improve how software engineers learn new information.
-Cockburn and Williams studied the software engineering practice of \textit{pair programming}, and found that 84\% of participants found the practice to be beneficial for increasing knowledge and helped them learn `` faster and better because [they were] always working with a partner''~\cite{Cockburn2001PairProgramming}.
-Gordon and colleagues developed Codepourri, a system that uses \textit{crowdsourcing} to create visual Python tutorials to improve information presented to learners~\cite{Gordon2015Codepourri}.
-Piorkowski and colleagues applied \textit{information foraging theory} to software engineers to determine how developers debug and propose software engineering tools integrate this process into their workflow~\cite{FlemingReactiveInformationForaging}.
-This project also seeks to improve software engineer learning, however our approach specifically aims to increase awareness of useful software engineering tools to help developers in their work.
+% Recommendations in Software
+Many researchers have developed approaches to try to solve the tool adoption problem for software users.
+Fischer and colleagues suggest passive help systems, which require software users to explicitly seek information, are ineffective and inconventient, and \textit{active help systems} designed to automatically guide and support users in their work are more effective~\cite{Fischer1984ActiveHelpSystems}.
+Passive recommendation approaches such as \textit{organizational memory} implemented in \textsc{Answer Garden}~\cite{Ackerman1990AnswerGarden}, \textit{group memory} in TeamInfo~\cite{Berlin1993TeamInfo}, and \textit{idea gardening}~\cite{Cao2011IdeaGarden} by Cao and colleagues use social and collaborative means to improve tool adoption and help software users overcome barriers.
+Other active solutions like Maltzahn's prototype recommender system \textsc{ToolBox}~\cite{Maltzahn1994Toolbox}, CommunityCommands by Matejka and colleagues\cite{Matejka2009CommunityCommands}, and Linton and colleagues' \textit{organization-wide learning} (OWL) technique~\cite{Linton2000OWL} monitor software actions by users by tracking logs on networked computers or stored in a database to suggest helpful commands and strategies to other users performing similar tasks.
+This research also aims to improve tool adoption among software users.
+To do improve the effectiveness of software recommendations, we introduce a new approach with three unique design principles and implement this approach in a novel active help system, \tool, that focuses on suggesting software engineering tools to developers.
 
-%Other existing approaches
-Researchers have also developed approaches to improve recommendations to software engineers.
-Fischer and colleagues encourage the use of \textit{active help systems} to guide users over passive help systems that require users to explicitly seek help~\cite{Fischer1984ActiveHelpSystems}.
-Cao and colleagues introduced \textit{idea gardening}, an approach for helping end-user programmers overcome barriers.
-Linton and colleagues implemented organization-wide learning (OWL) by using system logs make recommendations to employees throughout a company~\cite{Linton2000OWL}.
+%Recommendations to developers
+More specifically, researchers have created techniques to improve the tool adoption problem among software engineers.
+Dubois and Tamburrelli argue that \textit{gamification} can motivate software engineers to adopt new tools and better software development practices~\cite{Dubois2013Gamification}, and this has been implemented in systems such as Blaze~\cite{Snipes2014Blaze}, HALO~\cite{Sheth2011Halo}, and Teamfeed~\cite{Singer2012Teamfeed}.
+Latoza and colleagues suggest \textit{crowdsourcing} is also beneficial for software engineering\cite{Latoza2016Crowdsourcing}.
+This has been used by researchers to improve developer learning and feature adoption in systems like Codepourri for Python tutorials~\cite{Gordon2015Codepourri}, CrowdStudy for web applications~\cite{Nebeling2013CrowdStudy}, and platforms such as TopCoder\cite{Lakhani2010TopCoder}.
 Our work builds on research in this area by introducing a distinctive recommendation approach with three original design principles to make tool suggestions to developers more effective.
@@
 %Other existing tools
-More specifically, researchers and toolsmiths have developed automated recommender systems to increase awareness of software engineering tools.
-Maltzahn and colleagues developed ToolBox, a ``community sensitive help system'' to recommend Unix commands~\cite{Maltzahn1995Toolbox}.
-SpyGlass automatically recommends tools to help users navigate code~\cite{Viriyakattiyaporn2010Spyglass}.
-To improve the effectiveness of automated system-to-user recommendations, we implemented \tool~to evaluate our novel approach based on design principles derived from user-to-user recommendations.
+Furthermore, researchers and toolsmiths have developed automated recommender systems to increase awareness of software engineering tools.
+SpyGlass automatically monitors developer actions, infers navigation tasks, and recommends tools to help users navigate code more efficiently~\cite{Viriyakattiyaporn2010Spyglass}.
+Systems such as Review Bot by Balachandran~\cite{BalachandranReviewBot} and Tricorder by Sadowski and colleagues~\cite{SadowskiTricorder} seek to improve adoption of program analysis in industry by automatically running static analysis tools and presenting the output to software engineers during code reviews and project builds.
+To improve the effectiveness of automated system-to-user recommendations, we implemented \tool~to evaluate our recommendation approach based on design principles derived from user-to-user recommendations.
+Additionally, this is the first approach to our knowledge that can be extended to recommend different types of software engineering tools to developers and that can be utilized by other researchers to increase awareness of their work.
 
 %Other existing evaluations
-Existing research has also focused on different recommendation styles for software engineering tools.
-Murphy-Hill and colleagues outlined existing ways to make recommendations to present and evaluate new algorithms based on collaborative filtering and feature discovery~\cite{Murphy-HillDeveloperFluency}.
-Winters and colleagues analyzed different styles of tool recommendationsand found that suggestion style impacts tool adoption for software developers~\cite{Mike Winters}.
-This research introduces a brand new recommendation style and measures the effectiveness of our approach by comparing it to other various styles of recommendations.
+Finally, existing research has also analyzed different types and styles of software engineering tool recommendations.
+Murphy-Hill and colleagues outlined existing recommendation algorithms to propose new algorithms based on the previous methods~\cite{Murphy-Hill2011Fluency}.
+Moreover, Murphy-Hill explored seven different methods of tool recommendations: peer observations, peer recommendations, tool encounters, tutorials, written descriptions, Twitter or RSS Feeds, and discussion threads- and found that peer interactions (peer observation and recommendation) were the most effective mode of tool discovery among software engineers~\cite{Murphy-Hill2011PeerInteraction, Murphy-Hill2015HowDoUsers}.
+Piorkowski and colleagues evaluated different recommendation algorithms to determine if \textit{information foraging theory}~\cite{Pirolli1999IFT} can be applied to improve recommendations using structure and wording based on how software engineers seek information~\cite{Piorkowski2012ReactiveIFT}.
+Additionally, Winters and colleagues analyzed different styles of tool recommendations and found that suggestion style impacts tool adoption for software developers [Mike].
+This study compares the effectiveness of our approach to other recommender styles by modifying our design principles to investigate different wording and methods of communication in tool recommendations to developers.
 
@@
 Research suggests recommendations between colleagues is the most effective mode of tool discovery.
-Murphy-Hill and colleagues interviewed software engineers and found that, even though they appear less frequently in the workplace, developers prefer peer interactions over system-to-user recommendations.~\cite{MurphyHill2011PeerInteraction}~\cite{Murphy-Hill2015HowDoUsers}.
+Murphy-Hill and colleagues interviewed software engineers and found that, even though they appear less frequently in the workplace, developers prefer peer interactions over system-to-user recommendations.~\cite{Murphy-Hill2011PeerInteraction}.
 Similarly, Welty discovered that software users sought help from colleagues more often than search engines and help menus~\cite{Welty2011Help}.

### 2018-05-10 paper/paper.tex
Adding images to paper

@@
 Tilley and colleagues suggest tool adoption should be one of the most important goals of software engineering research, and present challenges preventing professional developers from adopting programming tools created by researchers, or research-off-the-shelf (ROTS) software~\cite{Tilley2003ROTS}.
-Furthermore, researchers have explored barriers preventing software engineers from utilizing useful tools for debugging~\cite{Cao2010Debugging}, static analysis~\cite{Johnson2013Why}, security~\cite{Xiao2014Security}, refactoring~\cite{Murphy-HillBarriersRefactoring}, documentation~\cite{ForwardDocumentationRelevance}, and more.
+Furthermore, researchers have explored barriers preventing software engineers from utilizing useful tools for debugging~\cite{Cao2010Debugging}, static analysis~\cite{Johnson2013Why}, security~\cite{Xiao2014Security}, refactoring~\cite{Murphy-HillBarriersRefactoring}, documentation~\cite{Forward2002Documentation}, and more.
 One barrier to tool adoption is the discoverability barrier, where users are unaware of a tool's existence~\cite{Murphy-HillScreencastingDiscovery}.
@@
 Our goal is that through commending and apprehending, we can improve the effectiveness of recommendations for software engineering tools and increase adoption among developers.
+Figure \ref{fig:chartA} provides a general overview of how our approach can be implemented as an active help system.
 
-%TODO: Non-lossy image
-%TODO: More interesting error
+%TODO: All non-lossy images
 \begin{figure*}
-	\includegraphics[width=\textwidth]{images/screenshot.png}
-	\caption{Screenshot of recommendation from \tool}	
-	\label{fig:tool} 
+	\includegraphics[width=\textwidth]{images/flowchartA.png}
+	\caption{Flowchart presenting a general implementation of our approach}	
+	\label{fig:chartA} 
 \end{figure*}
@@
 
+%TODO: More interesting error?
+\begin{figure*}
+	\includegraphics[width=\textwidth]{images/screenshot.png}
+	\caption{Screenshot of recommendation from \tool}	
+	\label{fig:tool} 
+\end{figure*}
+
 \section{Implementation Description}
@@
 This sections provides technical details on the implementation of our approach in \tool.
+Figure \ref{fig:chartB} shows a specific flowchart displaying the implementation of our design principles for the evaluation.
 The design of our system is motivated by current practices in the software engineering industry to make \tool~more similar to a peer for developers.
+
+\begin{figure*}
+	\includegraphics[width=\textwidth]{images/flowchartB.png}
+	\caption{Flowchart presenting how we implemented our approach in \tool}	
+	\label{fig:chartB} 
+\end{figure*}
 

### 2018-05-10 paper/paper.tex
Updated images and added references to text

@@
 
+\begin{figure*}
+	\includegraphics[width=\textwidth]{images/flowchartA.png}
+	\caption{Flowchart presenting a general implementation of our approach: \textit{A) Store project source code; B) Check for code changes; C.1) Add tool plugin, run tool on original code, and collect output; C.2) Add tool plugin, run tool on modified code, and collect output; D) Check for development tasks performed between versions of code; E) Search for other places where task can be applied; F) Recommend tool to help perform task.}}
+	\label{fig:chartA} 
+\end{figure*}
+
 \section{Approach}
@@
 Our approach uses three design pillars to increase awareness of software engineering tools: \textit{commend} developers on their work, \textit{apprehend} additional opportunities for improvement, and \textit{recommend} useful development tools to enhance the quality of the code.
+Figure \ref{fig:chartA} provides a general overview of how we implement these design pillars as an active help system.
 
@@
 
-To determine improvements in code quality, our approach monitors problems reported by the output of software engineering tools.
-For example, suppose we want to use our approach to increase awareness of useful refactoring tools.
-To do this, our technique will inspect code changes made by developers to determine if a refactoring activity occurs.
-If a refactoring activity is detected, then we commend the programmer for their work to improve the quality of the code.
+To determine improvements in code quality, our approach monitors projects for code changes made by software engineers (Figure \ref{fig:chartA}A, \ref{fig:chartA}.B).
+Software engineering tools are used to determine if programming tasks are performed by developers when they make code changes by automatically runs tools on the original version of the code and the modified version (Figure \ref{fig:chartA}.C).
+Then, we compare the tool output from on both versions of code to determine if any development tasks were performed by the developer (Figure \ref{fig:chartA}.D).
+For example, if we want to recommend a refactoring tool to a developer in an Integrated Development Environment (IDE), then we would wait for changes to the code base and use a tool to detect if a refactoring activity occured in the modifications.
+If a refactoring activity is detected, our approach commends the programmer for their code change to improve the software quality when making a recommendation for the refactoring tool.
 
@@
 
-After commending software engineers for their work, our approach automatically finds opportunities to make similar changes to improve the code.
-For example, after the programmer completes the refactoring task, we analyze the entire updated version of the code base to find other places where the same refactoring activity is applicable.
+After determining whether a development activity occured, our approach searches for similar instances in the code where the same activity can be applied.
+To apprehend opportunities for similar programming tasks, our approach involves automatically analyzing the tool output from the updated code to automatically find new opportunities where developers can perform the same task  (Figure \ref{fig:chartA}.E).
+For example, after the programmer completes the refactoring task in the IDE our approach analyzes the entire updated version of the code base to find other places where the same refactoring activity is applicable.
 
@@
 
-The final step of our approach is to recommend useful software engineering tools to developers.
-The recommendation to developers includes commending them for improving code quality and apprehending new opportunities for similar improvements.
-In our example, the recommendation to the developer will praise them for their work refactoring the code, provide additional places in the code where they can make similar refactoring changes, and then suggest the refactoring tool which is useful for detecting even more instances for refactoring activities.
+The final step of our approach is to recommend software engineering tools to developers  (Figure \ref{fig:chartA}.F).
+The recommendation to developers includes commending them for improving code quality based on their changes and apprehending new opportunities to make the same improvement.
+In the continuing example, after determining refactoring activity was performed and finding other locations in the code where the same task can be performed, then our approach will make a recommendation to the developer in the IDE.
+The recommendation will praise the developer for their refactoring change, provide additional places in the code where they can make the same refactoring change, and suggest using a refactoring tool for future refactoring activities.
 Our goal is that through commending and apprehending, we can improve the effectiveness of recommendations for software engineering tools and increase adoption among developers.
-Figure \ref{fig:chartA} provides a general overview of how our approach can be implemented as an active help system.
-
-%TODO: All non-lossy images
-\begin{figure*}
-	\includegraphics[width=\textwidth]{images/flowchartA.png}
-	\caption{Flowchart presenting a general implementation of our approach}	
-	\label{fig:chartA} 
-\end{figure*}
 
@@
 
-First, a GitHub user makes a change to a repository.
-\tool~automatically analyzes to commits and pull requests GitHub projects to find opportunities to commend developers when bugs reported by \textsc{Error Prone} are removed.
+First, we clone repositories locally to detect when GitHub users make changes to a project as a commit or pull request (Figure \ref{fig:chartB}.A.3,  \ref{fig:chartB}.B).
+\tool~automatically analyzes code changes to find opportunities to commend developers when bugs reported by \textsc{Error Prone} are removed.
 \textsc{Error Prone} is a static analysis tool that uses a suite of defined bug patterns to detect errors in Java code.
@@
 
-Next, \tool~apprehends places where similar opportunities to the code can be made.
-GitHub should be knowledgeable and familiar with the changes they propose, as well as the code base to which they are contributing.
+Next, \tool~apprehends places where similar opportunities to the code can be made (Figure \ref{fig:chartA}.E).
+GitHub developers should be knowledgeable and familiar with the changes they propose, as well as the code base to which they are contributing.
 \tool~suggests \textsc{Error Prone} when a reported bug is fixed by a developer in a commit or pull request, but the same error still exists elsewhere in the code.
@@
 	\includegraphics[width=\textwidth]{images/flowchartB.png}
-	\caption{Flowchart presenting how we implemented our approach in \tool}	
+	\caption{Flowchart presenting our implementation of \tool~for this evaluation: \textit{A) Store project source code; B) Check for code changes; C.1) Add tool plugin, run tool on original code, and collect output; C.2) Add tool plugin, run tool on modified code, and collect output; D) Check for development tasks performed between versions of code; E) Search for other places where task can be applied; F) Recommend tool to help perform task.}}
 	\label{fig:chartB} 
@@
 To analyze 700+ GitHub repositories simultaneously, we set up \tool~on virtual machines.
-We used Ansible\footnote{https://www.ansible.com/} to automatically generate and provision Jenkins jobs for every project.
-To limit the load on each machine, we ran our study in parallel by dividing the Jenkins jobs among \textit{n} virtual CentOS images.
-The scripts and instructions to used setup our study environment for \tool~are publicly available to view online.
+We used Ansible\footnote{https://www.ansible.com/} to automatically setup and install dependencies on the all the virtual machines, and then on each VM we use it to setup the Jenkins server and generate Jenkins jobs for each project.
+Each Jenkins job clones the GitHub repository, periodically checks for new commits and pull requests every 15 minutes, and runs \tool~to analyze project code changes.
+Figure \ref{fig:chartB}.A.1-A.3 displays the setup process for our evaluation of \tool.
+Additionally, the scripts and instructions to setup the study environment are publicly available online.\footnote{\url{https://github.com/chbrown13/tool-recommender-bot/tree/master/eval_scripts/}}
 
@@
 
-We manually reviewed each instance where \tool~reported a recommendation to a developer for two reasons.
-First, we wanted to ensure that only one \textsc{Error Prone} recommendation was made to each project.
-This avoids biasing our results by minimizing the chance other GitHub users working on the same project discover the tool from a comment made to that repository.
+For our evaluation, we manually reviewed each instance where \tool~reported a recommendation to a developer.
+This step can be seen in Figure \ref{fig:chartB}.F.
+We do this for several reasons: First, we wanted to ensure that only one \textsc{Error Prone} recommendation was made to each project to avoid biasing our results by minimizing the chance other GitHub users working on the same project discover the tool from a comment made to that repository.
 Additionally, in some cases one commit or pull request provided multiple opportunities for a recommendation.

### 2019-02-05 eval_scripts/setup.sh
Update jenkins filepath

@@ -21,7 +21,7 @@ sudo mv hosts /etc/ansible/hosts
 # Download tool-recommender-bot files and dependencies
 wget -q https://raw.githubusercontent.com/chbrown13/tool-recommender-bot/master/eval_scripts/start-bot.yml
 wget -q https://raw.githubusercontent.com/chbrown13/tool-recommender-bot/master/eval_scripts/stop-bot.yml
-wget -q https://raw.githubusercontent.com/chbrown13/tool-recommender-bot/master/jenkins.xml
+wget -q https://raw.githubusercontent.com/chbrown13/tool-recommender-bot/master/eval_scripts/jenkins.xml
 wget -q https://raw.githubusercontent.com/chbrown13/tool-recommender-bot/master/eval_scripts/eval.py
 
 

### 2019-02-05 com/chbrown13/tool_rec/Error.java
Merging dev branch changes

@@ -1,5 +1,6 @@
 package com.chbrown13.tool_rec;
 
+import java.io.*;
 import java.util.*;
 
 public class Error {
@@ -104,8 +105,8 @@ public class Error {
  	 * @return   String filepath
 	 */
 	public String getLocalFilePath() {
-        String path = this.filepath.replace(Utils.getCurrentDir() + "/", "");
-        return path.substring(path.indexOf("/") + 1);
+        String path = this.filepath.replace(Utils.getCurrentDir() + File.separator, "");
+        return path.substring(path.indexOf(File.separator) + 1);
 	}
 	
 	/**
@@ -194,8 +195,7 @@ public class Error {
 		} else {
 			comment = comment.replace("{similar}", simSentence.replace("{link}", String.join(" and ", getErrorLink(iter.next(), sha), getErrorLink(iter.next(), sha))).replace("{issue}", "similar issues"));
 		}
-		String link = "\n\n" + Utils.SURVEY.replace("{project}", Utils.getProjectName()).replace("{id}", this.id);
-		comment += link;
+		comment += "\n\nPlease feel free to add any comments below explaining why you did or did not find this recommendation useful.";
 		System.out.println(comment);
 		return comment;
 	}

### 2019-02-05 com/chbrown13/tool_rec/Utils.java
Fixed issue with Date and removed deprecated dependencies

@@ -459,10 +459,10 @@ public class Utils {
 	 * Returns the time threshold for changes to check
 	 */
 	public static String getTime() {
-		Date d = new Date();
-		d.setMinutes(new Date().getMinutes() - 15);
-		DateFormat df = new SimpleDateFormat("yyyy-MM-DD'T'HH:MM:SS'Z'");
-		return df.format(d);
+		Calendar commitTime = Calendar.getInstance();
+		commitTime.set(Calendar.MINUTE, commitTime.get(Calendar.MINUTE) - 15);
+		DateFormat df = new SimpleDateFormat("yyyy-MM-dd'T'HH:mm:ss'Z'");
+		return df.format(commitTime.getTime());
 	}	
 
 	/**

### 2019-02-05 paper/paper.tex

@@
 	\includegraphics[width=\textwidth]{images/flowchartB.png}
-	\caption{Flowchart presenting our implementation of \tool~for this evaluation: \textit{A) Store project source code; B) Check for code changes; C.1) Add tool plugin, run tool on original code, and collect output; C.2) Add tool plugin, run tool on modified code, and collect output; D) Check for development tasks performed between versions of code; E) Search for other places where task can be applied; F) Recommend tool to help perform task.}}
+	\caption{Flowchart presenting our implementation of \tool~for this evaluation: \textit{A.1) Setup for \tool~on virtual machines; A.2) Setup Jenkins server and create \tool~jobs; A.3) Clone GitHub repository; B) Check for code changes; C.1) Add \textsc{Error Prone} tool plugin to pom.xml file, build original code with Maven, and collect output; C.2) Add \textsc{Error Prone} tool plugin to pom.xml file, build modified code with Maven, and collect output; D) Check for bugs fixed between versions; E) Search for other instances of bug; F) Send email to researchers to review; G) Recommend Error Prone; H) Repeat process every 15 minutes; I) Pull latest code from GitHub.
+}}
 	\label{fig:chartB} 
